---
title: "2025 ROI Preference Survey Summary Statistics"
author: "Kelsey Sanchez"
date: "`r Sys.Date()`"
header-includes: 
  \usepackage[labelformat=empty]{caption} 
  \usepackage{float}
  
output:
  pdf_document:
    latex_engine: xelatex
    toc: no
    keep_tex: yes
    fig_width: 7
    fig_height: 5
    fig_caption: yes
    df_print: paged
---


This report gives the distribution of all responses for those that completed this survey. The Qx for this questionaire may be found here: https://nih.app.box.com/file/1955714291165

The analytic data set for this report is created from the “nih-nci-dceg-connect-prod-6d04.FlatConnect.preference2026” table in BQ which is updated daily. All variables are stored as CIDs which can be found in the master dictionary: https://github.com/Analyticsphere/ConnectMasterAndSurveyCombinedDataDictionary/blob/main/MasterSurveyComb_20220317.xlsx .

\extrafloats{100}
```{r libraries, include=FALSE}

library(bigrquery)
#library(foreach)
library(knitr)
library(kableExtra)
library(tinytex)
library(data.table) ###to write or read and data management 
library(tidyverse) ###for data management
library(dplyr) ###data management
library(stringr)


bq_auth()

```


```{r BQ Pull, include=FALSE}

project <- "nih-nci-dceg-connect-prod-6d04"


pt_pull <- "SELECT Connect_ID,  D_827220437, D_987563196, D_821247024, 
D_609630315, D_278023676, D_993557295, D_543379310
FROM `nih-nci-dceg-connect-prod-6d04.FlatConnect.participants` 
where Connect_ID IS NOT NULL and 
-- passive or active, no non-active or data destruction
(D_512820379='486306141' OR D_512820379='854703046') and 
-- verified
D_821247024='197316935' and 
-- consented and user profile submitted
(D_919254129='353358909') and (D_699625233='353358909') and 
-- completed preference survey
(D_278023676='231311385')"  

ROI_Pref_pull <- "SELECT * FROM `nih-nci-dceg-connect-prod-6d04.FlatConnect.preference2026` 
where Connect_ID is not null" 


pt_pull_table <- bq_project_query(project, pt_pull)
data_pt <- bq_table_download(pt_pull_table, bigint = "integer64")

ROI_Pref_pull_table <- bq_project_query(project, ROI_Pref_pull)
data_ROI_Pref <- bq_table_download(ROI_Pref_pull_table, bigint = "integer64")

pref2026 <- left_join(data_pt, data_ROI_Pref, by="Connect_ID")


pref_26= as_tibble(pref2026)

```




```{r functions, include=FALSE}


#Kable table for questions asked to all (no skip logic)
simple_tally_funct <- function(CID, Title){  
  
  CID <- rlang::ensym(CID)
  
  #Count
  tally_table <- pref_26 %>%  group_by(!!CID) %>%  
    mutate(Response = case_when(!!CID == "525453860"	~ "Not interested",
                           !!CID == "389550600"	~ "Slightly interested",
                           !!CID == "233944056"	~ "Somewhat interested",
                           !!CID == "567539823"	~ "Fairly interested",
                           !!CID == "135672398"	~ "Very Interested",
                           TRUE ~ "Skipped this Question"),
           Response = factor(Response, levels=c("Very Interested", "Fairly interested",
                                                "Somewhat interested","Slightly interested",
                                                "Not interested","Skipped this Question"))) %>% 
    group_by(Response) %>% 
    tally() %>% 
  mutate("N (%)" = paste0(format(n, big.mark = ","), " (", round(100 * n / sum(n), 2), " %)"))
  
  
  #Add total row
  total_row <- tally_table %>% 
    summarize(Response= "Total",
              n = sum(n),
              `N (%)` = paste0(format(sum(n), big.mark = ","), 
                               " (", 100, " %)"))
  
  #Include table row
  tally_all <- rbind(tally_table, total_row)
  
  tally_all <- tally_all %>% select(-n)
  
  #Put into a kable table
  knitr::kable(tally_all,
               caption = Title) %>% 
    add_indent(seq(1, nrow(tally_all) - 1)) %>%
    kable_styling(latex_options = "scale_down")
  
  

}



```
\newpage
# Neighborhood Information
## Interest in...
```{r Questions_1_4, warning=FALSE, echo=FALSE, message=FALSE}

 
simple_tally_funct(D_144761753_D_258232940,  "Outdoor spaces and transportation?")
simple_tally_funct(D_144761753_D_829592217,  "Retail Spaces?")
simple_tally_funct(D_144761753_D_958757635,  "The people and events?")
simple_tally_funct(D_144761753_D_121884258,  "Possible environmental pollutants?")
```

```{r Questions_5, warning=FALSE, echo=FALSE, message=FALSE}

neighborhood_topics <- pref_26  %>%
    pivot_longer(cols = starts_with("D_769359476_D_"),
                 names_to = "variable",
                 values_to = "Topic") %>%
    mutate(Topic = case_when(
        Topic == '1' ~ case_when(
            variable == 'D_769359476_D_362882148' ~ 'Community Spaces',
            variable == 'D_769359476_D_478235149' ~ 'Number of tobacco Spots',
            variable == 'D_769359476_D_713190902' ~ 'Access to healthy food options',
            variable == 'D_769359476_D_460968021' ~ 'Rates of traffic incidents',
            variable == 'D_769359476_D_148692319' ~ 'Access to public transit',
            variable == 'D_769359476_D_526672486' ~ 'Community snapshot',
            variable == 'D_769359476_D_390426962' ~ 'Walkability and bikeability',
            variable == 'D_769359476_D_735210186' ~ 'IHCS Environmental pollutants'
        )))  %>%
  select(Topic,  Connect_ID) 


## Need to find out how many participants selected NONE of these options
## But table must remain a response count NOT a participant count
no_response_ids_neighborhood_topics <- neighborhood_topics %>%
  group_by(Connect_ID) %>%
  dplyr::summarise(has_response = any(!is.na(Topic)), .groups = "drop") %>%
  filter(!has_response) %>%
  dplyr::pull(Connect_ID)

neighborhood_topics_all <- neighborhood_topics %>%
  filter(!is.na(Topic)) %>%   # keep actual responses only
  select(Connect_ID, Topic) %>%
  bind_rows(
    neighborhood_topics %>%
      filter(Connect_ID %in% no_response_ids_neighborhood_topics) %>%
      distinct(Connect_ID) %>%
      mutate(Topic = "Skipped this Question")
  )



nbh_tp <- neighborhood_topics_all %>%  group_by(Topic) %>% 
  tally() %>% 
  mutate("N (%)" = paste0(format(n, big.mark = ","), " (", round(100 * n / sum(n), 2), " %)")) %>% 
  arrange(desc(n))

  
  #Add total row
  total_row <- nbh_tp %>% 
    summarize(Topic= "Total",
              n = sum(n),
              `N (%)` = paste0(format(sum(n), big.mark = ","), 
                               " (", 100, " %)"))
  
  #Include table row
  nbh_tp_all <- rbind(nbh_tp, total_row)
  
  nbh_tp_all <- nbh_tp_all %>% select(-n)
  
  #Put into a kable table
  knitr::kable(nbh_tp_all,
               caption = "Top 5 Iopic Interests") %>% 
    add_indent(seq(1, nrow(nbh_tp_all) - 1)) %>%
    kable_styling(latex_options = "scale_down")

```

\newpage
# Known Personal Cancer Risks and Those Still Under Study
## Interest in...
```{r Questions_6_10, warning=FALSE, echo=FALSE, message=FALSE}

 
simple_tally_funct(D_863590289_D_992466690,  "Vaping?")
simple_tally_funct(D_863590289_D_441711468,  "Alcohol use?")
simple_tally_funct(D_863590289_D_543037789,  "Ingredients in hair products?")
simple_tally_funct(D_863590289_D_206053854,  "Ingredients in scented air fresheners?")
simple_tally_funct(D_863590289_D_690766963 ,  "Tattoos?")
```

\newpage
# Genetic Traits
## Interest in...
```{r Questions_11, warning=FALSE, echo=FALSE, message=FALSE}
simple_tally_funct(D_136941196,  "Receiving genetic information like this \n that is not directly related to your health?")
```

\newpage
# Learning about Research
## Interest in...
```{r Questions_12_13, warning=FALSE, echo=FALSE, message=FALSE}
simple_tally_funct(D_913318697_D_214194963,  "Connect’s future goals?")
simple_tally_funct(D_913318697_D_179827949,  "Educational topics on cancer?")
```

\newpage
# Research Discoveries in Connect
## How interested are you in receiving news about research discoveries even if the study findings are not yet conclusive?
```{r Questions_14, warning=FALSE, echo=FALSE, message=FALSE}
simple_tally_funct(D_486040313 ,  "Interest Level")
```

\newpage
# Multi-Cancer Early Detection 

```{r Questions_15, warning=FALSE, echo=FALSE, message=FALSE}
simple_tally_funct(D_151535519,  "Interest level")

```

\newpage
# Is there anything else you want to tell us about your preferences for receiving personal results from Connect and other study information?
```{r Questions_16, warning=FALSE, echo=FALSE, message=FALSE, results='asis'}


open_text <- pref_26  %>% filter(!is.na(D_395168461)) %>%  select(D_395168461)

count_no <- open_text %>%
  filter(str_detect(
    tolower(D_395168461),
    paste0("\\b(", paste(tolower(c("No", "N", "Nope", "Nothing", "None", "na", "N/A", "Not at this time", "Nyet", "All good")), collapse = "|"), ")\\b")
  ))


open_text_answ <- open_text %>% anti_join(count_no, by="D_395168461")

boxfolder <- 249010618955
currentDate <- Sys.Date()


openxlsx::write.xlsx(open_text_answ,paste0("Preference_Survey_Question_16__04_01_2026.xlsx"),row.names = F,na="")
  
cat(paste0("There are ", dim(count_no)[[1]], " responses like No/N/Nope/Nothing/None/NA, ect. \n Of those that gave a different answer, those have been put into Box here:\n https://nih.app.box.com/folder/249010618955"))

```
