---
title: "Connect Weekly Survey Module Metrics"
author: "Kelsey Sanchez"
date: 'Data Extracted and Report Ran: `r Sys.Date()`'
header-includes: 
  \usepackage[labelformat=empty]{caption} 
  \usepackage{placeins} 
  \usepackage{booktabs}
  \usepackage{pdflscape}
  
output:
  pdf_document:
    latex_engine: xelatex
    extra_dependencies: ["float"]
    toc: yes
    keep_tex: yes
    fig_width: 7
    fig_height: 5
    fig_caption: yes
    df_print: paged
---








This Weekly Survey Module report contains metrics related to Connect survey completion including baseline surveys and follow up surveys. Additional metrics will be added as new surveys are released. Metrics related to the baseline biospecimen surveys, menstrual cycle survey, and COVID survey can be found in the Weekly Biospecimen Metrics reports. Metrics related to overall baseline study activity completion, including baseline survey completion, can be found in the Weekly Operations Report. The Survey Module report is run on a weekly basis and encompasses data through today at 9:30 am. This data is extracted from the flattened participants table. This report is restricted to verified participants with a recruitment status of either active or passive.


\textbf{\textcolor{blue}{Do not share any data from this report that indicate the number of individuals at any of the Connect recruitment sites with individuals outside of the Connect Study.  This includes in manuscripts, abstracts, presentations, etc. You may present data aggregated across all of the Connect sites.}}.


```{r libraries, include=FALSE, warning=FALSE}

 # \usepackage{caption}
 # \captionsetup[figure]{labelformat=empty}


library(bigrquery)
library(dplyr)
library(gmodels)
library(epiDisplay)
library(lubridate)
library(tidyverse)
library(knitr)
#install_tinytex()
library(tinytex)
#library(vtable)
library(kableExtra)
library(gtsummary)
library(data.table)


library(arsenal)
library(rio)
library(scales)
library(gt)
library(stringr) 
library(logger) ## allows us to add messages in logs to find out when/where code breaks are happening


# ######## Checking outdated R packages
# ## Ensure CRAN mirror is set for both local and GCP environments
# knitr::opts_chunk$set(echo = FALSE)
# cran_mirror <- "https://cloud.r-project.org"
# options(repos = c(CRAN = cran_mirror))
# 
# ## Adding a note to the GCP logs
# outdated_packages <- tryCatch(
#   old.packages(repos = cran_mirror),
#   error = function(e) {
#     message("Warning: Unable to check for outdated packages. Error: ", e$message)
#     NULL
#   }
# )
# 
# if (!is.null(outdated_packages)) {
#   log_info(paste0(
#     "The following R packages are outdated: ",
#     paste(rownames(outdated_packages), collapse = ", ")
#   ))
# } else {
#   log_info("No outdated packages found or CRAN unreachable.")
# }
# 
# ## Updating packages in GCP if necessary
# #update.packages(ask = FALSE, checkBuilt = TRUE, repos = cran_mirror)
# packages_to_exclude <- c("arrow")
# 
# packages_to_update <- outdated_packages[!outdated_packages[, "Package"] %in% packages_to_exclude, "Package"] 
# 
# if (length(packages_to_update) > 0) {
# install.packages(packages_to_update, ask = FALSE, checkBuilt = TRUE, repos = cran_mirror)
# } else {
# message("No packages to update after exclusion.")
# }

## Update LaTeX packages
tinytex::tlmgr_update()


#update.packages("tinytex")


bq_auth()

```

```{r GCP_Test, include=FALSE}
#options(tinytex.verbose = TRUE)
```

```{r BQPull, include=FALSE}
knitr::opts_chunk$set(dev = "png",  comment = NA)

#knitr::opts_chunk$set(comment = NA)

project = "nih-nci-dceg-connect-prod-6d04"
queryreccc <- "SELECT  Connect_ID, d_512820379, d_821247024, d_914594314, d_832139544, d_949302066 , d_205553981, 
d_536735468 , d_976570371, d_663265240, d_265193023, d_222161762,d_770257102, d_264644252, d_265193023, d_541836531, 
d_386488297, d_452942800, d_517311251 , d_822499427, d_126331570, d_914639140, d_311580100, d_827220437, d_100767870, 
d_831041022, d_255077064, d_320303124, d_684635302, d_843688458, d_870643066, d_878865966, d_167958071, token,
state_d_934298480, state_d_706256705, state_d_435027713, d_199471989, d_956490759, d_263355177,
state_d_684926335, state_d_849518448, state_d_119643471, state_d_253532712, d_764863765, d_195145666, 
d_784810139, d_176068627, d_389890053, d_609630315, d_173836415_d_266600170_d_319972665_d_661940160, 
d_220186468, d_268176409, d_784810139, d_253883960, d_265193023, d_109610692, d_610227793, d_692560814, d_747006172, d_501613780, d_109610692,
d_278023676, d_543379310, d_993557295 

-- d_692560814, d_109610692, d_610227793, d_748726394
FROM `nih-nci-dceg-connect-prod-6d04.FlatConnect.participants` where Connect_ID IS NOT NULL  and (d_512820379='486306141' OR d_512820379='854703046')" 


#Verification status condition below, we have one table counting non-verifieds so it had to be separated out of the BQ conditionality

#and d_831041022='104430631'-- not needed, according to 3/12/24 decisions we'll be keeping participant journeys in overall counts

rec_table_cc <- bq_project_query(project, queryreccc)
data_bw <- bq_table_download(rec_table_cc, bigint = "integer64")

#select only the first collection to avoid duplicates
bio_bqpull <-"SELECT Connect_ID, min(d_556788178) as d_556788178 
FROM `nih-nci-dceg-connect-prod-6d04.FlatConnect.biospecimen` 
where Connect_ID is not null
group by Connect_ID"

bio_bqpull_table <- bq_project_query(project, bio_bqpull)
bio_bq <- bq_table_download(bio_bqpull_table, bigint = "integer64")

data_c <- left_join(data_bw, bio_bq, by="Connect_ID")


#need this separate filter to look at participants unable to be verified in a later table
data_ccc <- data_c %>%  filter(d_821247024==197316935) 


all_data= as_tibble(data_ccc) 




all_data <- all_data %>%  mutate(Site = case_when(d_827220437==472940358 ~ "Baylor Scott and White",
                                                  d_827220437==125001209 ~ "KP Colorado",
                                                  d_827220437==327912200 ~ "KP Georgia",
                                                  d_827220437==300267574 ~ "KP Hawaii",
                                                  d_827220437==452412599 ~ "KP Northwest",
                                                  d_827220437==548392715 ~ "Henry Ford",
                                                  d_827220437==531629870 ~ "HealthPartners",
                                                  d_827220437==303349821 ~ "Marshfield",
                                                  d_827220437==657167265 ~ "Sanford",
                                                  d_827220437==809703864 ~ "UChicago"),
                                 process = case_when(d_100767870 == 353358909 ~ "All",
                                                     d_949302066 != 231311385 ~ "None",
                                                     d_949302066 == 231311385 & d_536735468 == 231311385 & d_976570371 == 231311385 ~ "BOH, MRE, and SAS Sections",
                                                     d_949302066 == 231311385 & d_976570371 == 231311385 & d_663265240 == 231311385  ~ "BOH, SAS, and LAW Sections",
                                                     d_949302066 == 231311385 & d_536735468 == 231311385 & d_663265240 == 231311385  ~ "BOH, MRE, and LAW Sections",
                                                     d_949302066 == 231311385 & d_536735468 == 231311385 ~ "BOH and MRE Sections",
                                                     d_949302066 == 231311385 & d_976570371 == 231311385 ~ "BOH and SAS Sections",
                                                     d_949302066 == 231311385 & d_663265240 == 231311385 ~ "BOH and LAW Sections",
                                                     d_949302066 == 231311385 ~ "BOH Section only"),
                                 BL_comp = case_when(d_100767870==353358909 ~ "All",
                                                     process=="None" ~ "None",
                                                     process=="BOH Section only" ~ "BOH Only",
                                                     TRUE ~ "2 or 3 Sections"),
                                 age = case_when(state_d_934298480 == "713781738"~ "30-34",
                                                 state_d_934298480 == '631272782' ~ "35-39",
                                                 state_d_934298480 == '124276120' ~ "40-45",
                                                 state_d_934298480 == '450985724' ~ "46-50",
                                                 state_d_934298480 == '363147933' ~ "51-55",
                                                 state_d_934298480 == '636706443' ~ "56-60",
                                                 state_d_934298480 == '771230670' ~ "61-65",
                                                 state_d_934298480 == '722846087' ~ "66-70"),
                                 race = case_when(state_d_684926335 == '635279662' |state_d_849518448 == '768826601' | state_d_119643471 == '635279662' | state_d_253532712=='723775357' ~ "White, Non-Hispanic" , 
                                                  state_d_684926335 %in% c('232334767', '401335456') |
                                                    state_d_849518448 == '181769837' |
                                                    state_d_253532712 %in% c('153444133','572474909','308427446','211228524','277568192','611398522','181769837') |
                                                    state_d_119643471 %in% c( '232334767','211228524','308427446','432722256','232663805','785578696','200929978','490725843','965998904') ~ "Other",
                                                  state_d_684926335 == '178420302'  | 
                                                    state_d_849518448 == '178420302' | 
                                                    state_d_253532712 == '178420302' |
                                                    state_d_119643471  %in% c( '986445321','746038746','178420302') |
                                                    (is.na(state_d_119643471) & d_827220437 == '657167265') ~ "Unknown"),
                                 sex = case_when(state_d_706256705 == '536341288' | state_d_435027713 == '536341288' ~ "Female",
                                                 state_d_706256705 == '654207589' | state_d_435027713 == '654207589' ~ "Male",
                                                 #state_d_706256705 == '830573274' ~ "Intersex or Other", # too small of a count for now, need to combine with unknown 
                                                 state_d_706256705 == '830573274' | state_d_706256705 == '178420302' | state_d_435027713 == '178420302' ~ "Unknown"),
                                 BSL_compl = case_when(d_100767870==353358909 ~ "All Baseline Modules Completed",
                                                       TRUE ~ "One or More Baseline Modules Not Completed"),
                                 Pref_lang=case_when(d_255077064 == 773342525 ~ "Spanish",
                                                     TRUE ~ "English"),
                                 Recruit_Type= case_when(d_512820379==486306141 ~ "Active",
                                                  d_512820379==854703046 ~ "Passive"),
                                 
                                 
                                 qolcomplt = ifelse(d_320303124 == 231311385 ,"Submitted",
                                                    ifelse(d_320303124 == 615768760, "Started",
                                                           ifelse(as.numeric(difftime(Sys.Date(), as.POSIXct(ymd_hms(d_914594314)),
                                                                                      units="days")) < 90, "Not Eligible",
                                                                  ifelse(d_320303124 == 972455046, "Not Started", "Error")))),
                                
                                # RcrtV_Verification_v1r0 = 1 - must be verified
                                # AND RcrtV_VerificationTm_V1R0 LE 08/01/2025 - must have been verified on or before this date
                                # AND HdWd_WdConsent_v1r0 = 0 = and not withdrawn

                                roicomplt = case_when(d_278023676 == 231311385 ~ "Submitted",
                                                      d_278023676 == 615768760 ~ "Started",
                                                      as.Date(d_914594314) > as.Date("2025-08-01") |     # ineligible if verified after August 1 2025
                                                        d_821247024  != "197316935" |                     # ineligible if verification status isn't "verified"
                                                        d_747006172 != "104430631" ~ "Not Eligible",     # ineligible if consent is withdrawn
                                                      d_278023676 == 972455046 ~ "Not Started",
                                                      TRUE ~ "Not Eligible"
                                ),

                                
                                
                                 completion = case_when(d_100767870=="353358909" & 
                                                          (d_878865966=="353358909" | d_684635302=="353358909" | d_167958071=="353358909") ~ "Completed both survey and sample(s)",
                                                        d_100767870=="353358909" ~ "Completed all baseline survey modules 1-4, no baseline samples",
                                                        (d_878865966=="353358909" | d_684635302=="353358909" | 
                                                           d_167958071=="353358909") ~ "Completed any baseline sample, did not complete baseline survey",
                                                        TRUE ~ "Completed neither survey or sample(s)"),
                                 collection = ifelse((d_878865966 == 353358909 | d_167958071 == 353358909 | 
                                                              d_684635302 == 353358909 ), "Any biospecimen Collections","No biospecimen collections"),
                                 provided4 =case_when(d_311580100==353358909 ~ "Full SSN",
                                                     d_914639140==353358909 ~ "Partial SSN",
                                                     TRUE ~ "No SSN"),
                                 ssn_started=case_when(d_126331570==615768760 ~ "Started",
                                                       d_126331570==231311385 ~ "Submitted",
                                                       TRUE ~ "Not Started"),
                                 CES_status = case_when(d_956490759==972455046	~ "Not Started",
                                                        d_956490759==615768760	~ "Started",
                                                        d_956490759==231311385	~ "Submitted",
                                                        TRUE ~ "Not Eligible"),
                                 CSH_status = case_when(d_176068627==231311385	~ "Submitted",
                                                        d_176068627==615768760	~ "Started",
                                                        d_176068627==972455046 & (as.numeric(difftime(Sys.Date(), as.POSIXct(ymd_hms(d_914594314)),units="days")) >269)	~ "Not Started",
                                                        TRUE ~ "Not Eligible"), #not eligible until 270 days after verification
                                 verif_time_diff = as.numeric(difftime(Sys.Date(), as.Date(d_914594314), units="days")),
                                 dhq_status = case_when(d_692560814==789467219 |
                                                          !(as.Date(d_914594314) > "2024-12-01" & verif_time_diff>=180 & d_821247024=="197316935" & d_747006172 == '104430631') ~ "Not Eligible",
                                                        d_692560814==231311385 ~ "Submitted",
                                                        d_692560814==615768760 ~ "Started",
                                                        d_692560814==972455046 ~ "Not Started"),
                                 external_status = case_when(is.na(d_501613780)	~ "Null",
                                                             d_501613780==418049936	~ "Not yet begun",
                                                             d_501613780==269380840	~ "In Progress",
                                                             d_501613780==542659759	~ "Completed"),
                                                             #d_501613780==418049936 | is.na(d_501613780)	~ "Not yet begun"),
                                 external_status = factor(external_status, levels=c("Null","Not yet begun", "In Progress","Completed")),
                                 m1_comp_mins = as.numeric(difftime(as.POSIXct(ymd_hms(d_517311251)), as.POSIXct(ymd_hms(d_205553981)), units="hours"))*60,
                                 m2_comp_mins = as.numeric(difftime(as.POSIXct(ymd_hms(d_832139544)), as.POSIXct(ymd_hms(d_541836531)), units="hours"))*60,
                                 m3_comp_mins = as.numeric(difftime(as.POSIXct(ymd_hms(d_770257102)), as.POSIXct(ymd_hms(d_386488297)), units="hours"))*60,
                                 m4_comp_mins = as.numeric(difftime(as.POSIXct(ymd_hms(d_264644252)), as.POSIXct(ymd_hms(d_452942800)), units="hours"))*60,
                                 dhq_comp_mins = as.numeric(difftime(as.POSIXct(ymd_hms(d_610227793)), as.POSIXct(ymd_hms(d_109610692)), units="hours"))*60,
                                 csh_comp_mins = as.numeric(difftime(as.POSIXct(ymd_hms(d_389890053)), as.POSIXct(ymd_hms(d_609630315)), units="hours"))*60,
                                 roi_comp_mins = as.numeric(difftime(as.POSIXct(ymd_hms(d_543379310)), as.POSIXct(ymd_hms(d_993557295)), units="hours"))*60)

all_data$Site <- factor(all_data$Site, levels=c("Baylor Scott and White","HealthPartners", "Henry Ford","Marshfield","Sanford","UChicago","KP Colorado","KP Georgia", "KP Hawaii","KP Northwest"))
all_data$BL_comp <- factor(all_data$BL_comp, levels=c("All", "2 or 3 Sections", "BOH Only", "None"))
all_data$completion <- factor(all_data$completion, levels=c("Completed both survey and sample(s)", "Completed all baseline survey modules 1-4, no baseline samples", 
                                                  "Completed any baseline sample, did not complete baseline survey","Completed neither survey or sample(s)"))
all_data$process <- factor(all_data$process, levels=c("None", "BOH Section only", "BOH and MRE Sections", "BOH and SAS Sections",  "BOH and LAW Sections", 
                                                      "BOH, MRE, and SAS Sections", "BOH, SAS, and LAW Sections", "BOH, MRE, and LAW Sections", "All"))
all_data$provided4<- factor(all_data$provided4,levels=c("Full SSN", "Partial SSN", "No SSN"))

```


```{r Functions, include=FALSE}


### Regular tbl_cross

create_tbl_cross1 <- function(data,row_var, colm_var, row_or_col_pct, row_name, column_name){
cross__table <- data %>%  
  tbl_cross(
    row = !!sym(row_var),
    col = !!sym(colm_var),
    digits=c(0,2),
    percent = row_or_col_pct,
    label=list(!!sym(row_var) ~ row_name,
               !!sym(colm_var) ~ column_name),
    missing="ifany",
    margin_text="Total") 

#Ops doesn't like the grouped by variables on a different line the column labels
cross_table_df <- as.data.frame(cross__table)[-1, ]
  
}





### a tbl cross where the output should have all row percentages, but the Total column should be a column percentage

create_tbl_cross2 <- function(data, row_var, colm_var, row_or_col_pct, row_name, column_name, margin_text) {
  cross__table <- data %>%
    tbl_cross(
      row = !!sym(row_var),
      col = !!sym(colm_var),
      label = list(!!sym(row_var) ~ row_name,
                   !!sym(colm_var) ~ column_name),
      percent = row_or_col_pct,
      digits = c(0, 2),
      margin_text = margin_text
    )
  
  # Check if table_body exists and has data
  if (!is.null(cross__table[["table_body"]]) && nrow(cross__table[["table_body"]]) > 0) {
    # Need only the total column to be a column percentage
    cross__table[["table_body"]]$stat_0 <- sapply(strsplit(cross__table[["table_body"]]$stat_0, " "), "[", 1)
    
    cross__table_df <- as.data.frame(cross__table)[2:nrow(as.data.frame(cross__table)), ]
    colnames(cross__table_df)[1] <- row_name
    
    # Ensure 'Total Verified Participants' exists before modifying
    if ("Total Verified Participants" %in% colnames(cross__table_df)) {
      cross__table_df$`Total Verified Participants` <- as.numeric(gsub(",", "", cross__table_df$`Total Verified Participants`))
      
      total_participants <- cross__table_df$`Total Verified Participants`
      percentages <- round((total_participants / total_participants[length(total_participants)]) * 100, digits = 2)
      
      cross__table_df$`Total Verified Participants` <- paste0(format(total_participants, big.mark = ","), " (", percentages, "%)")
    }
    
    colnames(cross__table_df)[ncol(cross__table_df)] <- "Total Verified \n Participants"
    return(cross__table_df)
  } else {
    warning("The cross table is empty or missing table_body.")
    return(data.frame()) # Return an empty data frame if table_body is missing
  }
}




```



\newpage
# Baseline Survey

The Baseline Survey is available to Active recruits who enrolled with a valid token/PIN at time of user profile submission. The survey is available to passive recruits and active recruits who enrolled without a valid token/PIN at time of verification.

Starting July 5th, 2022, all four Initial Survey Modules were in MyConnect. In order of how the sections appear on MyConnect, the Initial Survey Sections are:  

BOH= Background and Overall Health (Module 1); available in MyConnect at time of study launch on 07/21/2021.  

LAW= Where you Live and Work (Module 4); available in MyConnect starting 07/05/2022 and at which point all 4 sections of the Baseline Survey became available to participants.

MRE= Medications, Reproductive Health, Exercise, and Sleep (Module 2); available in MyConnect starting 06/10/2022.

SAS= Smoking, Alcohol, and Sun Exposure (Module 3); available in MyConnect starting 06/10/2022.
```{r newTable1, echo=FALSE, warning=FALSE, message=FALSE, results='asis'}

comp_by_site_totals <- create_tbl_cross1(all_data,"Site", "BSL_compl", "row", "Site", " ")

total_rows <- nrow(comp_by_site_totals)
knitr::kable(comp_by_site_totals , 
             caption='Table 1.1. Completion of Initial Surveys by Site', 
             row.names=FALSE,align=c("l","c","c","c"),
             col.names=c("Site", "All Completed", "One or More Not Completed", "Total"),
             booktabs = TRUE) %>%  
  add_indent(seq(1, total_rows - 1))  %>% 
  kable_styling(latex_options = c("scale_down","hold_position")) # %>%  column_spec(3:4, width = "4cm")


```


 
 \newpage
 
```{r Table2, echo=FALSE, warning=FALSE, message=FALSE}

all_srvy_comp_totals <- create_tbl_cross1(all_data,"process", "Recruit_Type", "column", "Sections Submitted", " ")


knitr::kable(all_srvy_comp_totals ,
             col.names=c("Sections Submitted", "Active Verified","Passive Verified", "Total Verified"), 
             caption='Table 1.2. Initial Survey Submission Among Verified Participants \n Stratified by Active and Passive Recruits', 
             row.names=FALSE,align=c("l","c","c","c"), booktabs = TRUE) %>%  
  add_indent(seq(1, nrow(all_srvy_comp_totals) - 1))  %>%
  kable_styling(latex_options = c("scale_down","hold_position")) %>% 
  footnote("All sections were in MyConnect on July 5, 2022. There were 766 verified participants before that date.", 
           general_title = "Note: ", 
           footnote_as_chunk = T)

```


```{r Table3, echo=FALSE, warning=FALSE, message=FALSE}

## Each of these rows are essentially their own table
## Keep row percentage but make into one table

## Baseline Survey Status Counts
calculate_counts <- function(df, column_name, row_label) {
  total_rows <- dim(df)[[1]]
  value_counts <- sapply(c(972455046, 615768760, 231311385), function(value) {
    count <- sum(df[[column_name]] == value)
    formatted_count <- formatC(count, format = "f", big.mark = ",", digits = 0)
    percentage <- round(100 * count / total_rows, 2)
    paste0(formatted_count, " (", percentage, "%)")
  })
  total_label <- paste(formatC(total_rows, format = "f", big.mark = ",", digits = 0), "(100.00%)")
  c(row_label, value_counts, total_label)
}


section_comp <- data.frame(matrix(ncol =5, nrow = 4))


section_comp[1, ] <- calculate_counts(all_data, "d_949302066", "BOH")
section_comp[2, ] <- calculate_counts(all_data, "d_536735468", "MRE")
section_comp[3, ] <- calculate_counts(all_data, "d_976570371", "SAS")
section_comp[4, ] <- calculate_counts(all_data, "d_663265240", "LAW")


colnames(section_comp) <- c("Section", "Not Started", "Started", "Submitted", "Total Verified Participants")


knitr::kable(section_comp, 
             caption='Table 1.3: Initial Survey Section Submission Status Among Verified Participants', 
             col.names=c("Section", "Not Started", "Started", "Submitted", "Total Verified Participants"), 
             row.names=FALSE, align=c("l","c","c","c","c"), booktabs = TRUE) %>% 
  kable_styling(latex_options = c("scale_down","hold_position"))




```






\newpage
\FloatBarrier


```{r Table4.1, echo=FALSE, error=FALSE, message=FALSE, warning=FALSE, results='asis'}

#Time the last Basleine Module was completed
all_data <- all_data %>% group_by(Connect_ID) %>% mutate(last_mod_ts = max(d_832139544, d_770257102, d_264644252)) %>% ungroup()

all_data <- all_data %>% mutate(ver_M1 = as.numeric(difftime(as.POSIXct(ymd_hms(d_517311251)), as.POSIXct(ymd_hms(d_914594314)), units="hours")),
                                ver_M2 = as.numeric(difftime(as.POSIXct(ymd_hms(d_832139544)), as.POSIXct(ymd_hms(d_914594314)), units="hours")),
                                ver_M3 = as.numeric(difftime(as.POSIXct(ymd_hms(d_770257102)), as.POSIXct(ymd_hms(d_914594314)), units="hours")),
                                ver_M4 = as.numeric(difftime(as.POSIXct(ymd_hms(d_264644252)), as.POSIXct(ymd_hms(d_914594314)), units="hours")),
                                ver_last = as.numeric(difftime(as.POSIXct(ymd_hms(last_mod_ts)), as.POSIXct(ymd_hms(d_914594314)), units="hours")),
                                ver_M1_mins=ver_M1*60,
                                ver_M2_mins=ver_M2*60,
                                ver_M3_mins=ver_M3*60,
                                ver_M4_mins=ver_M4*60)


Table4a = all_data %>% group_by(Recruit_Type) %>% filter(d_949302066==231311385) %>% 
  dplyr::summarize('N'=n(),
                   Min = min(ver_M1, na.rm = TRUE),
                   Q1 = quantile(ver_M1, 0.25, na.rm = TRUE),
                   Median = median(ver_M1, na.rm = TRUE),
                   Mean = mean(ver_M1, na.rm = TRUE), 
                   SD= sd(ver_M1, na.rm = TRUE),
                   Q3 = quantile(ver_M1, 0.75, na.rm = TRUE),
                   'Perc.85' = quantile(ver_M1, 0.85, na.rm = TRUE),
                   'Perc.90' = quantile(ver_M1, 0.90, na.rm = TRUE),
                   'Perc.95' = quantile(ver_M1, 0.95, na.rm = TRUE),
                   Max = max(ver_M1, na.rm = TRUE)) 


Table4a2 = all_data %>% filter(d_949302066==231311385) %>% 
  dplyr::summarize('N'=n(),
                   Min = min(ver_M1, na.rm = TRUE),
                   Q1 = quantile(ver_M1, 0.25, na.rm = TRUE),
                   Median = median(ver_M1, na.rm = TRUE),
                   Mean = mean(ver_M1, na.rm = TRUE), 
                   SD= sd(ver_M1, na.rm = TRUE),
                   Q3 = quantile(ver_M1, 0.75, na.rm = TRUE),
                   'Perc.85' = quantile(ver_M1, 0.85, na.rm = TRUE),
                   'Perc.90' = quantile(ver_M1, 0.90, na.rm = TRUE),
                   'Perc.95' = quantile(ver_M1, 0.95, na.rm = TRUE),
                   Max = max(ver_M1, na.rm = TRUE)) 


Table4a1 <- Table4a #need to keep Table4a's first column name consistent to bind it later in the code
names(Table4a1)[1] <- "Recruit Type"





knitr::kable(Table4a1,format.args = list(big.mark = ","),
             caption='Table 1.4.a. Time (in hours) from Verification to BOH Submission \n Stratified by Active and Passive Recruits', 
             row.names=FALSE, align=c("l","c","c","c","c","c","c","c"),digits=2, booktabs = TRUE)%>% 
  kable_styling(latex_options = "scale_down", full_width = FALSE, font_size=8) 


knitr::kable(Table4a2,format.args = list(big.mark = ","),
             caption='Table 1.4.b. Time (in hours) from Verification to BOH Submission for All Participants',
             row.names=FALSE, align=c("l","c","c","c","c","c","c","c"),digits=2, booktabs = TRUE)%>% 
  kable_styling(latex_options = c("scale_down","hold_position")) 
```


```{r Table5, echo=FALSE, error=FALSE, message=FALSE, warning=FALSE}


verif_to_submit <- function(data, filter_column, filter_value, target_column) {
  data %>% 
    filter(!!sym(filter_column) == filter_value) %>% 
    summarize('N' = n(),
              Min = min(!!sym(target_column), na.rm = TRUE),
              Q1 = quantile(!!sym(target_column), 0.25, na.rm = TRUE),
              Median = median(!!sym(target_column), na.rm = TRUE),
              Mean = mean(!!sym(target_column), na.rm = TRUE), 
              SD = sd(!!sym(target_column), na.rm = TRUE),
              Q3 = quantile(!!sym(target_column), 0.75, na.rm = TRUE),
              'Perc.85' = quantile(!!sym(target_column), 0.85, na.rm = TRUE),
              'Perc.90' = quantile(!!sym(target_column), 0.90, na.rm = TRUE),
              'Perc.95' = quantile(!!sym(target_column), 0.95, na.rm = TRUE),
              Max = max(!!sym(target_column), na.rm = TRUE))
}


Table4b <- verif_to_submit(all_data, "d_536735468", 231311385, "ver_M2")
Table4c <- verif_to_submit(all_data, "d_976570371", 231311385, "ver_M3")
Table4d <- verif_to_submit(all_data, "d_663265240", 231311385, "ver_M4")
Table4e <- verif_to_submit(all_data, "d_100767870", 353358909, "ver_last")



### Table4a2 in previous chunk
tb5boh <- as.data.frame(Table4a2)
table4 <- rbind(tb5boh, Table4b, Table4c, Table4d, Table4e)



table4<- table4[, c(1:7, 9, 11)]
table4[,10] <- c("BOH", "MRE", "SAS", "LAW", "All")
table4<- table4[, c(10,1:9)]
colnames(table4)[1] <- "Section"


knitr::kable(table4,format.args = list(big.mark = ","),
             caption='Table 1.5. Time (in hours) from Verification to Initial Survey Module Submission',
             row.names=FALSE, align=c("l","c","c","c","c","c","c","c"),digits=2, booktabs = TRUE)%>% 
  kable_styling(latex_options = c("scale_down","hold_position")) 

```



\FloatBarrier





\newpage



```{r Submission_Minutes,echo=FALSE, error=FALSE, message=FALSE, warning=FALSE}



completing_module <- function(data, start_time, end_time, completion_flag, completion_status, module_name) {
  
  
  data <- data %>%
    filter(!!sym(completion_flag) == completion_status)
  
  
  comp_tm <- as.numeric(difftime(as.POSIXct(ymd_hms(data[[start_time]])), 
                                 as.POSIXct(ymd_hms(data[[end_time]])), 
                                 units = "hours"))
  
  
  data <- data %>%
    mutate(comp_mins = comp_tm * 60,
           time_frame = case_when(comp_mins < 5 ~ "Under 5 minutes",
                                  comp_mins < 10 ~ "5 to 10 minutes",
                                  comp_mins < 15 ~ "10 to 15 minutes",
                                  comp_mins < 20 ~ "15 to 20 minutes",
                                  comp_mins < 30 ~ "20 to 30 minutes",
                                  comp_mins < 45 ~ "30 to 45 minutes",
                                  comp_mins < 60 ~ "45 to 60 minutes",
                                  comp_mins >= 60 ~ "60 minutes+",
                                  is.na(data[[start_time]]) | is.na(data[[end_time]]) ~ "Missing Time Stamp(s)",
                                  start_time>end_time ~ "Start Time after End Time")) #new
  
  data$time_frame <- factor(data$time_frame, levels = c(
    "Under 5 minutes", "5 to 10 minutes", "10 to 15 minutes",
    "15 to 20 minutes", "20 to 30 minutes", "30 to 45 minutes",
    "45 to 60 minutes", "60 minutes+", "Missing Time Stamp(s)",
    "Start Time after End Time"
  ))
  
  #Add a Total Row
  summary_data <- data %>%
    group_by(time_frame) %>%
    summarize(n = n(), percentage = 100 * n / nrow(data)) %>%
    ungroup() %>%
    mutate(cumulative_percentage = cumsum(percentage)) %>%
    select(time_frame, n, percentage, cumulative_percentage)
  
  summary_row <- summary_data %>%
    summarize(n = sum(n), percentage = 100, 
              cumulative_percentage = 100,
              time_frame = "Total")
  
  summary_data <- bind_rows(summary_data, summary_row)
  
  table_summary <- summary_data %>%
    mutate(np = paste0(n, " (", round(percentage, digits = 2), "%)"),
           cumulative_percentage = paste0(round(cumulative_percentage, digits = 2), "%")) %>%
    select(time_frame, np, cumulative_percentage)
  
  knitr::kable(table_summary, 
               caption = paste0('Table ', module_name, ' Section Initial Survey Submission Time \n from Start to Submit for Verified Participants'), 
               col.names = c("Submission Time", "Total Participants", "Cumulative Percentage"), 
               row.names = FALSE, align = c("l", "c"), digits = 1, booktabs = TRUE) %>%  
    add_indent(seq(1, nrow(table_summary) - 1)) %>% 
    kable_styling(latex_options = "scale_down") 
}


table6.1_sum <- completing_module(all_data, "d_517311251", "d_205553981", "d_949302066", 231311385, "1.6.a. BOH")
table6.2_sum <- completing_module(all_data, "d_832139544", "d_541836531", "d_536735468", 231311385, "1.6.b. MRE")
table6.3_sum <- completing_module(all_data, "d_770257102", "d_386488297", "d_976570371", 231311385, "1.6.c. SAS")
table6.4_sum <- completing_module(all_data, "d_264644252", "d_452942800", "d_663265240", 231311385, "1.6.d. LAW")


```


```{r BL_comp_time,echo=FALSE,error=FALSE,message=FALSE,warning=FALSE,results='asis'}
table6.1_sum
table6.2_sum
table6.3_sum
```

\newpage
```{r LAW_comp_time,echo=FALSE,error=FALSE,message=FALSE,warning=FALSE,results='asis'}
table6.4_sum
```



\FloatBarrier

```{r Table7,echo=FALSE,error=FALSE,message=FALSE,warning=FALSE,results='asis'}



start_to_submit <- function(data, filter_column, filter_value, target_column) {
  data %>% 
    filter(!!sym(filter_column) == filter_value) %>% 
    summarize('N' = n(),
              Min = min(!!sym(target_column), na.rm = TRUE),
              Q1 = quantile(!!sym(target_column), 0.25, na.rm = TRUE),
              Median = median(!!sym(target_column), na.rm = TRUE),
              Mean = mean(!!sym(target_column), na.rm = TRUE), 
              SD = sd(!!sym(target_column), na.rm = TRUE),
              Q3 = quantile(!!sym(target_column), 0.75, na.rm = TRUE),
              'Perc.85' = quantile(!!sym(target_column), 0.85, na.rm = TRUE),
              'Perc.90' = quantile(!!sym(target_column), 0.90, na.rm = TRUE),
              'Perc.95' = quantile(!!sym(target_column), 0.95, na.rm = TRUE),
              Max = max(!!sym(target_column), na.rm = TRUE))
}

Table7a <- start_to_submit(all_data, "d_949302066", 231311385, "m1_comp_mins")
Table7b <- start_to_submit(all_data, "d_536735468", 231311385, "m2_comp_mins")
Table7c <- start_to_submit(all_data, "d_976570371", 231311385, "m3_comp_mins")
Table7d <- start_to_submit(all_data, "d_663265240", 231311385, "m4_comp_mins")


Table7 <- rbind(Table7a, Table7b, Table7c, Table7d)


Table7<- Table7[, c(1:7, 9, 11)]
Table7[,10] <- c("BOH", "MRE", "SAS", "LAW")
Table7<- Table7[, c(10,1:9)]
colnames(Table7)[1] <- "Section"


knitr::kable(Table7,format.args = list(big.mark = ","),
             caption='Table 1.7. Time (in minutes) from Start to Submit of Initial Survey Modules',
             row.names=FALSE, align=c("l","c","c","c","c","c","c","c"),digits=2, booktabs = TRUE)%>% 
  kable_styling(latex_options = c("scale_down","hold_position")) 


```








```{r Section8, echo=FALSE, warning = FALSE}



cannot_ver <- data_c %>%  filter(d_821247024==219863910 & d_512820379==486306141) %>%  
  mutate(sect_comp= case_when((d_949302066==231311385 | d_536735468==231311385 | 
                                 d_976570371==231311385 | d_663265240==231311385) ~ "At Least One",
                              TRUE ~ "None"))

Numb5 <- cannot_ver %>% group_by(sect_comp) %>%    dplyr::summarize(n=n(), percentage=100*n/nrow(.))  %>% dplyr::ungroup() %>%  dplyr::select(sect_comp, n, percentage)

Numb5_table <- Numb5 %>% mutate(np = paste0(n, " (", round(percentage, digits=2), "%)")) %>% select(sect_comp, np)

Numb5_table[dim(Numb5_table)[[1]]+1 , ] <- list("Total", paste(sum(Numb5$n), " (100%)"))


knitr::kable(Numb5_table, 
             caption='Table 1.8. Inital Survey Submission Status among Active Recruits who Could Not be Verified', 
             col.names=c("Sections Submitted", "Active Recruits"), 
             row.names=FALSE, align=c("l","c"),digits=1, booktabs = TRUE) %>%  
  add_indent(c(1:2)) %>% 
  kable_styling(latex_options = "scale_down")


```



```{r BL_demographics, echo=FALSE, warning=FALSE, message=FALSE, results='eval'}


BL_by_Sex_df <- create_tbl_cross2(all_data, "sex", "BL_comp", "row", "Sex", "Baseline Survey \n Completion", "Total Verified Participants")

knitr::kable(BL_by_Sex_df, 
             caption='Table 1.9. Initial Survey Completion Rate by Site Defined Sex \n Among Verified Participants',
             row.names=FALSE, align=c("l","c","c","c","c","c"), booktabs = TRUE) %>%
    kable_styling(latex_options = "scale_down") %>%  
    add_indent(seq(1, nrow(BL_by_Sex_df) - 1)) %>%  landscape() %>% 
  footnote(general="Note: Sex defined as the de-identified sex data reported by sites at time of invitation.",
           general_title = "")





BL_by_Age_df <- create_tbl_cross2(all_data, "age", "BL_comp", "row", "Age", "Baseline Survey \n Completion", "Total Verified Participants")

knitr::kable(BL_by_Age_df, 
             caption="Table 1.10. Initial Survey Completion Rate by Site Defined Age \n Among Verified Participants",
             row.names=FALSE, align=c("l","c","c","c","c","c"), booktabs = TRUE) %>%
    kable_styling(latex_options = "scale_down") %>%  
    add_indent(seq(1, nrow(BL_by_Age_df) - 1)) %>%  landscape() %>% 
  footnote(general="Note: Age defined as the de-identified age data reported by sites at time of invitation, not current age at time of survey completion.",
           general_title = "")





BL_by_Race_df <- create_tbl_cross2(all_data, "race", "BL_comp", "row", "Race", "Baseline Survey \n Completion", "Total Verified Participants")

knitr::kable(BL_by_Race_df, 
             caption="Table 1.11. Initial Survey Completion Rate by Site Defined Race \n Among Verified Participants",
             row.names=FALSE, align=c("l","c","c","c","c","c"), booktabs = TRUE) %>%
    kable_styling(latex_options = "scale_down") %>%  
    add_indent(seq(1, nrow(BL_by_Race_df) - 1)) %>%  landscape() %>%
    footnote(general = "Note: Race defined as the de-identified race data reported by sites at time of invitation.",
             general_title = "")



```




\newpage
# SSN Survey
The SSN Baseline Survey was available at time of baseline study launch on 07/21/2021. All verified participants that are not withdrawn are eligible for the survey. Participants can provide either their full (9-digits) or partial (4-digits) SSN in the survey. If a participant chooses to not provide their SSN the survey will still remain on their To Do List in MyConnect until SSN is provided.
\FloatBarrier
```{r SSN, echo=FALSE, warning=FALSE, message=FALSE, results='asis'}


ssn_surv_table <- create_tbl_cross2(all_data, "ssn_started", "provided4", "row", "Submission Status", 
                                    "Proportion of SSN Given", "Total Verified Participants")

knitr::kable(ssn_surv_table, 
             caption='Table 2.1 Proportion of SSN Given by Submission Status of SSN Survey Among Verified Participants',
             row.names=FALSE, align=c("l","c","c","c","c"), booktabs = TRUE) %>%
    kable_styling(latex_options = "scale_down") %>%  
    add_indent(seq(1, nrow(ssn_surv_table) - 1))

```


\newpage
# COVID-19 Survey
The COVID-19 Baseline Survey was available to participants as part of the Biospecimen Survey at time of baseline research biospecimen launch on 06/01/2022. On 07/05/2023 the COVID-related questions were removed from the Biospecimen Survey and split into it's own standalone survey. Participants become eligible for the COVID-19 questions at time of biospecimen donation for participants that are not withdrawn.
\FloatBarrier
```{r COVID_Section, echo=FALSE, warning=FALSE, message=FALSE, results='asis'}


# COVID questions were in the BU and BUM surveys prior to 7/5/2023; Here we only include the stand alone COVID Survey results
  #Need a biospecimen collection to be eligible for survey, collection on or after 7/5/23 to be eligible for the COVID survey


covid <- all_data %>%  
  mutate(COVID_status = case_when(d_220186468==231311385 ~ "Submitted",
                                  d_220186468==615768760 ~ "Started",
                                  d_220186468==972455046 ~ "Not Started",
                                  TRUE ~ "Not Eligible")) %>% 
  filter(COVID_status!="Not Eligible" & (as.Date(d_556788178) >= as.Date("2023-07-05"))) #stand alone survey only

covid_table <- create_tbl_cross1(covid,"Site", "COVID_status", "column", "Site", "Status")

covid_df <- as.data.frame(covid_table)
colnames(covid_df)[5] <- "Total Eligible for \n COVID-19 Survey"

knitr::kable(covid_df, 
             caption='Table 3.1 Baseline COVID Response Rate',
             row.names=FALSE, align=c("l","c","c","c","c","c"), booktabs = TRUE, escape = FALSE) %>%
    kable_styling(latex_options = "scale_down", full_width = FALSE) %>% 
  footnote( "Note: This table includes all participants who are eligible for the stand alone COVID-19 Survey. Eligibility is defined as having donated a biospecimen collection on or after July 5th, 2023.", 
            general_title = "",
            footnote_as_chunk = TRUE, 
            escape = FALSE, 
            threeparttable = TRUE)




  

Covid_time = all_data %>% 
  filter(d_220186468==231311385 & (as.Date(d_556788178) >= as.Date("2023-07-05"))) %>% 
  mutate(covid_start_stop = as.numeric(difftime(as.POSIXct(ymd_hms(d_784810139)), as.POSIXct(ymd_hms(d_268176409)), units="mins")), 
         timeframe = case_when(covid_start_stop<5 ~ "Under 5 Minutes",
                       covid_start_stop<10 ~ "5-10 Minutes",
                       covid_start_stop<15 ~ "10-15 Minutes",
                       covid_start_stop<20 ~ "15-20 Minutes",
                       covid_start_stop<30 ~ "20-30 Minutes",
                       covid_start_stop>=30 ~ "30+ Minutes",
                       is.na(d_784810139) | is.na(d_268176409) ~ "Missing Time Stamp(s)"),
timeframe = factor(timeframe, levels=c("Under 5 Minutes", "5-10 Minutes", "10-15 Minutes", 
                                         "15-20 Minutes", "20-30 Minutes", "30+ Minutes", "Missing Time Stamp(s)")))  %>% 
    group_by(timeframe) %>% tally() %>% 
    mutate(Percentage = (n / sum(n)) * 100)



summary_row <- data.frame(timeframe = "Total Submitted COVID-19 Surveys",
                          n = sum(Covid_time$n),
                          Percentage = 100)


Covid_time <- rbind(Covid_time, summary_row) %>%
    mutate(N_percent = paste0(formatC(n, big.mark = ",", format = "d"), 
                              " (", round(Percentage, digits = 1), "%)"),
           Cumulative_Percentage = round(cumsum(Percentage), digits=2))
Covid_time$Cumulative_Percentage[nrow(Covid_time)] <- 100

Covid_time <- Covid_time %>% 
    select(timeframe, N_percent, Cumulative_Percentage) %>%
    dplyr::rename(`Completion Time` = timeframe, `N%` = N_percent,
           'Cumulative Percentage' = Cumulative_Percentage)


knitr::kable(Covid_time, 
             caption='Table 3.2 Baseline COVID Survey Completion Length (in minutes) among Submitted COVID-19 Surveys',
             row.names=FALSE, align=c("l","c","c"), booktabs = TRUE, escape = FALSE) %>%
  add_indent(c(1:(nrow(Covid_time)-1))) %>% 
    kable_styling(latex_options = "scale_down", full_width = FALSE)  %>% 
  footnote("To determine the length of COVID-19 Survey questions, only those who completed the stand alone COVID-19 Survey were included in this table. Those that completed the COVID-19 survey questions within the baseline biospecimen survey were not included.",
           general_title = "",
           footnote_as_chunk = TRUE, 
           escape = FALSE, 
           threeparttable = TRUE)

```



\newpage
\FloatBarrier
# 3-Month Quality of Life Survey
The 3-Month Quality of Life Follow Up Survey is the PROMIS-29 survey. It is available to all verified participants that are not withdrawn at 3-months post-verification. The survey was released to prospective participants (verified on or after 12/01/2023) on 03/01/2024. On 08/29/2024 the survey was released to the backlog participants (verified before 12/01/2023).
```{r Table11s, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}



####### ALL 
QOL_comp_elg <- all_data %>% filter(qolcomplt!="Not Eligible") %>% 
  mutate(qolcomplt = factor(qolcomplt, levels=c("Not Started", "Started", "Submitted"))) %>% 
  select(Site, qolcomplt) %>% dplyr::arrange(Site,qolcomplt) %>% 
  tbl_cross(
  row = Site,
  col = qolcomplt,
  label = list(qolcomplt ~ "Survey Completion",Site~"Site"),
  percent = "row",
  digits=c(0,2),
  margin_text="Total QOL Eligible Participants") 

QOL_comp_elg[["table_body"]]$stat_0 <- sapply(strsplit(QOL_comp_elg[["table_body"]]$stat_0," "),"[",1)

QOL_comp_elg <- QOL_comp_elg %>%
  modify_header(stat_0 = "Total QOL Eligible \n Participants") %>%
  modify_caption("Table 4.1. Completion of 3-Month Quality of Life Survey Among Eligible Participants") %>%
  as_kable_extra(escape = FALSE, addtl_fmt = TRUE)

 
QOL_comp_elg %>% kable_styling(latex_options = c("scale_down","hold_position"))




##### verified on or after 12/1/23

QOL_comp_elg_after <- all_data %>% filter(qolcomplt!="Not Eligible" & as.Date(d_914594314) >= "2023-12-01") %>% 
  mutate(qolcomplt = factor(qolcomplt, levels=c("Not Started", "Started", "Submitted"))) %>% 
  select(Site, qolcomplt) %>% dplyr::arrange(Site,qolcomplt) %>% 
  tbl_cross(
  row = Site,
  col = qolcomplt,
  label = list(qolcomplt ~ "Survey Completion",Site~"Site"),
  percent = "row",
  digits=c(0,2),
  margin_text="Total QOL Eligible Participants") 

QOL_comp_elg_after[["table_body"]]$stat_0 <- sapply(strsplit(QOL_comp_elg_after[["table_body"]]$stat_0," "),"[",1)

 QOL_comp_elg_after <- QOL_comp_elg_after %>%
  modify_header(stat_0 = "Total QOL Eligible \n Participants") %>%
  modify_caption("Table 4.1.a. Completion of 3-Month Quality of Life Survey among Eligible participants Verified on or after December 1, 2023") %>%
  as_kable_extra(escape = FALSE, addtl_fmt = TRUE)

QOL_comp_elg_after %>% kable_styling(latex_options = c("scale_down","hold_position")) 





###### verified before 12/1/23
QOL_comp_elg_before <- all_data %>% filter(qolcomplt!="Not Eligible" & as.Date(d_914594314) < "2023-12-01") %>% 
  mutate(qolcomplt = factor(qolcomplt, levels=c("Not Started", "Started", "Submitted"))) %>% 
  select(Site, qolcomplt) %>% dplyr::arrange(Site,qolcomplt) %>% 
  tbl_cross(
  row = Site,
  col = qolcomplt,
  label = list(qolcomplt ~ "Survey Completion",Site~"Site"),
  percent = "row",
  digits=c(0,2),
  margin_text="Total QOL Eligible Participants") 

QOL_comp_elg_before[["table_body"]]$stat_0 <- sapply(strsplit(QOL_comp_elg_before[["table_body"]]$stat_0," "),"[",1)

QOL_comp_elg_before <- QOL_comp_elg_before %>%
  modify_header(stat_0 = "Total QOL Eligible \n Participants") %>%
  modify_caption("Table 4.1.b. Completion of 3-Month Quality of Life Survey among Eligible Participants Verified prior to December 1, 2023") %>%
  as_kable_extra(escape = FALSE, addtl_fmt = TRUE)


QOL_comp_elg_before %>% kable_styling(latex_options = c("scale_down","hold_position")) %>% 
  footnote(general = 'The QOL "PROMIS" or "QOL" survey was released to all those verified prior to December 1, 2023 on August 30, 2024.',general_title = "Note: ", footnote_as_chunk = T)

```


\newpage
\FloatBarrier

```{r Table12s, echo=FALSE, warning=FALSE, message=FALSE, results='asis'}

###### ALL ########
QOL_comp_BL_all <- all_data %>%  filter(qolcomplt!="Not Eligible") 

QOL_comp_BL <- create_tbl_cross2(QOL_comp_BL_all, "completion", "qolcomplt", "row", "Completion", "QOL Completion", "Total QOL Eligible Participants")
colnames(QOL_comp_BL)[5] <- "Total QOL Eligible \n Participants"


knitr::kable(QOL_comp_BL, 
             caption='Table 4.2. Completion of 3-Month Quality of Life Survey by Baseline Data Completeness',
             row.names=FALSE, align=c("l","c","c","c","c"), booktabs = TRUE) %>%
    kable_styling(latex_options = "scale_down") %>%  
    add_indent(seq(1, nrow(QOL_comp_BL) - 1)) %>%  landscape()




###### On or After 12/1/23 ########

QOL_comp_after <- all_data %>% filter(as.Date(d_914594314) >= "2023-12-01" & qolcomplt!="Not Eligible")  

QOL_comp_BL_after <- create_tbl_cross2(QOL_comp_after, "completion", "qolcomplt", "row", "Completion", "QOL Completion", "Total QOL Eligible Participants")

colnames(QOL_comp_BL_after)[5] <- "Total QOL Eligible \n Participants"

knitr::kable(QOL_comp_BL_after, 
             caption='Table 4.2.a. Completion of 3-Month Quality of Life Survey by Baseline Data Completeness among Eligible Participants Verified on or after December 1, 2023',
             row.names=FALSE, align=c("l","c","c","c","c"), booktabs = TRUE) %>%
    kable_styling(latex_options = "scale_down") %>%  
    add_indent(seq(1, nrow(QOL_comp_BL_after) - 1)) %>%  landscape()



###### Before 12/1/23 ########

QOL_comp_after <- all_data %>% filter(as.Date(d_914594314) < "2023-12-01" & qolcomplt!="Not Eligible")  

QOL_comp_BL_before <- create_tbl_cross2(QOL_comp_after, "completion", "qolcomplt", "row", "Completion", "QOL Completion", "Total QOL Eligible Participants")

colnames(QOL_comp_BL_before)[5] <- "Total QOL Eligible \n Participants"
knitr::kable(QOL_comp_BL_before, 
             caption='Table 4.2.b. Completion of 3-Month Quality of Life Survey by Baseline Data Completeness among Eligible Participants Verified on before December 1, 2023',
             row.names=FALSE, align=c("l","c","c","c","c"), booktabs = TRUE) %>%
    kable_styling(latex_options = "scale_down") %>%  
    add_indent(seq(1, nrow(QOL_comp_BL_before) - 1)) %>%  landscape()


```





```{r QOL_BySex_ByAge, echo=FALSE, warning=FALSE, message=FALSE, results='asis'}


Comp_by_Sex <- all_data %>% filter(qolcomplt!="Not Eligible") %>% 
  mutate(qolcomplt = factor(qolcomplt, levels=c("Not Started", "Started", "Submitted"))) %>% 
  select(sex, qolcomplt) %>% dplyr::arrange(sex,qolcomplt) %>% 
  tbl_cross(
  row = sex,
  col = qolcomplt,
  label = list(qolcomplt ~ "Survey Completion",sex~"Sex"),
  percent = "row",
  digits=c(0,2),
  margin_text="Total QOL Eligible Participants") 


Comp_by_Sex_table <- Comp_by_Sex %>%
  modify_header(stat_0 = "Total QOL Eligible \n Participants") %>%
  modify_caption("Table 4.3. 3-Month Quality of Life Survey Completion Rate by Site Defined Sex \n Among Eligible Participants") %>%
  as_kable_extra(escape = FALSE, addtl_fmt = TRUE) %>% kable_styling(latex_options = c("scale_down","hold_position"))  

add_footnote(Comp_by_Sex_table, "Note: Sex defined as the de-identified sex data reported by sites at time of invitation.", 
             notation = "none")





Comp_by_Age <- all_data %>% filter(qolcomplt!="Not Eligible") %>% 
  mutate(qolcomplt = factor(qolcomplt, levels=c("Not Started", "Started", "Submitted"))) %>% 
  select(age, qolcomplt) %>% dplyr::arrange(age,qolcomplt) %>% 
  tbl_cross(
  row = age,
  col = qolcomplt,
  label = list(qolcomplt ~ "Survey Completion",age~"Age"),
  percent = "row",
  digits=c(0,2),
  margin_text="Total QOL Eligible Participants") 


Comp_by_Age <- Comp_by_Age %>%
  modify_header(stat_0 = "Total QOL Eligible \n Participants") %>%
  modify_caption("Table 4.4. 3-Month Quality of Life Survey Completion Rate by Age \n Among Eligible Participants") %>%
  as_kable_extra(escape = FALSE, addtl_fmt = TRUE)  %>% kable_styling(latex_options = c("scale_down","hold_position")) 

add_footnote(Comp_by_Age, "Note: Age defined as the de-identified age data reported by sites at time of invitation, not current age at time of survey completion.", 
             notation="none")


```



```{r merge1, include=FALSE, warning=FALSE}


### Pulling in Module 1 completion to get participant defined race for the next few tables



recr_M1 <- bq_project_query(project, query="SELECT token,Connect_ID, d_821247024, d_914594314,  d_827220437,d_512820379, d_255077064,
                            d_949302066 , d_517311251  FROM  `nih-nci-dceg-connect-prod-6d04.FlatConnect.participants` WHERE  d_821247024='197316935' and (d_512820379='486306141' OR d_512820379='854703046')")
recr_m1 <- bq_table_download(recr_M1,bigint = "integer64",n_max = Inf, page_size = 10000)
cnames <- names(recr_m1)
# Check that it doesn't match any non-number
numbers_only <- function(x) !grepl("\\D", x)
# to check variables in recr_noinact_wl1
for (i in 1: length(cnames)){
  varname <- cnames[i]
  var<-pull(recr_m1,varname)
  recr_m1[,cnames[i]] <- ifelse(numbers_only(var), as.numeric(as.character(var)), var)
}


####### Handling participants that somehow completed both Mod1 version 1 and Mod1 version 2

sql_M1_1 <- bq_project_query(project, query="SELECT Connect_ID, D_384191091_D_384191091_D_583826374, D_384191091_D_384191091_D_636411467, 
                             D_384191091_D_384191091_D_458435048, D_384191091_D_384191091_D_706998638, D_384191091_D_384191091_D_973565052, 
                             D_384191091_D_384191091_D_586825330, D_384191091_D_384191091_D_412790539, D_384191091_D_384191091_D_807835037,
                             D_384191091_D_747350323,D_384191091_D_384191091_D_746038746, d_784119588
                             FROM `nih-nci-dceg-connect-prod-6d04.FlatConnect.module1_v1` where Connect_ID is not null")
sql_M1_2 <- bq_project_query(project, query="SELECT Connect_ID, D_384191091_D_384191091_D_583826374 ,D_384191091_D_384191091_D_636411467, 
                             D_384191091_D_384191091_D_458435048, D_384191091_D_384191091_D_706998638, D_384191091_D_384191091_D_973565052,
                             D_384191091_D_384191091_D_586825330,D_384191091_D_384191091_D_412790539,D_384191091_D_384191091_D_807835037,
                             D_384191091_D_747350323,D_384191091_D_384191091_D_746038746, d_784119588
                             FROM `nih-nci-dceg-connect-prod-6d04.FlatConnect.module1_v2` where Connect_ID is not null")


M1_V1 <- bq_table_download(sql_M1_1, bigint = "integer64")
M1_V2 <- bq_table_download(sql_M1_2, bigint = "integer64")

# Select matching column names
M1_V1_vars <- colnames(M1_V1)
M1_V2_vars <- colnames(M1_V2)
common_vars <- intersect(M1_V1_vars, M1_V2_vars)

# Subset to common columns
M1_V1_common <- M1_V1[, common_vars]
M1_V2_common <- M1_V2[, common_vars]

# Add version indicator
M1_V1_common$version <- 1
M1_V2_common$version <- 2

# Identify columns with mismatched types
mismatched_cols <- names(M1_V1_common)[sapply(names(M1_V1_common), function(col) {
  class(M1_V1_common[[col]]) != class(M1_V2_common[[col]])
})]

# Convert mismatched columns to character for consistency
M1_V1_common <- M1_V1_common %>%
  mutate(across(all_of(mismatched_cols), as.character))
M1_V2_common <- M1_V2_common %>%
  mutate(across(all_of(mismatched_cols), as.character))

# Combine both versions for participants who completed both
M1_common <- bind_rows(M1_V1_common, M1_V2_common) %>%
  arrange(Connect_ID, desc(version))

# For columns unique to each version
V1_only_vars <- setdiff(M1_V1_vars, common_vars)
V2_only_vars <- setdiff(M1_V2_vars, common_vars)

# Subset each version for unique columns and add version indicator
m1_v1_only <- M1_V1[, c("Connect_ID", V1_only_vars)] %>%
  mutate(version = 1)
m1_v2_only <- M1_V2[, c("Connect_ID", V2_only_vars)] %>%
  mutate(version = 2)

# Combine the unique and common data
m1_common_v1 <- left_join(M1_common, m1_v1_only, by = c("Connect_ID", "version"))
m1_combined_v1v2 <- left_join(m1_common_v1, m1_v2_only, by = c("Connect_ID", "version"))

# Filter for complete cases where specific completion criteria are met
m1_complete <- m1_combined_v1v2 %>%
  filter(Connect_ID %in% recr_m1$Connect_ID[recr_m1$d_949302066 == 231311385]) %>%
  arrange(desc(version))

# Remove duplicates, keeping only the most recent version for each Connect_ID
m1_complete_nodup <- m1_complete[!duplicated(m1_complete$Connect_ID),]

m1_complete_nodup$Connect_ID <- as.numeric(m1_complete_nodup$Connect_ID)



all_data$Connect_ID <- as.numeric(all_data$Connect_ID)


m1_comp_df= left_join(m1_complete_nodup, all_data, by="Connect_ID")
dim(m1_comp_df)


m1_comp <- as_tibble(m1_comp_df)


knitr::opts_chunk$set(comment = NA)

```



```{r Race, warning=FALSE, echo=FALSE, message=FALSE}


race_columns <- c("D_384191091_D_384191091_D_583826374", 
                  "D_384191091_D_384191091_D_636411467",
                  "D_384191091_D_384191091_D_458435048",
                  "D_384191091_D_384191091_D_706998638",
                  "D_384191091_D_384191091_D_973565052",
                  "D_384191091_D_384191091_D_586825330",
                  "D_384191091_D_384191091_D_412790539",
                  "D_384191091_D_384191091_D_807835037")

# All data is currently string values, need to convert "1" and "0" to 1 and 0 to be summarized
m1_comp[race_columns] <- lapply(m1_comp[race_columns], as.numeric)

m1_comp$multi_racial <- ifelse(rowSums(m1_comp[race_columns], na.rm = TRUE) > 1, 1, 0)

m1_comp <- m1_comp %>%  
  mutate(race = case_when(
    multi_racial == 1 ~ "Multi-Racial",
    D_384191091_D_384191091_D_583826374 == 1 ~ "American Indian or Native American",
    D_384191091_D_384191091_D_636411467 == 1 ~ "Asian/Asian American",
    D_384191091_D_384191091_D_458435048 == 1 ~ "Black, African American, or African",
    D_384191091_D_384191091_D_706998638 == 1 ~ "Hispanic, Latino, or Spanish",
    D_384191091_D_384191091_D_973565052 == 1 ~ "Middle Eastern or North African",
    D_384191091_D_384191091_D_586825330 == 1 ~ "Hawaiian or Pacific Islander",
    D_384191091_D_384191091_D_412790539 == 1 ~ "White",
    (D_384191091_D_384191091_D_807835037 == 1 | !is.na(D_384191091_D_747350323)) ~ "Other",
    D_384191091_D_384191091_D_746038746==1 ~ "Prefer Not to Answer",
    TRUE ~ "Skipped this question"
  ))


```




```{r QOL_By_Race, echo=FALSE, warning=FALSE, message=FALSE, results='asis'}


Comp_by_race <- m1_comp %>% filter(qolcomplt!="Not Eligible") %>% 
  mutate(qolcomplt = factor(qolcomplt, levels=c("Not Started", "Started", "Submitted"))) %>% 
  select(race, qolcomplt) %>% dplyr::arrange(race,qolcomplt) %>% 
  tbl_cross(
  row = race,
  col = qolcomplt,
  label = list(qolcomplt ~ "Survey Completion",race~"Race"),
  percent = "row",
  digits=c(0,2),
  margin_text="Total QOL Eligible Participants") 


Comp_by_race <- Comp_by_race %>%
  modify_header(stat_0 = "Total QOL Eligible \n Participants") %>%
  modify_caption("Table 4.5. 3-Month Quality of Life Survey Completion Rate by Race \n Among Eligible Participants") %>%
  as_kable_extra(escape = FALSE, addtl_fmt = TRUE) %>% kable_styling(latex_options = c("scale_down","hold_position"))

reduced <- all_data %>% filter(d_949302066 != 231311385 & qolcomplt!="Not Eligible") # Those who are eligible for PROMIS but didn't complete mod1 yet

add_footnote(Comp_by_race, paste0('Note: In order to determine race, Module 1 must first be completed. There are ', dim(reduced)[[1]] , ' QOL eligible participants that have either not started or not finished Module 1.'),
             notation="none")


```


```{r QOL_By_SiteRace, echo=FALSE, error=FALSE, message=FALSE, warning=FALSE}

QOL_by_race <- all_data %>% filter(qolcomplt!="Not Eligible") 

QOL_by_race_df <- create_tbl_cross2(QOL_by_race, "race", "qolcomplt", "row", "Race", "3-Month Quality of Life \n Survey Completion", "Total Verified Participants")

knitr::kable(QOL_by_race_df, 
             caption="Table 4.5.a 3-Month Quality of Life Survey Completion Rate by Site Defined Race \n Among Verified Participants",
             row.names=FALSE, align=c("l","c","c","c","c","c"), booktabs = TRUE) %>%
    kable_styling(latex_options = "scale_down") %>%  
    add_indent(seq(1, nrow(BL_by_Race_df) - 1)) %>%  landscape() %>%
    footnote(general = "Note: Race defined as the de-identified race data reported by sites at time of invitation.",
             general_title = "")

```


```{r QOL_By_Race_And_Sex, echo=FALSE, warning=FALSE, message=FALSE, results='asis'}

m1_comp = m1_comp %>%  mutate(sex_race= case_when(sex=="Female" & multi_racial==1 ~ "Female: Multi-Racial",
                                            sex=="Female" & D_384191091_D_384191091_D_583826374==1 ~ "Female: American Indian or Native American",
                                            sex=="Female" & D_384191091_D_384191091_D_636411467==1 ~ "Female: Asian/Asian American",
                                            sex=="Female" & D_384191091_D_384191091_D_458435048==1 ~ "Female: Black, African American, or African",
                                            sex=="Female" & D_384191091_D_384191091_D_706998638==1 ~ "Female: Hispanic, Latino, or Spanish",
                                            sex=="Female" & D_384191091_D_384191091_D_973565052==1 ~ "Female: Middle Eastern or North African",
                                            sex=="Female" & D_384191091_D_384191091_D_586825330==1 ~ "Female: Hawaiian or Pacific Islander",
                                            sex=="Female" & D_384191091_D_384191091_D_412790539==1 ~ "Female: White",
                                            sex=="Female" & (D_384191091_D_384191091_D_807835037==1 | !is.na(D_384191091_D_747350323)) ~ "Female: Other",
                                            sex=="Female" & D_384191091_D_384191091_D_746038746==1 ~ "Female: Prefer Not to Answer",
                                            
                                            sex=="Male" & multi_racial==1 ~ "Male: Multi-Racial",
                                            sex=="Male" & D_384191091_D_384191091_D_583826374==1 ~ "Male: American Indian or Native American",
                                            sex=="Male" & D_384191091_D_384191091_D_636411467==1 ~ "Male: Asian/Asian American",
                                            sex=="Male" & D_384191091_D_384191091_D_458435048==1 ~ "Male: Black, African American, or African",
                                            sex=="Male" & D_384191091_D_384191091_D_706998638==1 ~ "Male: Hispanic, Latino, or Spanish",
                                            sex=="Male" & D_384191091_D_384191091_D_973565052==1 ~ "Male: Middle Eastern or North African",
                                            sex=="Male" & D_384191091_D_384191091_D_586825330==1 ~ "Male: Hawaiian or Pacific Islander",
                                            sex=="Male" & D_384191091_D_384191091_D_412790539==1 ~ "Male: White",
                                            sex=="Male" & (D_384191091_D_384191091_D_807835037==1 | !is.na(D_384191091_D_747350323)) ~ "Male: Other",
                                            sex=="Male" & D_384191091_D_384191091_D_746038746==1 ~ "Male: Prefer Not to Answer",
                                            
                                            sex=="Unknown" & multi_racial==1 ~ "Unknown: Multi-Racial",
                                            sex=="Unknown" & D_384191091_D_384191091_D_583826374==1 ~ "Unknown: American Indian or Native American",
                                            sex=="Unknown" & D_384191091_D_384191091_D_636411467==1 ~ "Unknown: Asian/Asian American",
                                            sex=="Unknown" & D_384191091_D_384191091_D_458435048==1 ~ "Unknown: Black, African American, or African",
                                            sex=="Unknown" & D_384191091_D_384191091_D_706998638==1 ~ "Unknown: Hispanic, Latino, or Spanish",
                                            sex=="Unknown" & D_384191091_D_384191091_D_973565052==1 ~ "Unknown: Middle Eastern or North African",
                                            sex=="Unknown" & D_384191091_D_384191091_D_586825330==1 ~ "Unknown: Hawaiian or Pacific Islander",
                                            sex=="Unknown" & D_384191091_D_384191091_D_412790539==1 ~ "Unknown: White",
                                            sex=="Unknown" & (D_384191091_D_384191091_D_807835037==1 | !is.na(D_384191091_D_747350323)) ~ "Unknown: Other",
                                            sex=="Unknown" & D_384191091_D_384191091_D_746038746==1 ~ "Unknown: Prefer Not to Answer",
                                                     TRUE  ~ "Skipped this question"))

Comp_by_sex_race <- m1_comp %>% filter(qolcomplt!="Not Eligible") %>% 
  mutate(qolcomplt = factor(qolcomplt, levels=c("Not Started", "Started", "Submitted"))) %>% 
  select(sex_race, qolcomplt) %>% dplyr::arrange(sex_race,qolcomplt) %>% 
  tbl_cross(
  row = sex_race,
  col = qolcomplt,
  label = list(qolcomplt ~ "Survey Completion",sex_race~"Sex and Race"),
  percent = "row",
  digits=c(0,2),
  margin_text="Total QOL Eligible Participants") 


Comp_by_sex_race <- Comp_by_sex_race %>%
  modify_header(stat_0 = "Total QOL Eligible \n Participants") %>%
  modify_caption("Table 4.6. 3-Month Quality of Life Survey Completion Rate by Sex and Race \n Among Eligible Participants") %>%
  as_kable_extra(escape = FALSE, addtl_fmt = TRUE)

reduced <- all_data %>% filter(d_949302066 != 231311385 & qolcomplt!="Not Eligible") # Those who are eligible for PROMIS but didn't complete mod1 yet

Comp_by_sex_race %>% kable_styling(latex_options = c("scale_down","hold_position")) %>% 
  footnote(general = paste0('In order to determine race, Module 1 must first be completed. There are ', dim(reduced)[[1]] , ' QOL eligible participants that have either not started or not finished Module 1.'),general_title = "Note: ", footnote_as_chunk = T)


```


```{r QOL_By_Demographic, echo=FALSE, warning=FALSE, message=FALSE, results='asis'}

m1_comp <- m1_comp %>%
  mutate(
    "White Women" = if_else(race == "White" & sex == "Female", 1, 0),
    "Black Men" = if_else(race == "Black, African American, or African" & sex == "Male", 1, 0),
    "Women Under 45" = if_else((age == "35-39" | age == "40-45") & sex == "Female", 1, 0),
    "Women Over 45" = if_else((age == "46-50" | age == "51-55" | age == "56-60" | age == "61-65" | age == "66-70") & sex == "Female", 1, 0),
    "Men Under 45" = if_else((age == "35-39" | age == "40-45") & sex == "Male", 1, 0),
    "Men Over 45" = if_else((age == "46-50" | age == "51-55" | age == "56-60" | age == "61-65" | age == "66-70") & sex == "Male", 1, 0)
  )

# Can be in more then one category
all_data_long <- m1_comp %>%
  pivot_longer(cols = c("White Women", "Black Men", "Women Under 45", "Women Over 45", "Men Under 45", "Men Over 45"),
               names_to = "Demographic_Group", values_to = "Flag") %>%
  filter(Flag == 1)  # Keep only rows where participants are in one or more of these demographics


Comp_by_Demographic <- all_data_long %>% 
  filter(qolcomplt != "Not Eligible") %>%
  mutate(qolcomplt = factor(qolcomplt, levels = c("Not Started", "Started", "Submitted")),
         Demographic_Group = factor(Demographic_Group, levels=c("White Women","Black Men","Women Under 45","Women Over 45","Men Under 45","Men Over 45"))) %>%
  select(Demographic_Group, qolcomplt) %>%
  tbl_cross(
    row = Demographic_Group,
    col = qolcomplt,
    label = list(qolcomplt ~ "Survey Completion", Demographic_Group ~ "Demographic"),
    percent = "row",
    digits = c(0, 2),
    margin_text = "Total"
  )


Comp_by_Demographic <- Comp_by_Demographic %>%
  modify_header(stat_0 = "Total") %>%
  modify_caption("Table 4.7. 3-Month Quality of Life Survey Completion Rate \n by Demographic Among Eligible Participants") %>%
  as_kable_extra(escape = FALSE, addtl_fmt = TRUE)

# Style the table output
Comp_by_Demographic %>% kable_styling(latex_options = c("scale_down", "hold_position"))  %>% 
  footnote(general = "Participants may be counted more then once in these categories.",general_title = "Note: ", footnote_as_chunk = T)


```

\FloatBarrier
```{r QOL_start_stop, echo=FALSE, warning=FALSE, message=FALSE}

##### Back to wanting all participants, whether or not they finished Module 1. So switching back to all_data df


QOL_time <- all_data %>% 
  filter(qolcomplt=="Submitted") %>%
  mutate(compTM_qol = as.numeric(difftime(as.POSIXct(ymd_hms(d_843688458)), as.POSIXct(ymd_hms(d_870643066)), units="mins")),
         permission = case_when(compTM_qol<5 ~ "Under 5 Minutes",
                                compTM_qol<10 ~ "5-10 Minutes",
                                compTM_qol<15 ~ "10-15 Minutes",
                                compTM_qol<20 ~ "15-20 Minutes",
                                compTM_qol<30 ~ "20-30 Minutes",
                                compTM_qol>=30 ~ "30+ Minutes"),
         permission = factor(permission, levels=c("Under 5 Minutes", "5-10 Minutes", "10-15 Minutes", 
                                                   "15-20 Minutes", "20-30 Minutes", "30+ Minutes")))  %>% 
    group_by(permission) %>% tally() %>% 
  mutate(Percentage = (n / sum(n)) * 100)



summary_row <- data.frame(permission = "Total Submitted QOL Survey",
                          n = sum(QOL_time$n),
                          Percentage = 100)


QOL_TM <- rbind(QOL_time, summary_row) %>%
  mutate(N_percent = paste0(formatC(n, big.mark = ",", format = "d"), 
                            " (", round(Percentage, digits = 1), "%)"),
         Cumulative_Percentage = round(cumsum(Percentage), digits=2))
QOL_TM$Cumulative_Percentage[nrow(QOL_TM)] <- 100

QOL_TM <- QOL_TM %>% 
  select(permission, N_percent, Cumulative_Percentage) %>%
  dplyr::rename(`Completion Time` = permission, `N%` = N_percent,
         'Cumulative Percentage' = Cumulative_Percentage)


knitr::kable(QOL_TM, #format.args = list(big.mark = ","),
             caption = 'Table 4.8. 3-Month Quality of Life Survey Completion Time from Start to Submit \n Among Eligible Participants That Submitted the Survey', 
             booktabs=T, linesep = "", row.names=FALSE, align=c("l", "c", "c")) %>% 
  add_indent(c(1:(nrow(QOL_TM)-1))) %>%  
  kable_styling(latex_options = "scale_down") #c("scale_down","hold_position"))

```


```{r Table14, echo=FALSE, warning=FALSE, message=FALSE}




## Time from QOL trigger to submission of QOL survey
# category= 3mo QOL Survey Reminders attempt=1st contact notification_time will be used in place of FIRST_QOL_REMINDER

trig_qol <- bq_project_query(project,
query="SELECT distinct(token), notification_time FROM `nih-nci-dceg-connect-prod-6d04.FlatConnect.notifications`
where category='3mo QOL Survey Reminders' and attempt='1st contact'")
trigger <- bigrquery::bq_table_download(trig_qol,bigint = "integer64")


trigger_time <- left_join(all_data, trigger, by="token")


## Those verified before 12/1/2023 were notified in batches that there's a new survey. New participants become eligible after 90 days  
trigger_time <- trigger_time %>%
  mutate(trig = case_when(d_914594314 <= as.Date("2023-12-01") ~ ymd_hms(notification_time),
                          TRUE ~ ymd_hms(d_914594314) + days(90)))

trig_time<- trigger_time %>%  filter(qolcomplt=="Submitted") %>%
  mutate(trigTM_qol = as.numeric(difftime(as.POSIXct(ymd_hms(d_843688458)), as.POSIXct(ymd_hms(trig)), units="days")))

Trig_table = trig_time %>%
  dplyr::summarize('N'=n(),
                   Min = round(min(trigTM_qol, na.rm = TRUE), digits=2),
                   Q1 = round(quantile(trigTM_qol, 0.25, na.rm = TRUE), digits=2),
                   Median = round(median(trigTM_qol, na.rm = TRUE), digits=2),
                   Mean = round(mean(trigTM_qol, na.rm = TRUE),  digits=2),
                   SD= round(sd(trigTM_qol, na.rm = TRUE), digits=2),
                   Q3 = round(quantile(trigTM_qol, 0.75, na.rm = TRUE), digits=2),
                   'Perc.90' = round(quantile(trigTM_qol, 0.90, na.rm = TRUE), digits=2),
                   Max = round(max(trigTM_qol, na.rm = TRUE), digits=2))

knitr::kable(Trig_table, 
             caption = 'Table 4.9. 3-Month Quality of Life Survey Completion from Trigger to Submit for \n Verified Participants, in Days', 
             row.names=FALSE, format.args = list(big.mark = ","), linesep = "", 
             booktabs = T, align=c("l", "c", "c", "c", "c", "c", "c", "c", "c")) %>% 
  kable_styling(latex_options = c("scale_down","hold_position")) 

```


```{r QOL_ver_time, echo=FALSE, warning=FALSE, message=FALSE}

qol_ver<- all_data %>%  filter(qolcomplt != "Not Eligible") %>% 
  mutate(ver_surv = case_when(as.Date(d_914594314) < "2023-01-01" ~ "More than 1 Year",
                              as.Date(d_914594314) < "2023-07-01" ~ "6 Months - 1 Year",
                              as.Date(d_914594314) < "2024-01-01" ~ "3 Months - 6 Months",
                              as.Date(d_914594314) >= "2024-01-01" ~ "At 3 Months"),
         ver_surv = factor(ver_surv, levels=c("More than 1 Year","6 Months - 1 Year","3 Months - 6 Months","At 3 Months")))


qol_ver_df <- create_tbl_cross2(qol_ver, "ver_surv", "qolcomplt", "row", "Time from Verification to QOL Survey Release", "Survey Completion", 
                                "Total QOL Eligible Participants")

colnames(qol_ver_df)[5] <- "Total QOL Eligible \n Participants"
knitr::kable(qol_ver_df, 
             caption='Table 4.10. 3-Month Quality of Life Survey Completion By Time from Verification to QOL Survey Release',
             row.names=FALSE, align=c("l","c","c","c","c"), booktabs = TRUE) %>%
    kable_styling(latex_options = "scale_down") %>%  
    add_indent(seq(1, nrow(qol_ver_df) - 1)) %>%  landscape()
  


```



```{r BL_PROMIS_timeframe, echo=FALSE, warning=FALSE, message=FALSE}




#BU
trig_BU <- bq_project_query(project,
query="SELECT distinct(token), min(notification_time) as BU_time #distinct token to account for duplicate notifications
FROM `nih-nci-dceg-connect-prod-6d04.FlatConnect.notifications`
where (category='Baseline Clinical Blood and Urine Sample Survey Reminders' and attempt='1st contact') OR
(category='Baseline Clinical Biospecimen Survey Reminder' and attempt='1st contact')
group by token")
trigger_BU <- bigrquery::bq_table_download(trig_BU,bigint = "integer64")


#BUM
trig_BUM <- bq_project_query(project,
query="SELECT distinct(token), min(notification_time) as BUM_time #distinct token to account for duplicate notifications
FROM `nih-nci-dceg-connect-prod-6d04.FlatConnect.notifications`
where category='Baseline Research Biospecimen Survey Reminders' and attempt='1st contact' OR 
category='Biospecimen Survey Reminder' and attempt='1st contact'
group by token")
trigger_BUM <- bigrquery::bq_table_download(trig_BUM,bigint = "integer64")


trigger_time <- left_join(trigger_time, trigger_BU, by="token") %>%  left_join(trigger_BUM)


################   Numerator  ##############

#Completed QOL before or on the same day as BL survey-- now within 30 days
BL_QOL <- trigger_time %>%
  filter(qolcomplt == "Submitted") %>%
    mutate(BOH = as.Date(d_843688458) <= as.Date(d_517311251) & difftime(as.Date(d_517311251), as.Date(d_843688458), units="days") <31,
         MRE = as.Date(d_843688458) <= as.Date(d_832139544) & difftime( as.Date(d_832139544), as.Date(d_843688458), units="days") <31,
         SAS = as.Date(d_843688458) <= as.Date(d_770257102) & difftime( as.Date(d_770257102), as.Date(d_843688458), units="days") <31,
         LAW = as.Date(d_843688458) <= as.Date(d_264644252) & difftime( as.Date(d_264644252), as.Date(d_843688458), units="days") <31,
         BUM = (as.Date(BUM_time) < as.Date(trig) ) & (as.Date(d_843688458) <= as.Date(d_222161762)) & difftime( as.Date(d_222161762), as.Date(d_843688458), units="days") <31,  
         BU = (as.Date(BU_time) < as.Date(trig) ) & (as.Date(d_843688458) <= as.Date(d_764863765)) & difftime( as.Date(d_764863765), as.Date(d_843688458), units="days") <31,
         MW = (as.Date(d_173836415_d_266600170_d_319972665_d_661940160) < as.Date(trig)) & 
           (as.Date(d_843688458) <= as.Date(d_195145666)) & difftime( as.Date(d_195145666), as.Date(d_843688458), units="days") <31,
         COVID = (as.Date(d_556788178) < as.Date(trig)) & (as.Date(d_556788178) >= as.Date("2023-07-05")) & 
           (as.Date(d_843688458) <= as.Date(d_784810139)) & difftime( as.Date(d_784810139),as.Date(d_843688458),units="days") <31) %>%
  pivot_longer(
    cols = c(BOH, MRE, SAS, LAW, BUM, BU, MW, COVID),
    names_to = "qol_timeframe",
    values_to = "is_in_timeframe"
  ) %>%
  filter(is_in_timeframe) %>%  # Keep only TRUE rows
  group_by(qol_timeframe) %>%
  tally()


#############    Denominator #################

## Determine when a person was QOL eligible
# trigger_time <- trigger_time %>%
#   mutate(trig = case_when(d_914594314 < as.Date("2023-12-01") ~ ymd_hms(notification_time),
#                           TRUE ~ ymd_hms(d_914594314) + days(90)))

## Determine when a participant was BL survey eligible
#MRE/SAS/LAW- once BOH completed ----   d_517311251
#BUM/BU- when notified by email 
#MW- when notified the MW kit was shipped
#COVID- pushed to prod on 7/5/2023 and requires biospecimen donation 





## Those that are eligible for QOL, and eligible for whichever BL module, but hadn't completed that BL module upon QOL eligibility activation
BL_time_eligible <- trigger_time %>%
  filter(!is.na(qolcomplt) & qolcomplt != "Not Eligible") %>%
  mutate( BOH = is.na(d_517311251) | (as.Date(trig) <= as.Date(d_517311251)),
          MRE = !is.na(d_517311251) & (is.na(d_832139544) | as.Date(trig) <= as.Date(d_832139544)),
          SAS = !is.na(d_517311251) & (is.na(d_770257102) | as.Date(trig) <= as.Date(d_770257102)),
          LAW = !is.na(d_517311251) & (is.na(d_264644252) | as.Date(trig) <= as.Date(d_264644252)),
          BUM = (as.Date(BUM_time) < as.Date(trig))  & (is.na(d_222161762) | as.Date(trig) <= as.Date(d_222161762)),
          BU = (as.Date(BU_time) < as.Date(trig))  & (is.na(d_764863765) | as.Date(trig) <= as.Date(d_764863765)),
          MW = (as.Date(d_173836415_d_266600170_d_319972665_d_661940160) < as.Date(trig)) &
            (is.na(d_195145666) | as.Date(trig) <= as.Date(d_195145666)),
          COVID = as.Date(d_556788178) < as.Date(trig) &
            as.Date(d_556788178) >= as.Date("2023-07-05") &
            (is.na(d_784810139) | as.Date(trig) <= as.Date(d_784810139))) %>%
  pivot_longer(
    cols = c(BOH, MRE, SAS, LAW, BUM, BU, MW, COVID),
    names_to = "qol_timeframe",
    values_to = "is_in_timeframe"
  ) %>%
  filter(is_in_timeframe) %>%  # Keep only rows where the condition is TRUE
  group_by(qol_timeframe) %>%
  tally()



###############################################################################

after_QOL <- cbind(BL_QOL, BL_time_eligible)
after_QOL <- after_QOL[c(1,6,8,5,3,2,7,4), c(1,2,4)] # row order BOH, MRE, SAS, LAW, BUM, BU, MW, COVID, and remove repeated column
colnames(after_QOL) <- c("Survey", "n", "eligible")

after_QOL_table <- after_QOL %>%
  mutate(Percentage = (n / eligible) * 100,
         N_percent = paste0(formatC(n, big.mark = ",", format = "d"), 
                            " (", round(Percentage, digits = 2), "%)")) %>% 
  dplyr::rename('Eligible for Survey' = eligible,
         'N%' = N_percent) %>% 
    select('Survey', 'N%', 'Eligible for Survey')


knitr::kable(after_QOL_table,
             caption = 'Table 4.11. Baseline Survey Completion Within 30 days of 3-Month Quality of Life Survey Survey Completion', 
             booktabs=T, linesep = "", row.names=FALSE, align=c("l", "c", "c")) %>% 
  kable_styling(latex_options = "scale_down") %>% 
  footnote(general = "Note: Percentages calculated among those who were eligible but had not yet completed the survey at the time of QOL invitation.", 
           general_title = "",
         footnote_as_chunk = TRUE, 
         escape = FALSE, 
         threeparttable = TRUE)



```





\newpage                   
\FloatBarrier
# 6-month Diet History Questionnaire (III)
Note: The Diet History Questionnaire (DHQ) III survey was released on May 30, 2025 to prospective participants that are not withdrawn and verified on or after December 1, 2024 at the time they reach 6-months (180 days) verified.
```{r DHQ_Sect1, echo=FALSE, warning=FALSE, message=FALSE}


dhq1 <- all_data %>% filter(dhq_status!="Not Eligible" & !is.na(dhq_status)) 

dhq1_table <- create_tbl_cross1(dhq1,"Site", "dhq_status", "row", "Site", "Status")

dhq1_df <- as.data.frame(dhq1_table)
colnames(dhq1_df)[5] <- "Total Eligible for \n DHQ Survey"

knitr::kable(dhq1_df, 
             caption='Table 5.1 6-month Diet History Questionnaire Response Rate',
             row.names=FALSE, align=c("l","c","c","c","c","c"), booktabs = TRUE) %>%
    kable_styling(latex_options = "scale_down")  %>% 
  footnote(general = "Note: There may be up to a 24 hour delay between a participant completing the survey and retrieving their submitted status and completion timestamp.", 
           general_title = "",
         footnote_as_chunk = TRUE, 
         escape = FALSE, 
         threeparttable = TRUE)




#############

DHQ_comp_BL <- create_tbl_cross2(dhq1, "completion", "dhq_status", "row", "Completion", "DHQ Completion", "Total DHQ Eligible Participants")
colnames(DHQ_comp_BL)[5] <- "Total DHQ Eligible \n Participants"


knitr::kable(DHQ_comp_BL, 
             caption='Table 5.2. Completion of 6-month Diet History Questionnaire \n by Baseline Data Completeness',
             row.names=FALSE, align=c("l","c","c","c","c"), booktabs = TRUE) %>%
    kable_styling(latex_options = "scale_down") %>%  
    add_indent(seq(1, nrow(DHQ_comp_BL) - 1)) %>%  landscape()




##############

dhq_time = dhq1 %>% 
  filter(dhq_status=="Submitted") %>% 
  mutate(dhq_start_stop = as.numeric(difftime(as.POSIXct(ymd_hms(d_610227793)), as.POSIXct(ymd_hms(d_109610692)), units="mins")), 
         timeframe = case_when(dhq_start_stop<30 ~ "Under 30 Minutes",
                               dhq_start_stop<45 ~ "30-45 Minutes",
                               dhq_start_stop<60 ~ "45-60 Minutes",
                               dhq_start_stop<90 ~ "60-90 Minutes",
                               dhq_start_stop<120 ~ "90-120 Minutes",
                               dhq_start_stop>=120 ~ "Greater than 120 Minutes",
                               is.na(d_784810139) | is.na(d_268176409) ~ "Missing Time Stamp(s)"),
timeframe = factor(timeframe, levels=c("Under 30 Minutes", "30-45 Minutes", 
                                         "45-60 Minutes", "60-90 Minutes", "90-120 Minutes", 
                                       "Greater than 120 Minutes", "Missing Time Stamp(s)")))  %>% 
    group_by(timeframe) %>% tally() %>% 
    mutate(Percentage = (n / sum(n)) * 100)



summary_row <- data.frame(timeframe = "Total Submitted DHQ Surveys",
                          n = sum(dhq_time$n),
                          Percentage = 100)


dhq_time <- rbind(dhq_time, summary_row) %>%
    mutate(N_percent = paste0(formatC(n, big.mark = ",", format = "d"), 
                              " (", round(Percentage, digits = 2), "%)"),
           Cumulative_Percentage = round(cumsum(Percentage), digits=2))
dhq_time$Cumulative_Percentage[nrow(dhq_time)] <- 100

dhq_time <- dhq_time %>% 
    select(timeframe, N_percent, Cumulative_Percentage) %>%
    dplyr::rename(`Completion Time` = timeframe, `N%` = N_percent,
           'Cumulative Percentage' = Cumulative_Percentage)


knitr::kable(dhq_time, 
             caption='Table 5.3 6-month Diet History Questionnaire Completion Length (in minutes) \n among Submitted Surveys',
             row.names=FALSE, align=c("l","c","c"), booktabs = TRUE) %>%
  add_indent(c(1:(nrow(dhq_time)-1))) %>% 
    kable_styling(latex_options = "scale_down") 




```


```{r DHQ_Sect2, echo=FALSE, warning=FALSE, message=FALSE}

## Time from DHQ trigger to submission of DHQ survey

trig_DHQ <- bq_project_query(project,
query="SELECT distinct(token), notification_time as DHQ_notif
FROM `nih-nci-dceg-connect-prod-6d04.FlatConnect.notifications`
where category='Baseline DHQ III Reminders' and attempt='1st contact'")
trigger_DHQ <- bigrquery::bq_table_download(trig_DHQ,bigint = "integer64")


trigger_time_DHQ <- left_join(trigger_time, trigger_DHQ, by="token")


trig_time_DHQ <- trigger_time_DHQ %>%  filter(dhq_status == "Submitted") %>%
  mutate(trigTM_DHQ = as.numeric(difftime(as.POSIXct(ymd_hms(d_610227793)), as.POSIXct(ymd_hms(DHQ_notif)), units="days")))

Trig_table_DHQ = trig_time_DHQ %>%
  dplyr::summarize('N'=n(),
                   Min = round(min(trigTM_DHQ, na.rm = TRUE), digits=2),
                   Q1 = round(quantile(trigTM_DHQ, 0.25, na.rm = TRUE), digits=2),
                   Median = round(median(trigTM_DHQ, na.rm = TRUE), digits=2),
                   Mean = round(mean(trigTM_DHQ, na.rm = TRUE),  digits=2),
                   SD= round(sd(trigTM_DHQ, na.rm = TRUE), digits=2),
                   Q3 = round(quantile(trigTM_DHQ, 0.75, na.rm = TRUE), digits=2),
                   'Perc.90' = round(quantile(trigTM_DHQ, 0.90, na.rm = TRUE), digits=2),
                   Max = round(max(trigTM_DHQ, na.rm = TRUE), digits=2))

knitr::kable(Trig_table_DHQ, 
             caption = 'Table 5.4. 6-month Diet History Questionnaire Completion from Trigger to Submit for \n Verified Participants, in Days', 
             row.names=FALSE, format.args = list(big.mark = ","), linesep = "", 
             booktabs = T, align=c("l", "c", "c", "c", "c", "c", "c", "c", "c")) %>% 
  kable_styling(latex_options = c("scale_down","hold_position")) 

```



```{r DHQ_Sect3, echo=FALSE, warning=FALSE, message=FALSE}

## Determine when a person was DHQ eligible = time notification was sent

################   Numerator  ##############

#Completed DHQ before or on the same day as BL survey--now within 30 days
BL_DHQ <- trigger_time_DHQ %>%
  filter(dhq_status == "Submitted") %>%
  mutate(BOH = as.Date(d_610227793) <= as.Date(d_517311251) & difftime(as.Date(d_517311251), as.Date(d_610227793), units="days") <31,
         MRE = as.Date(d_610227793) <= as.Date(d_832139544) & difftime(as.Date(d_832139544), as.Date(d_610227793), units="days") <31,
         SAS = as.Date(d_610227793) <= as.Date(d_770257102) & difftime(as.Date(d_770257102), as.Date(d_610227793), units="days") <31,
         LAW = as.Date(d_610227793) <= as.Date(d_264644252) & difftime(as.Date(d_264644252), as.Date(d_610227793), units="days") <31,
         BUM = (as.Date(BUM_time) < as.Date(DHQ_notif) ) & (as.Date(d_610227793) <= as.Date(d_222161762)) & difftime(as.Date(d_222161762), as.Date(d_610227793), units="days") <31,  
         BU = (as.Date(BU_time) < as.Date(DHQ_notif) ) & (as.Date(d_610227793) <= as.Date(d_764863765)) & difftime(as.Date(d_764863765), as.Date(d_610227793), units="days") <31, 
         MW = (as.Date(d_173836415_d_266600170_d_319972665_d_661940160) < as.Date(DHQ_notif)) & (as.Date(d_610227793) <= as.Date(d_195145666)) & 
           difftime(as.Date(d_195145666), as.Date(d_610227793), units="days") <31,
         COVID = (as.Date(d_556788178) < as.Date(DHQ_notif)) & (as.Date(d_556788178) >= as.Date("2023-07-05")) & (as.Date(d_610227793) <= as.Date(d_784810139)) & 
           difftime(as.Date(d_784810139),as.Date(d_610227793),units="days") <31) %>%
  pivot_longer(
    cols = c(BOH, MRE, SAS, LAW, BUM, BU, MW, COVID),
    names_to = "DHQ_timeframe",
    values_to = "is_in_timeframe"
  ) %>%
  filter(is_in_timeframe) %>%  # Keep only TRUE rows
  group_by(DHQ_timeframe) %>%
  tally() %>% 
  complete(DHQ_timeframe = c("BOH", "MRE", "SAS", "LAW", "BUM", "BU", "MW", "COVID"), fill = list(n = 0))


#############    Denominator #################



## Determine when a participant was BL survey eligible
#MRE/SAS/LAW- once BOH completed ----   d_517311251
#BUM/BU- when notified by email 
#MW- when notified the MW kit was shipped
#COVID- pushed to prod on 7/5/2023 and requires biospecimen donation 





## Those that are eligible for DHQ, and eligible for whichever BL module, but who hadn't completed that BL module upon DHQ eligibility activation
DHQ_time_eligible2 <- trigger_time_DHQ %>%
  filter(!is.na(dhq_status) & dhq_status!="Not Eligible") %>%
  mutate( BOH = is.na(d_517311251) | (as.Date(DHQ_notif) <= as.Date(d_517311251)),
          MRE = !is.na(d_517311251) & (is.na(d_832139544) | as.Date(DHQ_notif) <= as.Date(d_832139544)),
          SAS = !is.na(d_517311251) & (is.na(d_770257102) | as.Date(DHQ_notif) <= as.Date(d_770257102)),
          LAW = !is.na(d_517311251) & (is.na(d_264644252) | as.Date(DHQ_notif) <= as.Date(d_264644252)),
          BUM = (as.Date(BUM_time) < as.Date(DHQ_notif))  & (is.na(d_222161762) | as.Date(DHQ_notif) <= as.Date(d_222161762)),
          BU = (as.Date(BU_time) < as.Date(DHQ_notif))  & (is.na(d_764863765) | as.Date(DHQ_notif) <= as.Date(d_764863765)),
          MW = (as.Date(d_173836415_d_266600170_d_319972665_d_661940160) < as.Date(DHQ_notif)) &
            (is.na(d_195145666) | as.Date(DHQ_notif) <= as.Date(d_195145666)),
          COVID = as.Date(d_556788178) < as.Date(DHQ_notif) &
            as.Date(d_556788178) >= as.Date("2023-07-05") &
            (is.na(d_784810139) | as.Date(DHQ_notif) <= as.Date(d_784810139))) %>%
  pivot_longer(
    cols = c(BOH, MRE, SAS, LAW, BUM, BU, MW, COVID),
    names_to = "DHQ_notifframe",
    values_to = "is_in_timeframe"
  ) %>%
  filter(is_in_timeframe) %>%  # Keep only rows where the condition is TRUE
  group_by(DHQ_notifframe) %>%
  tally() %>% 
  complete(DHQ_notifframe = c("BOH", "MRE", "SAS", "LAW", "BUM", "BU", "MW", "COVID"), fill = list(n = 0))



###############################################################################

after_DHQ <- cbind(BL_DHQ, DHQ_time_eligible2)
after_DHQ <- after_DHQ[c(1,6,8,5,3,2,7,4), c(1,2,4)] # row order BOH, MRE, SAS, LAW, BUM, BU, MW, COVID, and remove repeated column
colnames(after_DHQ) <- c("Survey", "n", "eligible")

after_DHQ_table <- after_DHQ %>%
  mutate(Percentage = (n / eligible) * 100,
         N_percent = paste0(formatC(n, big.mark = ",", format = "d"), 
                            " (", round(Percentage, digits = 1), "%)")) %>% 
  dplyr::rename('Eligible for Survey' = eligible,
         'N%' = N_percent) %>% 
    select('Survey', 'N%', 'Eligible for Survey')


knitr::kable(after_DHQ_table,
             caption = 'Table 5.5. Baseline Survey Completion Within 30 days of 6-month Diet History Questionnaire Completion', 
             booktabs=T, linesep = "", row.names=FALSE, align=c("l", "c", "c")) %>% 
  kable_styling(latex_options = "scale_down") %>% 
  footnote(general = "Note: Percentages calculated among those who were eligible but had not yet completed the survey at the time of DHQ invitation.", 
           general_title = "",
         footnote_as_chunk = TRUE, 
         escape = FALSE, 
         threeparttable = TRUE)



```


```{r DHQ_Sect4, echo=FALSE, warning=FALSE, message=FALSE}

##pushed on May 2029, 2025

dhq_ver<- dhq1 %>%   
  mutate(verif_months = verif_time_diff/30,
         ver_surv = case_when(verif_months<6 ~ "Less than 6 Months",
                              verif_months<12 ~ "6-12 Months",
                              verif_months<18 ~ "12-18 Months",
                              verif_months>=18 ~ "More than 18 Months"),
         ver_surv = factor(ver_surv, levels=c("More than 18 Months","12-18 Months","6-12 Months", "Less than 6 Months")))


dhq_ver_df <- create_tbl_cross2(dhq_ver, "ver_surv", "dhq_status", "row", "Time from Verification to DHQ Survey Release", "Survey Completion", 
                                "Total DHQ Eligible Participants")

colnames(dhq_ver_df)[5] <- "Total DHQ Eligible \n Participants"
knitr::kable(dhq_ver_df, 
             caption='Table 5.6. 6-month Diet History Questionnaire Completion By Time from Verification to Release',
             row.names=FALSE, align=c("l","c","c","c","c"), booktabs = TRUE) %>%
    kable_styling(latex_options = "scale_down") %>%  
    add_indent(seq(1, nrow(dhq_ver_df) - 1)) %>%  landscape()
  


```


```{r DHQ_Sect5, echo=FALSE, warning=FALSE, message=FALSE}


dhq1_table7 <- create_tbl_cross1(dhq1, 'dhq_status', 'external_status', 'row', 'Survey Status', 'Reserach Platform Status')

dhq1_df7 <- as.data.frame(dhq1_table7)
colnames(dhq1_df7)[6] <- "Total Eligible for \n DHQ Survey"

knitr::kable(dhq1_df7, 
             caption='Table 5.7. Cross Check between 6-month Diet History Questionnaire Survey Status flag \n and the Status According to the DHQ System',
             row.names=FALSE, align=c("l","c","c","c","c"), booktabs = TRUE) %>%
    kable_styling(latex_options = "scale_down") %>% 
  footnote(general = "Note: A 'Null' status according to the DHQ system means the participant has not logged into MyConnect since becoming eligible for the DHQ. 'Not yet begun' means they have logged into MyConnect but have not yet started the DHQ survey. There may also be up to a 24 hour delay between a participant starting and/or completing the survey and retrieving their 'Submitted', 'In Progress', and/or 'Completed' status.", 
           general_title = "",
         footnote_as_chunk = TRUE, 
         escape = FALSE, 
         threeparttable = TRUE) 


```


```{r DHQ_BySex_ByAge, echo=FALSE, error=FALSE, message=FALSE, warning=FALSE}


DHQ_Comp_by_Sex <- dhq1 %>% 
  mutate(dhq_status = factor(dhq_status, levels=c("Not Started", "Started", "Submitted"))) %>% 
  select(sex, dhq_status) %>% dplyr::arrange(sex,dhq_status) %>% 
  tbl_cross(
  row = sex,
  col = dhq_status,
  label = list(dhq_status ~ "Survey Completion",sex~"Sex"),
  percent = "row",
  digits=c(0,2),
  margin_text="Total DHQ Eligible Participants") 


DHQ_Comp_by_Sex_table <- DHQ_Comp_by_Sex %>%
  modify_header(stat_0 = "Total DHQ Eligible \n Participants") %>%
  modify_caption("Table 5.8. 6-month Diet History Questionnaire Completion Rate by Site Defined Sex \n Among Eligible Participants") %>%
  as_kable_extra(escape = FALSE, addtl_fmt = TRUE) %>% kable_styling(latex_options = c("scale_down","hold_position"))  

add_footnote(DHQ_Comp_by_Sex_table, "Note: Sex defined as the de-identified sex data reported by sites at time of invitation.", 
             notation = "none")





DHQ_Comp_by_Age <- dhq1 %>% 
  mutate(dhq_status = factor(dhq_status, levels=c("Not Started", "Started", "Submitted"))) %>% 
  select(age, dhq_status) %>% dplyr::arrange(age,dhq_status) %>% 
  tbl_cross(
  row = age,
  col = dhq_status,
  label = list(dhq_status ~ "Survey Completion",age~"Age"),
  percent = "row",
  digits=c(0,2),
  margin_text="Total DHQ Eligible Participants") 


DHQ_Comp_by_Age <- DHQ_Comp_by_Age %>%
  modify_header(stat_0 = "Total DHQ Eligible \n Participants") %>%
  modify_caption("Table 5.9. 6-month Diet History Questionnaire Completion Rate by Age \n Among Eligible Participants") %>%
  as_kable_extra(escape = FALSE, addtl_fmt = TRUE)  %>% kable_styling(latex_options = c("scale_down","hold_position")) 

add_footnote(DHQ_Comp_by_Age, "Note: Age defined as the de-identified age data reported by sites at time of invitation, not current age at time of survey completion.", 
             notation="none")


```


```{r DHQ_By_Race, echo=FALSE, warning=FALSE, message=FALSE, results='asis'}


DHQ_Comp_by_race <- m1_comp %>% filter(dhq_status!="Not Eligible") %>% 
  mutate(dhq_status = factor(dhq_status, levels=c("Not Started", "Started", "Submitted"))) %>% 
  select(race, dhq_status) %>% dplyr::arrange(race,dhq_status) %>% 
  tbl_cross(
  row = race,
  col = dhq_status,
  label = list(dhq_status ~ "Survey Completion",race~"Race"),
  percent = "row",
  digits=c(0,2),
  margin_text="Total DHQ Eligible Participants") 


DHQ_Comp_by_race <- DHQ_Comp_by_race %>%
  modify_header(stat_0 = "Total DHQ Eligible \n Participants") %>%
  modify_caption("Table 5.10. 6-month Diet History Questionnaire Completion Rate by Race \n Among Eligible Participants") %>%
  as_kable_extra(escape = FALSE, addtl_fmt = TRUE) %>% kable_styling(latex_options = c("scale_down","hold_position"))

reduced <- all_data %>% filter(d_949302066 != 231311385 & dhq_status!="Not Eligible") # Those who are eligible for PROMIS but didn't complete mod1 yet

add_footnote(DHQ_Comp_by_race, paste0('Note: In order to determine race, Module 1 must first be completed. There are ', dim(reduced)[[1]] , ' DHQ eligible participants that have either not started or not finished Module 1.'),
             notation="none")


```


```{r DHQ_By_SiteRace, echo=FALSE, warning=FALSE, message=FALSE, results='asis'}


DHQ_by_race_df <- create_tbl_cross2(dhq1, "race", "dhq_status", "row", "Race", "6-month Diet History Questionnaire", "Total Verified Participants")

knitr::kable(DHQ_by_race_df, 
             caption="Table 5.10.a 6-month Diet History Questionnaire Completion Rate by Site Defined Race \n Among Verified Participants",
             row.names=FALSE, align=c("l","c","c","c","c","c"), booktabs = TRUE) %>%
    kable_styling(latex_options = "scale_down") %>%  
    add_indent(seq(1, nrow(BL_by_Race_df) - 1)) %>%  landscape() %>%
    footnote(general = "Note: Race defined as the de-identified race data reported by sites at time of invitation.",
             general_title = "")

```


```{r DHQ_By_Race_And_Sex, echo=FALSE, warning=FALSE, message=FALSE, results='asis'}

DHQ_Comp_by_sex_race <- m1_comp %>% filter(dhq_status!="Not Eligible") %>% 
  mutate(dhq_status = factor(dhq_status, levels=c("Not Started", "Started", "Submitted"))) %>% 
  select(sex_race, dhq_status) %>% dplyr::arrange(sex_race,dhq_status) %>% 
  tbl_cross(
  row = sex_race,
  col = dhq_status,
  label = list(dhq_status ~ "Survey Completion",sex_race~"Sex and Race"),
  percent = "row",
  digits=c(0,2),
  margin_text="Total DHQ Eligible Participants") 


DHQ_Comp_by_sex_race <- DHQ_Comp_by_sex_race %>%
  modify_header(stat_0 = "Total DHQ Eligible \n Participants") %>%
  modify_caption("Table 5.11. 6-month Diet History Questionnaire Completion Rate by Sex and Race \n Among Eligible Participants") %>%
  as_kable_extra(escape = FALSE, addtl_fmt = TRUE)

reduced <- all_data %>% filter(d_949302066 != 231311385 & dhq_status!="Not Eligible") # Those who are eligible for PROMIS but didn't complete mod1 yet

DHQ_Comp_by_sex_race %>% kable_styling(latex_options = c("scale_down","hold_position")) %>% 
  footnote(general = paste0('In order to determine race, Module 1 must first be completed. There are ', dim(reduced)[[1]] , ' DHQ eligible participants that have either not started or not finished Module 1.'),general_title = "Note: ", footnote_as_chunk = T)


```


```{r DHQ_By_Demographic, echo=FALSE, warning=FALSE, message=FALSE, results='asis'}

DHQ_Comp_by_Demographic <- all_data_long %>% 
  filter(dhq_status != "Not Eligible") %>%
  mutate(dhq_status = factor(dhq_status, levels = c("Not Started", "Started", "Submitted")),
         Demographic_Group = factor(Demographic_Group, levels=c("White Women","Black Men","Women Under 45","Women Over 45","Men Under 45","Men Over 45"))) %>%
  select(Demographic_Group, dhq_status) %>%
  tbl_cross(
    row = Demographic_Group,
    col = dhq_status,
    label = list(dhq_status ~ "Survey Completion", Demographic_Group ~ "Demographic"),
    percent = "row",
    digits = c(0, 2),
    margin_text = "Total"
  )


DHQ_Comp_by_Demographic <- DHQ_Comp_by_Demographic %>%
  modify_header(stat_0 = "Total") %>%
  modify_caption("Table 5.12. 6-month Diet History Questionnaire Completion Rate \n by Demographic Among Eligible Participants") %>%
  as_kable_extra(escape = FALSE, addtl_fmt = TRUE)

# Style the table output
DHQ_Comp_by_Demographic %>% kable_styling(latex_options = c("scale_down", "hold_position"))  %>% 
  footnote(general = "Participants may be counted more then once in these categories.",general_title = "Note: ", footnote_as_chunk = T)


```







\newpage
\FloatBarrier

# 9-Month Cancer Screening History Survey
The 9-Month Cancer Screening History Follow Up Survey (CSH) is available to verified participants that are not withdrawn at 9-months post-verification. The survey was released to both prospective and backlog participants at the same time on 01/06/2025.

```{r CSH, echo=FALSE, warning=FALSE, message=FALSE, results='asis'}



CSH_comp <- all_data %>% filter(CSH_status!="Not Eligible") %>% 
  mutate(CSH_status = factor(CSH_status, levels=c("Not Started", "Started", "Submitted"))) %>% 
  select(Site, CSH_status) %>% dplyr::arrange(Site,CSH_status) %>% 
  tbl_cross(
    row = Site,
    col = CSH_status,
    label = list(CSH_status ~ "Survey Completion",Site~"Site"),
    percent = "row",
    digits=c(0,2),
    margin_text="Total CSH Eligible Participants") 

CSH_comp[["table_body"]]$stat_0 <- sapply(strsplit(CSH_comp[["table_body"]]$stat_0," "),"[",1)

CSH_comp <- CSH_comp %>%
  modify_header(stat_0 = "Total CSH Eligible \n Participants") %>%

  modify_caption("Table 6.1. Completion of 9-Month Cancer Screening History Survey Among Eligible Participants") %>%
  as_kable_extra(escape = FALSE, addtl_fmt = TRUE)


CSH_comp %>% kable_styling(latex_options = c("scale_down","hold_position"))

```



```{r CSH_BL, echo=FALSE, warning=FALSE, message=FALSE, results='asis'}


CSH_comp_BL <- all_data %>%  filter(CSH_status!="Not Eligible") %>%  
  mutate(CSH_status = factor(CSH_status, levels=c("Not Started", "Started", "Submitted")),
         completion = factor(completion, levels=c("Completed both survey and sample(s)","Completed all baseline survey modules 1-4, no baseline samples", 
                                                  "Completed any baseline sample, did not complete baseline survey","Completed neither survey or sample(s)")))


CSH_com_df <- create_tbl_cross2(CSH_comp_BL, "completion", "CSH_status", "row", "Completion", "Survey Completion", "Total CSH Eligible Participants")

colnames(CSH_com_df)[5] <- "Total CSH Eligible \n Participants"

knitr::kable(CSH_com_df, 
             caption='Table 6.2. Completion of 9-Month Cancer Screening History Survey by Baseline Data Completeness',
             row.names=FALSE, align=c("l","c","c","c","c"), booktabs = TRUE) %>%
  kable_styling(latex_options = "scale_down") %>%  
  add_indent(seq(1, nrow(CSH_com_df) - 1)) %>%  landscape()

```


\FloatBarrier
```{r CSH_Start_Stop, echo=FALSE, warning=FALSE, message=FALSE}


CSH_time <- all_data %>% filter(CSH_status == "Submitted") %>%
  mutate(comp_tm_CSH = as.numeric(difftime(as.POSIXct(ymd_hms(d_389890053)), as.POSIXct(ymd_hms(d_609630315)), units="mins")),
         start_stop_time = case_when(comp_tm_CSH<5 ~ "Under 5 Minutes",
                                     comp_tm_CSH<10 ~ "5-10 Minutes",
                                     comp_tm_CSH<15 ~ "10-15 Minutes",
                                     comp_tm_CSH<20 ~ "15-20 Minutes",
                                     comp_tm_CSH<30 ~ "20-30 Minutes",
                                     comp_tm_CSH>=30 ~ "30+ Minutes",
                                     is.na(d_389890053) | is.na(d_609630315) ~ "Missing Stop or Start Timestamp"),
         start_stop_time = factor(start_stop_time, levels=c("Under 5 Minutes", "5-10 Minutes", "10-15 Minutes", 
                                                            "15-20 Minutes", "20-30 Minutes", "30+ Minutes", "Missing Stop or Start Timestamp")))  %>% 
  group_by(start_stop_time) %>% tally()

CSH_time$Percentage <- (CSH_time$n / sum(CSH_time$n)) * 100

summary_row <- data.frame(start_stop_time = "Total CSH Eligible Participants",
                          n = sum(CSH_time$n),
                          Percentage = 100)


CSH_TM <- rbind(CSH_time, summary_row) %>%
  mutate(N_percent = paste0(formatC(n, big.mark = ",", format = "d"), 
                            " (", round(Percentage, digits = 1), "%)"))


CSH_TM <- CSH_TM %>% 
  select(start_stop_time, N_percent) %>%
  dplyr::rename(`Completion Time` = start_stop_time, 
         `N%` = N_percent)


knitr::kable(CSH_TM, 
             caption = 'Table 6.3. 9-Month Cancer Screening History Survey Completion Time from Start to Submit \n Among Eligible Participants', 
             booktabs=T, linesep = "", row.names=FALSE, align=c("l", "c")) %>% 
  add_indent(c(1:(nrow(CSH_TM)-1))) %>%  
  kable_styling(latex_options = "scale_down") #c("scale_down","hold_position"))

```


```{r CSH_trig_stop, echo=FALSE, warning=FALSE, message=FALSE}

## Time from CSH trigger to submission of CSH survey

trig_csh <- bq_project_query(project,
                             query="SELECT distinct(Connect_ID), notification_time as CSH_notif FROM `nih-nci-dceg-connect-prod-6d04.FlatConnect.notifications` notif
                             left join `nih-nci-dceg-connect-prod-6d04.FlatConnect.participants` pts
                             on notif.token=pts.token
                             where category LIKE '%Screen%' and attempt='1st contact'")


trigger_csh <- bigrquery::bq_table_download(trig_csh,bigint = "integer64")


trigger_time$Connect_ID <- as.numeric(trigger_time$Connect_ID)
trigger_csh$Connect_ID <- as.numeric(trigger_csh$Connect_ID)

trigger_time <- left_join(trigger_time, trigger_csh, by="Connect_ID")


CSH_notif_table = trigger_time %>%  
  filter(CSH_status == "Submitted") %>%
  mutate(time = as.numeric(difftime(as.POSIXct(ymd_hms(d_389890053)), as.POSIXct(ymd_hms(CSH_notif)), units="days"))) %>% 
  dplyr::summarize('N'=n(),
                   Min = round(min(time, na.rm = TRUE), digits=2),
                   Q1 = round(quantile(time, 0.25, na.rm = TRUE), digits=2),
                   Median = round(median(time, na.rm = TRUE), digits=2),
                   Mean = round(mean(time, na.rm = TRUE),  digits=2),
                   SD= round(sd(time, na.rm = TRUE), digits=2),
                   Q3 = round(quantile(time, 0.75, na.rm = TRUE), digits=2),
                   'Perc.90' = round(quantile(time, 0.90, na.rm = TRUE), digits=2),
                   Max = round(max(time, na.rm = TRUE), digits=2))



knitr::kable(CSH_notif_table, 
             caption = 'Table 6.4. 9-Month Cancer Screening History Survey Completion from Trigger \n to Submit for Verified Participants, in Days', 
             row.names=FALSE, format.args = list(big.mark = ","), linesep = "", 
             booktabs = T, align=c("l", "c", "c", "c", "c", "c", "c", "c", "c")) %>% 
  kable_styling(latex_options = c("scale_down","hold_position")) 

```


\newpage
\FloatBarrier


```{r BL_After_CSH2, echo=FALSE, warning=FALSE, message=FALSE}

## Determine when a person was CSH eligible
# time notification was sent

################   Numerator  ##############

#Completed CSH before or on the same day as BL survey--now within 30 days
BL_CSH <- trigger_time %>%
  filter(CSH_status == "Submitted") %>%
  mutate(BOH = as.Date(d_389890053) <= as.Date(d_517311251) & difftime(as.Date(d_517311251), as.Date(d_389890053), units="days") <31,
         MRE = as.Date(d_389890053) <= as.Date(d_832139544) & difftime(as.Date(d_832139544), as.Date(d_389890053), units="days") <31,
         SAS = as.Date(d_389890053) <= as.Date(d_770257102) & difftime(as.Date(d_770257102), as.Date(d_389890053), units="days") <31,
         LAW = as.Date(d_389890053) <= as.Date(d_264644252) & difftime(as.Date(d_264644252), as.Date(d_389890053), units="days") <31,
         BUM = (as.Date(BUM_time) < as.Date(CSH_notif) ) & (as.Date(d_389890053) <= as.Date(d_222161762)) & difftime(as.Date(d_222161762), as.Date(d_389890053), units="days") <31,  
         BU = (as.Date(BU_time) < as.Date(CSH_notif) ) & (as.Date(d_389890053) <= as.Date(d_764863765)) & difftime(as.Date(d_764863765), as.Date(d_389890053), units="days") <31, 
         MW = (as.Date(d_173836415_d_266600170_d_319972665_d_661940160) < as.Date(CSH_notif)) & (as.Date(d_389890053) <= as.Date(d_195145666)) & 
           difftime(as.Date(d_195145666), as.Date(d_389890053), units="days") <31,
         COVID = (as.Date(d_556788178) < as.Date(CSH_notif)) & (as.Date(d_556788178) >= as.Date("2023-07-05")) & (as.Date(d_389890053) <= as.Date(d_784810139)) & 
           difftime(as.Date(d_784810139),as.Date(d_389890053),units="days") <31) %>%
  pivot_longer(
    cols = c(BOH, MRE, SAS, LAW, BUM, BU, MW, COVID),
    names_to = "CSH_timeframe",
    values_to = "is_in_timeframe"
  ) %>%
  filter(is_in_timeframe) %>%  # Keep only TRUE rows
  group_by(CSH_timeframe) %>%
  tally()


#############    Denominator #################



## Determine when a participant was BL survey eligible
#MRE/SAS/LAW- once BOH completed ----   d_517311251
#BUM/BU- when notified by email 
#MW- when notified the MW kit was shipped
#COVID- pushed to prod on 7/5/2023 and requires biospecimen donation 





## Those that are eligible for CSH, and eligible for whichever BL module, who hadn't completed that BL module upon CSH eligibility activation
BL_time_eligible2 <- trigger_time %>%
  filter(!is.na(CSH_status) & CSH_status != "Not Eligible") %>%
  mutate( BOH = is.na(d_517311251) | (as.Date(CSH_notif) <= as.Date(d_517311251)),
          MRE = !is.na(d_517311251) & (is.na(d_832139544) | as.Date(CSH_notif) <= as.Date(d_832139544)),
          SAS = !is.na(d_517311251) & (is.na(d_770257102) | as.Date(CSH_notif) <= as.Date(d_770257102)),
          LAW = !is.na(d_517311251) & (is.na(d_264644252) | as.Date(CSH_notif) <= as.Date(d_264644252)),
          BUM = (as.Date(BUM_time) < as.Date(CSH_notif))  & (is.na(d_222161762) | as.Date(CSH_notif) <= as.Date(d_222161762)),
          BU = (as.Date(BU_time) < as.Date(CSH_notif))  & (is.na(d_764863765) | as.Date(CSH_notif) <= as.Date(d_764863765)),
          MW = (as.Date(d_173836415_d_266600170_d_319972665_d_661940160) < as.Date(CSH_notif)) &
            (is.na(d_195145666) | as.Date(CSH_notif) <= as.Date(d_195145666)),
          COVID = as.Date(d_556788178) < as.Date(CSH_notif) &
            as.Date(d_556788178) >= as.Date("2023-07-05") &
            (is.na(d_784810139) | as.Date(CSH_notif) <= as.Date(d_784810139))) %>%
  pivot_longer(
    cols = c(BOH, MRE, SAS, LAW, BUM, BU, MW, COVID),
    names_to = "CSH_notifframe",
    values_to = "is_in_timeframe"
  ) %>%
  filter(is_in_timeframe) %>%  # Keep only rows where the condition is TRUE
  group_by(CSH_notifframe) %>%
  tally()



###############################################################################

after_CSH <- cbind(BL_CSH, BL_time_eligible2)
after_CSH <- after_CSH[c(1,6,8,5,3,2,7,4), c(1,2,4)] # row order BOH, MRE, SAS, LAW, BUM, BU, MW, COVID, and remove repeated column
colnames(after_CSH) <- c("Survey", "n", "eligible")

after_CSH_table <- after_CSH %>%
  mutate(Percentage = (n / eligible) * 100,
         N_percent = paste0(formatC(n, big.mark = ",", format = "d"), 
                            " (", round(Percentage, digits = 2), "%)")) %>% 
  dplyr::rename('Eligible for Survey' = eligible,
         'N%' = N_percent) %>% 
    select('Survey', 'N%', 'Eligible for Survey')


knitr::kable(after_CSH_table,
             caption = 'Table 6.5. Baseline Survey Completion Within 30 days of \n Month Cancer Screening History Survey Survey Completion', 
             booktabs=T, linesep = "", row.names=FALSE, align=c("l", "c", "c")) %>% 
  kable_styling(latex_options = "scale_down") %>% 
  footnote(general = "Note: Percentages calculated among those who were eligible but had not yet completed the survey at the time of CSH invitation.", 
           general_title = "",
         footnote_as_chunk = TRUE, 
         escape = FALSE, 
         threeparttable = TRUE)



```



```{r CSH_ver_time, echo=FALSE, warning=FALSE, message=FALSE}

csh_ver<- all_data %>%  filter(CSH_status != "Not Eligible") %>% 
  mutate(ver_surv = case_when(as.Date(d_914594314) < "2023-07-01" ~ "More than 18 Months",
                              as.Date(d_914594314) < "2024-01-01" ~ "12-18 Months",
                              as.Date(d_914594314) >= "2024-01-01" ~ "9-12 Months"),
         ver_surv = factor(ver_surv, levels=c("More than 18 Months","12-18 Months","9-12 Months")))


csh_ver_df <- create_tbl_cross2(csh_ver, "ver_surv", "CSH_status", "row", "Time from Verification to CSH Survey Release", "Survey Completion", 
                                "Total CSH Eligible Participants")

colnames(csh_ver_df)[5] <- "Total CSH Eligible \n Participants"
knitr::kable(csh_ver_df, 
             caption='Table 6.6. 9-Month Cancer Screening History Survey Completion \n By Time from Verification to CSH Survey Release',
             row.names=FALSE, align=c("l","c","c","c","c"), booktabs = TRUE) %>%
    kable_styling(latex_options = "scale_down") %>%  
    add_indent(seq(1, nrow(csh_ver_df) - 1)) %>%  landscape()
  


```


```{r CSH_BySex_ByAge, echo=FALSE, error=FALSE, message=FALSE, warning=FALSE}


CSH_Comp_by_Sex <- all_data %>%  filter(CSH_status != "Not Eligible") %>% 
  mutate(CSH_status = factor(CSH_status, levels=c("Not Started", "Started", "Submitted"))) %>% 
  select(sex, CSH_status) %>% dplyr::arrange(sex,CSH_status) %>% 
  tbl_cross(
  row = sex,
  col = CSH_status,
  label = list(CSH_status ~ "Survey Completion",sex~"Sex"),
  percent = "row",
  digits=c(0,2),
  margin_text="Total CSH Eligible Participants") 


CSH_Comp_by_Sex_table <- CSH_Comp_by_Sex %>%
  modify_header(stat_0 = "Total CSH Eligible \n Participants") %>%
  modify_caption("Table 6.7. 9-Month Cancer Screening History Survey Completion Rate by Site Defined Sex \n Among Eligible Participants") %>%
  as_kable_extra(escape = FALSE, addtl_fmt = TRUE) %>% kable_styling(latex_options = c("scale_down","hold_position"))  

add_footnote(CSH_Comp_by_Sex_table, "Note: Sex defined as the de-identified sex data reported by sites at time of invitation.", 
             notation = "none")





CSH_Comp_by_Age <- all_data %>%  filter(CSH_status != "Not Eligible") %>% 
  mutate(CSH_status = factor(CSH_status, levels=c("Not Started", "Started", "Submitted"))) %>% 
  select(age, CSH_status) %>% dplyr::arrange(age,CSH_status) %>% 
  tbl_cross(
  row = age,
  col = CSH_status,
  label = list(CSH_status ~ "Survey Completion",age~"Age"),
  percent = "row",
  digits=c(0,2),
  margin_text="Total CSH Eligible Participants") 


CSH_Comp_by_Age <- CSH_Comp_by_Age %>%
  modify_header(stat_0 = "Total CSH Eligible \n Participants") %>%
  modify_caption("Table 6.8. 9-Month Cancer Screening History Survey Completion Rate by Age \n Among Eligible Participants") %>%
  as_kable_extra(escape = FALSE, addtl_fmt = TRUE)  %>% kable_styling(latex_options = c("scale_down","hold_position")) 

add_footnote(CSH_Comp_by_Age, "Note: Age defined as the de-identified age data reported by sites at time of invitation, not current age at time of survey completion.", 
             notation="none")


```


```{r CSH_By_Race, echo=FALSE, warning=FALSE, message=FALSE, results='asis'}


CSH_Comp_by_race <- m1_comp %>% filter(CSH_status!="Not Eligible") %>% 
  mutate(CSH_status = factor(CSH_status, levels=c("Not Started", "Started", "Submitted"))) %>% 
  select(race, CSH_status) %>% dplyr::arrange(race,CSH_status) %>% 
  tbl_cross(
  row = race,
  col = CSH_status,
  label = list(CSH_status ~ "Survey Completion",race~"Race"),
  percent = "row",
  digits=c(0,2),
  margin_text="Total CSH Eligible Participants") 


CSH_Comp_by_race <- CSH_Comp_by_race %>%
  modify_header(stat_0 = "Total CSH Eligible \n Participants") %>%
  modify_caption("Table 6.9. 9-Month Cancer Screening History Survey Completion Rate by Race \n Among Eligible Participants") %>%
  as_kable_extra(escape = FALSE, addtl_fmt = TRUE) %>% kable_styling(latex_options = c("scale_down","hold_position"))

reduced <- all_data %>% filter(d_949302066 != 231311385 & CSH_status!="Not Eligible") # Those who are eligible for PROMIS but didn't complete mod1 yet

add_footnote(CSH_Comp_by_race, paste0('Note: In order to determine race, Module 1 must first be completed. There are ', dim(reduced)[[1]] , ' CSH eligible participants that have either not started or not finished Module 1.'),
             notation="none")


```


```{r CSH_By_SiteRace, echo=FALSE, warning=FALSE, message=FALSE, results='asis'}

csh1 <- all_data %>%  filter(CSH_status != "Not Eligible")

CSH_by_race_df <- create_tbl_cross2(csh1, "race", "CSH_status", "row", "Race", "9-Month Cancer Screening History Survey", "Total Verified Participants")

knitr::kable(CSH_by_race_df, 
             caption="Table 6.9.a 9-Month Cancer Screening History Survey Completion Rate by Site Defined Race \n Among Verified Participants",
             row.names=FALSE, align=c("l","c","c","c","c","c"), booktabs = TRUE) %>%
    kable_styling(latex_options = "scale_down") %>%  
    add_indent(seq(1, nrow(BL_by_Race_df) - 1)) %>%  landscape() %>%
    footnote(general = "Note: Race defined as the de-identified race data reported by sites at time of invitation.",
             general_title = "")

```


```{r CSH_By_Race_And_Sex, echo=FALSE, warning=FALSE, message=FALSE, results='asis'}

CSH_Comp_by_sex_race <- m1_comp %>% filter(CSH_status!="Not Eligible") %>% 
  mutate(CSH_status = factor(CSH_status, levels=c("Not Started", "Started", "Submitted"))) %>% 
  select(sex_race, CSH_status) %>% dplyr::arrange(sex_race,CSH_status) %>% 
  tbl_cross(
  row = sex_race,
  col = CSH_status,
  label = list(CSH_status ~ "Survey Completion",sex_race~"Sex and Race"),
  percent = "row",
  digits=c(0,2),
  margin_text="Total CSH Eligible Participants") 


CSH_Comp_by_sex_race <- CSH_Comp_by_sex_race %>%
  modify_header(stat_0 = "Total CSH Eligible \n Participants") %>%
  modify_caption("Table 6.10. 9-Month Cancer Screening History Survey Completion Rate by Sex and Race \n Among Eligible Participants") %>%
  as_kable_extra(escape = FALSE, addtl_fmt = TRUE)

reduced <- all_data %>% filter(d_949302066 != 231311385 & CSH_status!="Not Eligible") # Those who are eligible for PROMIS but didn't complete mod1 yet

CSH_Comp_by_sex_race %>% kable_styling(latex_options = c("scale_down","hold_position")) %>% 
  footnote(general = paste0('In order to determine race, Module 1 must first be completed. There are ', dim(reduced)[[1]] , ' CSH eligible participants that have either not started or not finished Module 1.'),general_title = "Note: ", footnote_as_chunk = T)


```


```{r CSH_By_Demographic, echo=FALSE, warning=FALSE, message=FALSE, results='asis'}

CSH_Comp_by_Demographic <- all_data_long %>% 
  filter(CSH_status != "Not Eligible") %>%
  mutate(CSH_status = factor(CSH_status, levels = c("Not Started", "Started", "Submitted")),
         Demographic_Group = factor(Demographic_Group, levels=c("White Women","Black Men","Women Under 45","Women Over 45","Men Under 45","Men Over 45"))) %>%
  select(Demographic_Group, CSH_status) %>%
  tbl_cross(
    row = Demographic_Group,
    col = CSH_status,
    label = list(CSH_status ~ "Survey Completion", Demographic_Group ~ "Demographic"),
    percent = "row",
    digits = c(0, 2),
    margin_text = "Total"
  )


CSH_Comp_by_Demographic <- CSH_Comp_by_Demographic %>%
  modify_header(stat_0 = "Total") %>%
  modify_caption("Table 6.11. 9-Month Cancer Screening History Survey Completion Rate \n by Demographic Among Eligible Participants") %>%
  as_kable_extra(escape = FALSE, addtl_fmt = TRUE)

# Style the table output
CSH_Comp_by_Demographic %>% kable_styling(latex_options = c("scale_down", "hold_position"))  %>% 
  footnote(general = "Participants may be counted more then once in these categories.",general_title = "Note: ", footnote_as_chunk = T)


```






\newpage
\FloatBarrier
# 2024 Connect Experience Survey
The Connect Experience Cross-Sectional Survey (CES) was released to eligible participants (verified between 03/01/2024 and 07/31/2024 and not withdrawn) on 10/03/2024. This survey was a one-time cross-sectional survey that is no longer being newly released to participants.
```{r CES, echo=FALSE, warning=FALSE, message=FALSE, results='asis'}



CES_comp <- all_data %>% filter(CES_status!="Not Eligible") %>% 
  mutate(CES_status = factor(CES_status, levels=c("Not Started", "Started", "Submitted"))) %>% 
  select(Site, CES_status) %>% dplyr::arrange(Site,CES_status) %>% 
  tbl_cross(
  row = Site,
  col = CES_status,
  label = list(CES_status ~ "Survey Completion",Site~"Site"),
  percent = "row",
  digits=c(0,2),
  margin_text="Total CES Eligible Participants") 

CES_comp[["table_body"]]$stat_0 <- sapply(strsplit(CES_comp[["table_body"]]$stat_0," "),"[",1)

CES_comp <- CES_comp %>%
  modify_header(stat_0 = "Total CES Eligible \n Participants") %>%
  modify_caption("Table 7.1. Completion of Connect Experience Survey Among Eligible Participants") %>%
  as_kable_extra(escape = FALSE, addtl_fmt = TRUE)

 
CES_comp %>% kable_styling(latex_options = c("scale_down","hold_position"))

```



```{r CES_BL, echo=FALSE, warning=FALSE, message=FALSE, results='asis'}


CES_comp_BL <- all_data %>%  filter(CES_status!="Not Eligible") %>%  
  mutate(CES_status = factor(CES_status, levels=c("Not Started", "Started", "Submitted")),
         completion = factor(completion, levels=c("Completed both survey and sample(s)","Completed all baseline survey modules 1-4, no baseline samples", 
                                                  "Completed any baseline sample, did not complete baseline survey","Completed neither survey or sample(s)")))


CES_com_df <- create_tbl_cross2(CES_comp_BL, "completion", "CES_status", "row", "Completion", "Survey Completion", "Total CES Eligible Participants")

colnames(CES_com_df)[5] <- "Total CES Eligible \n Participants"

knitr::kable(CES_com_df, 
             caption='Table 7.2. Completion of Connect Experience Survey by Baseline Data Completeness',
             row.names=FALSE, align=c("l","c","c","c","c"), booktabs = TRUE) %>%
    kable_styling(latex_options = "scale_down") %>%  
    add_indent(seq(1, nrow(CES_com_df) - 1)) %>%  landscape()

```



\FloatBarrier
```{r CES_Start_Stop, echo=FALSE, warning=FALSE, message=FALSE}


CES_time <- all_data %>% filter(CES_status=="Submitted") %>%
  mutate(comp_tm_CES = as.numeric(difftime(as.POSIXct(ymd_hms(d_199471989)), as.POSIXct(ymd_hms(d_263355177)), units="mins")),
         start_stop_time = case_when(comp_tm_CES<5 ~ "Under 5 Minutes",
                                comp_tm_CES<10 ~ "5-10 Minutes",
                                comp_tm_CES<15 ~ "10-15 Minutes",
                                comp_tm_CES<20 ~ "15-20 Minutes",
                                comp_tm_CES<30 ~ "20-30 Minutes",
                                comp_tm_CES>=30 ~ "30+ Minutes",
                                is.na(d_199471989) | is.na(d_263355177) ~ "Missing Stop or Start Timestamp"),
         start_stop_time = factor(start_stop_time, levels=c("Under 5 Minutes", "5-10 Minutes", "10-15 Minutes", 
                                                   "15-20 Minutes", "20-30 Minutes", "30+ Minutes", "Missing Stop or Start Timestamp")))  %>% 
    group_by(start_stop_time) %>% tally()

CES_time$Percentage <- (CES_time$n / sum(CES_time$n)) * 100

summary_row <- data.frame(start_stop_time = "Total CES Eligible Participants",
                          n = sum(CES_time$n),
                          Percentage = 100)


CES_TM <- rbind(CES_time, summary_row)

CES_TM[1, 4] <- paste0(formatC(CES_TM[1, 2], big.mark = ",", format = "d"), " (", round(CES_TM[1, 3], digits = 2), "%)")
CES_TM[2, 4] <- paste0(formatC(CES_TM[2, 2], big.mark = ",", format = "d"), " (", round(CES_TM[2, 3], digits = 2), "%)")
CES_TM[3, 4] <- paste0(formatC(CES_TM[3, 2], big.mark = ",", format = "d"), " (", round(CES_TM[3, 3], digits = 2), "%)")
CES_TM[4, 4] <- paste0(formatC(CES_TM[4, 2], big.mark = ",", format = "d"), " (", round(CES_TM[4, 3], digits = 2), "%)")
CES_TM[5, 4] <- paste0(formatC(CES_TM[5, 2], big.mark = ",", format = "d"), " (", round(CES_TM[5, 3], digits = 2), "%)")
CES_TM[6, 4] <- paste0(formatC(CES_TM[6, 2], big.mark = ",", format = "d"), " (", round(CES_TM[6, 3], digits = 2), "%)")
CES_TM[7, 4] <- paste0(formatC(CES_TM[7, 2], big.mark = ",", format = "d"), " (", round(CES_TM[7, 3], digits = 2), "%)")


CES_TM_table <- CES_TM[, c(1,4)]

colnames(CES_TM_table) <- c("Completion Time", "N%")

knitr::kable(CES_TM_table, 
             caption = 'Table 7.3. Connect Experience Survey Completion Time from Start to Submit \n Among Eligible Participants', 
             booktabs=T, linesep = "", row.names=FALSE, align=c("l", "c")) %>% 
  add_indent(c(1:(nrow(CES_TM_table)-1))) %>%  
  kable_styling(latex_options = "scale_down") #c("scale_down","hold_position"))

```

\FloatBarrier
```{r CES_trig_stop, echo=FALSE, warning=FALSE, message=FALSE}


ces_notif_time<- all_data %>%  
  filter(CES_status=="Submitted") %>%
  mutate(notification_time = "2024-09-30",
         time = as.numeric(difftime(as.Date(d_199471989), as.Date(notification_time), units="days")))

ces_notif_table = ces_notif_time %>%
  dplyr::summarize('N'=n(),
                   Min = round(min(time, na.rm = TRUE), digits=2),
                   Q1 = round(quantile(time, 0.25, na.rm = TRUE), digits=2),
                   Median = round(median(time, na.rm = TRUE), digits=2),
                   Mean = round(mean(time, na.rm = TRUE),  digits=2),
                   SD= round(sd(time, na.rm = TRUE), digits=2),
                   Q3 = round(quantile(time, 0.75, na.rm = TRUE), digits=2),
                   'Perc.90' = round(quantile(time, 0.90, na.rm = TRUE), digits=2),
                   Max = round(max(time, na.rm = TRUE), digits=2))



knitr::kable(ces_notif_table, 
             caption = 'Table 7.4. Connect Experience Survey Completion from Trigger to Submit for \n Verified Participants, in Days', 
             row.names=FALSE, format.args = list(big.mark = ","), linesep = "", 
             booktabs = T, align=c("l", "c", "c", "c", "c", "c", "c", "c", "c")) %>% 
  kable_styling(latex_options = c("scale_down","hold_position")) 

```



\FloatBarrier

```{r BL_After_CES2, echo=FALSE, warning=FALSE, message=FALSE}


################   Numerator  ##############

#Completed CES before or on the same day as BL survey-- now within 30 days
BL_CES <- trigger_time %>%
  filter(CES_status == "Submitted") %>%
  mutate(BOH = as.Date(d_199471989) <= as.Date(d_517311251) & difftime(as.Date(d_517311251), as.Date(d_199471989), units="days") <31,
         MRE = as.Date(d_199471989) <= as.Date(d_832139544) & difftime(as.Date(d_832139544), as.Date(d_199471989), units="days") <31,
         SAS = as.Date(d_199471989) <= as.Date(d_770257102) & difftime(as.Date(d_770257102), as.Date(d_199471989), units="days") <31,
         LAW = as.Date(d_199471989) <= as.Date(d_264644252) & difftime(as.Date(d_264644252), as.Date(d_199471989), units="days") <31,
         BUM = (as.Date(BUM_time) < as.Date("2024-09-30") ) & (as.Date(d_199471989) <= as.Date(d_222161762)) & difftime(as.Date(d_222161762), as.Date(d_199471989), units="days") <31,  
         BU = (as.Date(BU_time) < as.Date("2024-09-30")  ) & (as.Date(d_199471989) <= as.Date(d_764863765)) & difftime(as.Date(d_764863765), as.Date(d_199471989), units="days") <31, 
         MW = (as.Date(d_173836415_d_266600170_d_319972665_d_661940160) < as.Date("2024-09-30") ) & (as.Date(d_199471989) <= as.Date(d_195145666))  & 
           difftime(as.Date(d_195145666), as.Date(d_199471989), units="days") <31,
         COVID = (as.Date(d_556788178) < as.Date("2024-09-30") ) & (as.Date(d_556788178) >= as.Date("2023-07-05")) & (as.Date(d_199471989) <= as.Date(d_784810139)) & 
           difftime(as.Date(d_784810139),as.Date(d_199471989),units="days") <31) %>%
  pivot_longer(
    cols = c(BOH, MRE, SAS, LAW, BUM, BU, MW, COVID),
    names_to = "CES_timeframe",
    values_to = "is_in_timeframe"
  ) %>%
  filter(is_in_timeframe) %>%  # Keep only TRUE rows
  group_by(CES_timeframe) %>%
  tally()


#############    Denominator #################

## Determine when a person was CES eligible
# All participants with a survey status NOT 'Not Eligible' or null; notificaton for CES was sent on 9/30/24


## Determine when a participant was BL survey eligible
#MRE/SAS/LAW- once BOH completed ----   d_517311251
#BUM/BU- when notified by email 
#MW- when notified the MW kit was shipped
#COVID- pushed to prod on 7/5/2023 and requires biospecimen donation 





## of those that are eligible for CES, and eligible for whichever BL module, who hadn't completed that module upon eligibility activation
BL_time_eligible3 <- trigger_time %>%
  filter(!is.na(CES_status) & CES_status != "Not Eligible") %>%
  mutate( BOH = is.na(d_517311251) | (as.Date("2024-09-30")  <= as.Date(d_517311251)),
          MRE = !is.na(d_517311251) & (is.na(d_832139544) | as.Date("2024-09-30")  <= as.Date(d_832139544)),
          SAS = !is.na(d_517311251) & (is.na(d_770257102) | as.Date("2024-09-30")  <= as.Date(d_770257102)),
          LAW = !is.na(d_517311251) & (is.na(d_264644252) | as.Date("2024-09-30")  <= as.Date(d_264644252)),
          BUM = (as.Date(BUM_time) < as.Date("2024-09-30") )  & (is.na(d_222161762) | as.Date("2024-09-30")  <= as.Date(d_222161762)),
          BU = (as.Date(BU_time) < as.Date("2024-09-30") )  & (is.na(d_764863765) | as.Date("2024-09-30")  <= as.Date(d_764863765)),
          MW = (as.Date(d_173836415_d_266600170_d_319972665_d_661940160) < as.Date("2024-09-30") ) &
            (is.na(d_195145666) | as.Date("2024-09-30")  <= as.Date(d_195145666)),
          COVID = as.Date(d_556788178) < as.Date("2024-09-30")  &
            as.Date(d_556788178) >= as.Date("2023-07-05") &
            (is.na(d_784810139) | as.Date("2024-09-30")  <= as.Date(d_784810139))) %>%
  pivot_longer(
    cols = c(BOH, MRE, SAS, LAW, BUM, BU, MW, COVID),
    names_to = "CES_timeframe",
    values_to = "is_in_timeframe"
  ) %>%
  filter(is_in_timeframe) %>%  # Keep only rows where the condition is TRUE
  group_by(CES_timeframe) %>%
  tally()



###############################################################################

after_CES <- cbind(BL_CES, BL_time_eligible3)
after_CES <- after_CES[c(1,6,8,5,3,2,7,4), c(1,2,4)] # row order BOH, MRE, SAS, LAW, BUM, BU, MW, COVID, and remove repeated column
colnames(after_CES) <- c("Survey", "n", "eligible")

after_CES_table <- after_CES %>%
  mutate(Percentage = (n / eligible) * 100,
         N_percent = paste0(formatC(n, big.mark = ",", format = "d"), 
                            " (", round(Percentage, digits = 2), "%)")) %>% 
  dplyr::rename('Eligible for Survey' = eligible,
         'N%' = N_percent) %>% 
    select('Survey', 'N%', 'Eligible for Survey')


knitr::kable(after_CES_table,
             caption = 'Table 7.5. Baseline Survey Completion Within 30 days of Connect Experience Survey Survey Completion', 
             booktabs=T, linesep = "", row.names=FALSE, align=c("l", "c", "c")) %>% 
  kable_styling(latex_options = "scale_down") %>% 
  footnote(general = "Note: Percentages calculated among those who were eligible but had not yet completed the survey at the time of CES invitation.", 
           general_title = "",
         footnote_as_chunk = TRUE, 
         escape = FALSE, 
         threeparttable = TRUE)


```




\FloatBarrier
\newpage                   
# 2026 ROI Preference Survey
The 2026 ROI Preference Survey is available to participants from January 9th to February 25 2026. All participants who were verified on or before August 1, 2025, who are not withdrawn or deceased, and did not refuse all future activities or all future surveys were eligible.
```{r roipref, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}


####### Completion of 2026 ROI Pref Among Eligible Participants (like table 4.1)
ROI_comp_elg <- all_data %>% filter(roicomplt!="Not Eligible") %>%
  mutate(roicomplt = factor(roicomplt, levels=c("Not Started", "Started", "Submitted"))) %>%
  select(Site, roicomplt) %>% dplyr::arrange(Site,roicomplt) %>%
  tbl_cross(
  row = Site,
  col = roicomplt,
  label = list(roicomplt ~ "Survey Completion",Site~"Site"),
  percent = "row",
  digits=c(0,2),
  margin_text="Total ROI Pref Eligible Participants")

ROI_comp_elg[["table_body"]]$stat_0 <- sapply(strsplit(ROI_comp_elg[["table_body"]]$stat_0," "),"[",1)

ROI_comp_elg %>%
  modify_header(stat_0 = "Total ROI Pref Eligible Participants") %>%
  modify_caption("Table 8.1. Completion of 2026 ROI Pref Among Eligible Participants") %>%
  as_kable() %>%   
  kable_styling(latex_options = c("scale_down", "hold_position"))


```


```{r roibaseline, echo=FALSE, warning=FALSE, message=FALSE, results='asis'}
#####  Completion of 2026 ROI Pref by Baseline Data Completeness, similar to table 4.2

ROI_comp_BL_all <- all_data %>%  filter(roicomplt!="Not Eligible")

ROI_comp_BL <- create_tbl_cross2(ROI_comp_BL_all, "completion", "roicomplt", "row", "Completion", "ROI Completion", "Total ROI Pref Eligible Participants")
colnames(ROI_comp_BL)[5] <- "Total ROI Pref Eligible Participants"


knitr::kable(ROI_comp_BL,
             caption='Table 8.2. Completion of 2026 ROI Pref by Baseline Data Completeness',
             row.names=FALSE, align=c("l","c","c","c","c"), booktabs = TRUE) %>%
    kable_styling(latex_options = "scale_down") %>%
    add_indent(seq(1, nrow(ROI_comp_BL) - 1)) %>%  landscape()
```
```{r ROI_start_stop, echo=FALSE, warning=FALSE, message=FALSE}

##### Back to wanting all participants, whether or not they finished Module 1. So switching back to all_data df


ROI_time <- all_data %>%
  filter(roicomplt=="Submitted") %>%
  mutate(compTM_roi = as.numeric(difftime(as.POSIXct(ymd_hms(d_543379310)), as.POSIXct(ymd_hms(d_993557295)), units="mins")),
         permission = case_when(compTM_roi<5 ~ "Under 5 Minutes",
                                compTM_roi<10 ~ "5-10 Minutes",
                                compTM_roi<15 ~ "10-15 Minutes",
                                compTM_roi<20 ~ "15-20 Minutes",
                                compTM_roi<30 ~ "20-30 Minutes",
                                compTM_roi>=30 ~ "30+ Minutes"),
         permission = factor(permission, levels=c("Under 5 Minutes", "5-10 Minutes", "10-15 Minutes",
                                                   "15-20 Minutes", "20-30 Minutes", "30+ Minutes")))  %>%
    group_by(permission) %>% tally() %>%
  mutate(Percentage = (n / sum(n)) * 100)



summary_row <- data.frame(permission = "Total Submitted ROI Survey",
                          n = sum(ROI_time$n),
                          Percentage = 100)


ROI_TM <- rbind(ROI_time, summary_row) %>%
  mutate(N_percent = paste0(formatC(n, big.mark = ",", format = "d"),
                            " (", round(Percentage, digits = 1), "%)"),
         Cumulative_Percentage = round(cumsum(Percentage), digits=2))
ROI_TM$Cumulative_Percentage[nrow(ROI_TM)] <- 100

ROI_TM <- ROI_TM %>%
  select(permission, N_percent, Cumulative_Percentage) %>%
  dplyr::rename(`Completion Time` = permission, `N%` = N_percent,
         'Cumulative Percentage' = Cumulative_Percentage)


knitr::kable(ROI_TM, #format.args = list(big.mark = ","),
             caption = 'Table 8.3. 2026 ROI Pref Completion Time from Start to Submit \n Among Eligible Participants That Submitted the Survey',
             booktabs=T, linesep = "", row.names=FALSE, align=c("l", "c", "c")) %>%
  add_indent(c(1:(nrow(ROI_TM)-1))) %>%
  kable_styling(latex_options = "scale_down") #c("scale_down","hold_position"))

```


```{r ROI_trigger, echo=FALSE, warning=FALSE, message=FALSE}

## Time from ROI trigger to submission of ROI survey

# SELECT DISTINCT token, notification_time as ROI_notif
# FROM `nih-nci-dceg-connect-dev.FlatConnect.notifications`
# WHERE category = '2026 Return of Results Preference Survey Reminders'
#   AND attempt IN ('1st contact', '1st contact group 2');

trig_roi <- bq_project_query(project,
query="SELECT distinct(token), notification_time as ROI_notif FROM `nih-nci-dceg-connect-prod-6d04.FlatConnect.notifications`
where category='2026 Return of Results Preference Survey Reminders'")
trigger_ROI <- bigrquery::bq_table_download(trig_roi,bigint = "integer64")

trigger_time_ROI <- left_join(trigger_time, trigger_ROI, by="token")


# For submitted cases, compute days from trigger to submission.

trig_time <- trigger_time_ROI %>%
  filter(roicomplt == "Submitted") %>%
  select(Connect_ID, d_543379310, ROI_notif, roicomplt) %>%
  mutate(
    trigTM_roi = as.numeric(
      difftime(
        ymd_hms(d_543379310),
        ROI_notif,
        units = "days"
      )
    )
  )


Trig_table = trig_time %>%
  dplyr::summarize('N'=n(),
                   Min = round(min(trigTM_roi, na.rm = TRUE), digits=2),
                   Q1 = round(quantile(trigTM_roi, 0.25, na.rm = TRUE), digits=2),
                   Median = round(median(trigTM_roi, na.rm = TRUE), digits=2),
                   Mean = round(mean(trigTM_roi, na.rm = TRUE),  digits=2),
                   SD= round(sd(trigTM_roi, na.rm = TRUE), digits=2),
                   Q3 = round(quantile(trigTM_roi, 0.75, na.rm = TRUE), digits=2),
                   'Perc.90' = round(quantile(trigTM_roi, 0.90, na.rm = TRUE), digits=2),
                   Max = round(max(trigTM_roi, na.rm = TRUE), digits=2))

knitr::kable(Trig_table,
             caption = 'Table 8.4. 2026 ROI Pref Completion from Trigger to Submit for \n Verified Participants, in Days',
             row.names=FALSE, format.args = list(big.mark = ","), linesep = "",
             booktabs = T, align=c("l", "c", "c", "c", "c", "c", "c", "c", "c")) %>%
  kable_styling(latex_options = c("scale_down","hold_position"))

```



```{r BL_ROI_timeframe, echo=FALSE, warning=FALSE, message=FALSE}




################   Numerator  ##############

#Completed ROI before or on the same day as BL survey-- now within 30 days
BL_ROI <- trigger_time_ROI %>%
  filter(roicomplt == "Submitted") %>%
    mutate(BOH = as.Date(d_543379310) <= as.Date(d_517311251) & difftime(as.Date(d_517311251), as.Date(d_543379310), units="days") <31,
         MRE = as.Date(d_543379310) <= as.Date(d_832139544) & difftime( as.Date(d_832139544), as.Date(d_543379310), units="days") <31,
         SAS = as.Date(d_543379310) <= as.Date(d_770257102) & difftime( as.Date(d_770257102), as.Date(d_543379310), units="days") <31,
         LAW = as.Date(d_543379310) <= as.Date(d_264644252) & difftime( as.Date(d_264644252), as.Date(d_543379310), units="days") <31,
         BUM = (as.Date(BUM_time) < as.Date(ROI_notif) ) & (as.Date(d_543379310) <= as.Date(d_222161762)) & difftime( as.Date(d_222161762), as.Date(d_543379310), units="days") <31,
         BU = (as.Date(BU_time) < as.Date(ROI_notif) ) & (as.Date(d_543379310) <= as.Date(d_764863765)) & difftime( as.Date(d_764863765), as.Date(d_543379310), units="days") <31,
         MW = (as.Date(d_173836415_d_266600170_d_319972665_d_661940160) < as.Date(ROI_notif)) &
           (as.Date(d_543379310) <= as.Date(d_195145666)) & difftime( as.Date(d_195145666), as.Date(d_543379310), units="days") <31,
         COVID = (as.Date(d_556788178) < as.Date(ROI_notif)) & (as.Date(d_556788178) >= as.Date("2023-07-05")) &
           (as.Date(d_543379310) <= as.Date(d_784810139)) & difftime( as.Date(d_784810139),as.Date(d_543379310),units="days") <31) %>%
  pivot_longer(
    cols = c(BOH, MRE, SAS, LAW, BUM, BU, MW, COVID),
    names_to = "roi_timeframe",
    values_to = "is_in_timeframe"
  ) %>%
  filter(is_in_timeframe) %>%  # Keep only TRUE rows
  group_by(roi_timeframe) %>%
  tally()


#############    Denominator #################

## Determine when a person was QOL eligible
# trigger_time <- trigger_time %>%
#   mutate(trig = case_when(d_914594314 < as.Date("2023-12-01") ~ ymd_hms(notification_time),
#                           TRUE ~ ymd_hms(d_914594314) + days(90)))

## Determine when a participant was BL survey eligible
#MRE/SAS/LAW- once BOH completed ----   d_517311251
#BUM/BU- when notified by email
#MW- when notified the MW kit was shipped
#COVID- pushed to prod on 7/5/2023 and requires biospecimen donation





## Those that are eligible for ROI, and eligible for whichever BL module, but hadn't completed that BL module upon ROI eligibility activation
ROI_BL_time_eligible <- trigger_time_ROI %>%
  filter(!is.na(roicomplt) & roicomplt != "Not Eligible") %>%
  mutate( BOH = is.na(d_517311251) | (as.Date(ROI_notif) <= as.Date(d_517311251)),
          MRE = !is.na(d_517311251) & (is.na(d_832139544) | as.Date(ROI_notif) <= as.Date(d_832139544)),
          SAS = !is.na(d_517311251) & (is.na(d_770257102) | as.Date(ROI_notif) <= as.Date(d_770257102)),
          LAW = !is.na(d_517311251) & (is.na(d_264644252) | as.Date(ROI_notif) <= as.Date(d_264644252)),
          BUM = (as.Date(BUM_time) < as.Date(ROI_notif))  & (is.na(d_222161762) | as.Date(ROI_notif) <= as.Date(d_222161762)),
          BU = (as.Date(BU_time) < as.Date(ROI_notif))  & (is.na(d_764863765) | as.Date(ROI_notif) <= as.Date(d_764863765)),
          MW = (as.Date(d_173836415_d_266600170_d_319972665_d_661940160) < as.Date(trig)) &
            (is.na(d_195145666) | as.Date(trig) <= as.Date(d_195145666)),
          COVID = as.Date(d_556788178) < as.Date(trig) &
            as.Date(d_556788178) >= as.Date("2023-07-05") &
            (is.na(d_784810139) | as.Date(trig) <= as.Date(d_784810139))) %>%
  pivot_longer(
    cols = c(BOH, MRE, SAS, LAW, BUM, BU, MW, COVID),
    names_to = "roi_timeframe",
    values_to = "is_in_timeframe"
  ) %>%
  filter(is_in_timeframe) %>%  # Keep only rows where the condition is TRUE
  group_by(roi_timeframe) %>%
  tally()



###############################################################################

after_ROI <- cbind(BL_ROI, ROI_BL_time_eligible)
after_ROI <- after_ROI[c(1,6,8,5,3,2,7,4), c(1,2,4)] # row order BOH, MRE, SAS, LAW, BUM, BU, MW, COVID, and remove repeated column
colnames(after_ROI) <- c("Survey", "n", "eligible")

after_ROI_table <- after_ROI %>%
  mutate(Percentage = (n / eligible) * 100,
         N_percent = paste0(formatC(n, big.mark = ",", format = "d"),
                            " (", round(Percentage, digits = 2), "%)")) %>%
  dplyr::rename('Eligible for Survey' = eligible,
         'N%' = N_percent) %>%
    select('Survey', 'N%', 'Eligible for Survey')


knitr::kable(after_ROI_table,
             caption = 'Table 8.5. Baseline Survey Completion Within 30 days of 2026 ROI Pref Completion ',
             booktabs=T, linesep = "", row.names=FALSE, align=c("l", "c", "c")) %>%
  kable_styling(latex_options = "scale_down") %>%
  footnote(general = "Note: Percentages calculated among those who were eligible but had not yet completed the survey at the time of ROI invitation.",
           general_title = "",
         footnote_as_chunk = TRUE,
         escape = FALSE,
         threeparttable = TRUE)



```


\FloatBarrier

```{r ROI_ver_time, echo=FALSE, warning=FALSE, message=FALSE}

# using release date as January 09 2026:

roi_ver <- all_data %>%
  filter(roicomplt != "Not Eligible") %>%
  mutate(
    roi_ver_surv = case_when(
      as.Date(d_914594314) < as.Date("2025-01-09") ~ "More than 1 Year",
      as.Date(d_914594314) < as.Date("2025-07-09") ~ "6 Months - 1 Year",
      as.Date(d_914594314) < as.Date("2025-10-09") ~ "3 Months - 6 Months",
      as.Date(d_914594314) >= as.Date("2025-10-09") ~ "At 3 Months"
    ),
    roi_ver_surv = factor(
      roi_ver_surv,
      levels = c(
        "More than 1 Year",
        "6 Months - 1 Year",
        "3 Months - 6 Months",
        "At 3 Months"
      )
    )
  )



roi_ver_df <- create_tbl_cross2(roi_ver, "roi_ver_surv", "roicomplt", "row", "Time from Verification to ROI Survey Release", "Survey Completion",
                                "Total ROI Pref Eligible Participants")

colnames(roi_ver_df)[5] <- "Total ROI Pref Eligible Participants"
knitr::kable(roi_ver_df,
             caption='Table 8.6. 2026 ROI Pref Completion By Time from Verification to ROI Survey Release',
             row.names=FALSE, align=c("l","c","c","c","c"), booktabs = TRUE) %>%
    kable_styling(latex_options = "scale_down") %>%
    add_indent(seq(1, nrow(roi_ver_df) - 1)) %>%  landscape()



```




```{r ROI_BySex_ByAge, echo=FALSE, warning=FALSE, message=FALSE, results='asis'}


ROI_Comp_by_Sex <- all_data %>% filter(roicomplt!="Not Eligible") %>%
  mutate(roicomplt = factor(roicomplt, levels=c("Not Started", "Started", "Submitted"))) %>%
  select(sex, roicomplt) %>% dplyr::arrange(sex,roicomplt) %>%
  tbl_cross(
  row = sex,
  col = roicomplt,
  label = list(roicomplt ~ "Survey Completion",sex~"Sex"),
  percent = "row",
  digits=c(0,2),
  margin_text="Total ROI Pref Eligible Participants")


ROI_Comp_by_Sex_table <- ROI_Comp_by_Sex %>%
  modify_header(stat_0 = "Total ROI Pref Eligible Participants") %>%
  modify_caption("Table 8.7. 2026 ROI Pref Completion Rate by Site Defined Sex  \n  Among Eligible Participants") %>%
  as_kable_extra(escape = FALSE, addtl_fmt = TRUE) %>% kable_styling(latex_options = c("scale_down","hold_position"))


# leave this?
add_footnote(ROI_Comp_by_Sex_table, "Note: Sex defined as the de-identified sex data reported by sites at time of invitation.",
             notation = "none")


ROI_Comp_by_Age <- all_data %>% filter(roicomplt!="Not Eligible") %>%
  mutate(roicomplt = factor(roicomplt, levels=c("Not Started", "Started", "Submitted"))) %>%
  select(age, roicomplt) %>% dplyr::arrange(age,roicomplt) %>%
  tbl_cross(
  row = age,
  col = roicomplt,
  label = list(roicomplt ~ "Survey Completion",age~"Age"),
  percent = "row",
  digits=c(0,2),
  margin_text="Total ROI Pref Eligible Participants")


ROI_Comp_by_Age <- ROI_Comp_by_Age %>%
  modify_header(stat_0 = "Total ROI Pref Eligible Participants") %>%
  modify_caption("Table 8.8. 2026 ROI Pref Completion Rate by Age \n Among Eligible Participants") %>%
  as_kable_extra(escape = FALSE, addtl_fmt = TRUE)  %>% kable_styling(latex_options = c("scale_down","hold_position"))


# leave this?
add_footnote(ROI_Comp_by_Age, "Note: Age defined as the de-identified age data reported by sites at time of invitation, not current age at time of survey completion.",
             notation="none")


```



```{r ROI_By_Race, echo=FALSE, warning=FALSE, message=FALSE, results='asis'}


ROI_Comp_by_race <- m1_comp %>% filter(roicomplt!="Not Eligible") %>%
  mutate(roicomplt = factor(roicomplt, levels=c("Not Started", "Started", "Submitted"))) %>%
  select(race, roicomplt) %>% dplyr::arrange(race,roicomplt) %>%
  tbl_cross(
  row = race,
  col = roicomplt,
  label = list(roicomplt ~ "Survey Completion",race~"Race"),
  percent = "row",
  digits=c(0,2),
  margin_text="Total ROI Pref Eligible Participants")


ROI_Comp_by_race <- ROI_Comp_by_race %>%
  modify_header(stat_0 = "Total ROI Pref Eligible \n Participants") %>%
  modify_caption("Table 8.9. 2026 ROI Pref Completion Rate by Race \n Among Eligible Participants") %>%
  as_kable_extra(escape = FALSE, addtl_fmt = TRUE) %>% kable_styling(latex_options = c("scale_down","hold_position"))

# will we need this for anything? keep this

roireduced <- all_data %>% filter(d_949302066 != 231311385 & roicomplt!="Not Eligible") # Those who are eligible for ROI but didn't complete mod1 yet


# leave this or something like it?

add_footnote(ROI_Comp_by_race, paste0('Note: In order to determine race, Module 1 must first be completed. There are ', dim(roireduced)[[1]] , ' ROI eligible participants that have either not started or not finished Module 1.'),
             notation="none")


```


```{r ROI_By_SiteRace, echo=FALSE, error=FALSE, message=FALSE, warning=FALSE}

ROI_by_race <- all_data %>% filter(roicomplt!="Not Eligible")

ROI_by_race_df <- create_tbl_cross2(ROI_by_race, "race", "roicomplt", "row", "Race", "ROI Pref \n Survey Completion", "Total Verified Participants")


# language -- verified (this example ) vs. eligible (github request)
knitr::kable(ROI_by_race_df,
             caption="Table 8.9.a 2026 ROI Pref Completion Rate by Site Defined Race \n Among Verified Participants",
             row.names=FALSE, align=c("l","c","c","c","c","c"), booktabs = TRUE) %>%
    kable_styling(latex_options = "scale_down") %>%
    add_indent(seq(1, nrow(BL_by_Race_df) - 1)) %>%  landscape() %>%
    footnote(general = "Note: Race defined as the de-identified race data reported by sites at time of invitation.",
             general_title = "")

```


```{r ROI_By_Race_And_Sex, echo=FALSE, warning=FALSE, message=FALSE, results='asis'}

ROI_Comp_by_sex_race <- m1_comp %>% filter(roicomplt!="Not Eligible") %>%
  mutate(roicomplt = factor(roicomplt, levels=c("Not Started", "Started", "Submitted"))) %>%
  select(sex_race, roicomplt) %>% dplyr::arrange(sex_race,roicomplt) %>%
  tbl_cross(
  row = sex_race,
  col = roicomplt,
  label = list(roicomplt ~ "Survey Completion",sex_race~"Sex and Race"),
  percent = "row",
  digits=c(0,2),
  margin_text="Total ROI Pref Eligible Participants")


ROI_Comp_by_sex_race <- ROI_Comp_by_sex_race %>%
  modify_header(stat_0 = "Total ROI Pref Eligible Participants") %>%
  modify_caption("Table 8.10. 2026 ROI Pref Completion Rate by Sex and Race \n Among Eligible Participants") %>%
  as_kable_extra(escape = FALSE, addtl_fmt = TRUE)

reduced <- all_data %>% filter(d_949302066 != 231311385 & roicomplt!="Not Eligible") # Those who are eligible for ROI but didn't complete mod1 yet

ROI_Comp_by_sex_race %>% kable_styling(latex_options = c("scale_down","hold_position")) %>%
  footnote(general = paste0('In order to determine race, Module 1 must first be completed. There are ', dim(reduced)[[1]] , ' ROI eligible participants that have either not started or not finished Module 1.'),general_title = "Note: ", footnote_as_chunk = T)


```


```{r ROI_By_Demographic, echo=FALSE, warning=FALSE, message=FALSE, results='asis'}

ROI_Comp_by_Demographic <- all_data_long %>%
  filter(roicomplt != "Not Eligible") %>%
  mutate(roicomplt = factor(roicomplt, levels = c("Not Started", "Started", "Submitted")),
         Demographic_Group = factor(Demographic_Group, levels=c("White Women","Black Men","Women Under 45","Women Over 45","Men Under 45","Men Over 45"))) %>%
  select(Demographic_Group, roicomplt) %>%
  tbl_cross(
    row = Demographic_Group,
    col = roicomplt,
    label = list(roicomplt ~ "Survey Completion", Demographic_Group ~ "Demographic"),
    percent = "row",
    digits = c(0, 2),
    margin_text = "Total"
  )


ROI_Comp_by_Demographic <- ROI_Comp_by_Demographic %>%
  modify_header(stat_0 = "Total") %>%
  modify_caption("Table 8.11. 2026 ROI Pref Completion Rate \n by Demographic Among Eligible Participants") %>%
  as_kable_extra(escape = FALSE, addtl_fmt = TRUE)

# Style the table output
ROI_Comp_by_Demographic %>% kable_styling(latex_options = c("scale_down", "hold_position"))  %>%
  footnote(general = "Participants may be counted more then once in these categories.",general_title = "Note: ", footnote_as_chunk = T)


```




# Survey Metrics by Language Completed
Spanish was made available in MyConnect beginning August 1, 2024. All surveys are now available in both English and Spanish. Surveys released after 08/01/2024 were available in both English and Spanish at time of survey release.
\FloatBarrier
```{r Pref_Lang_Time_All, echo=FALSE, warning=FALSE, message=FALSE}


pref_lang_site <- all_data %>% 
  tbl_cross(
    col = Pref_lang,
    row = Site,
    digits=c(0,2),
    percent = "column",
    label=list(Pref_lang="Preferred Language",
                Site = "Site"),
    missing="ifany",
    margin_text="Total") %>% 
  modify_header(stat_0 = "Total") %>%
  modify_caption("Table 9.1. Preferred Language by Site") %>%
  as_kable_extra(escape = FALSE, addtl_fmt = TRUE) %>%  
  kable_styling(latex_options = "scale_down") 

add_footnote(pref_lang_site, "Note: Preferred language is based on language of signed consent form and current user profile language status",
             notation="none")

```






```{r Survey_Flag_Setup, echo=FALSE, error=FALSE, message=FALSE, warning=FALSE}


## SSN survey is not viewable in BQ so we will not have the language flag for that survey

## d_784119588 is a variable for survey language preference and is in every single survey table EXCEPT DHQ
## DHQ is an outside survey with the participants table variable d_748726394 for language
    ## in the queries below named both language variables 'language' too be able to run seemlessly through the survey loops
## d_255077064 is the Consent and Notification Language set in the participants table



queries <- list(
  m1_lang_c = "SELECT pts.Connect_ID, m1.d_784119588 as language, d_255077064
                FROM `nih-nci-dceg-connect-prod-6d04.FlatConnect.participants` pts
                left join `nih-nci-dceg-connect-prod-6d04.FlatConnect.module1_v2` m1
                on m1.Connect_ID=pts.Connect_ID
                WHERE pts.Connect_ID IS NOT NULL and d_949302066='231311385' and
                (pts.d_512820379='486306141' OR pts.d_512820379='854703046') and pts.d_821247024 = '197316935'",
  #module1 v1 doesn't need to be merged in- language wasn't an option then so everyone is English by default. The case when below allows null survey language variables to be set to English already
  m2_lang_c = "SELECT pts.Connect_ID, m2.d_784119588 as language, d_255077064 
                FROM `nih-nci-dceg-connect-prod-6d04.FlatConnect.participants` pts
                left join `nih-nci-dceg-connect-prod-6d04.FlatConnect.module2_v2` m2
                on m2.Connect_ID=pts.Connect_ID
                WHERE pts.Connect_ID IS NOT NULL and d_536735468='231311385' and 
                (pts.d_512820379='486306141' OR pts.d_512820379='854703046') and pts.d_821247024 = '197316935'",
  #module2 v1 doesn't need to be merged in- language wasn't an option then so everyone is English by default. The case when below allows null survey language variables to be set to English already
  m3_lang_c = "SELECT pts.Connect_ID, m3.d_784119588 as language, d_255077064 
                FROM `nih-nci-dceg-connect-prod-6d04.FlatConnect.participants` pts
                left join `nih-nci-dceg-connect-prod-6d04.FlatConnect.module3_v1` m3
                on m3.Connect_ID=pts.Connect_ID
                WHERE pts.Connect_ID IS NOT NULL and d_976570371='231311385' and 
                (pts.d_512820379='486306141' OR pts.d_512820379='854703046') and pts.d_821247024 = '197316935'",
  m4_lang_c = "SELECT pts.Connect_ID, m4.d_784119588 as language, d_255077064 
                FROM `nih-nci-dceg-connect-prod-6d04.FlatConnect.participants` pts
                left join `nih-nci-dceg-connect-prod-6d04.FlatConnect.module4_v1` m4
                on m4.Connect_ID=pts.Connect_ID
                WHERE pts.Connect_ID IS NOT NULL and pts.d_663265240='231311385' and 
                (pts.d_512820379='486306141' OR pts.d_512820379='854703046') and pts.d_821247024 = '197316935'",
  BUM_lang_c = "SELECT pts.Connect_ID, bum.d_784119588 as language, d_255077064 
                FROM `nih-nci-dceg-connect-prod-6d04.FlatConnect.participants` pts
                left join `nih-nci-dceg-connect-prod-6d04.FlatConnect.bioSurvey_v1` bum
                on bum.Connect_ID=pts.Connect_ID
                WHERE pts.Connect_ID IS NOT NULL and d_265193023='231311385' and 
                (pts.d_512820379='486306141' OR pts.d_512820379='854703046') and pts.d_821247024 = '197316935'",
  BU_lang_c = "SELECT pts.Connect_ID, bu.d_784119588 as language, d_255077064
                FROM `nih-nci-dceg-connect-prod-6d04.FlatConnect.participants` pts
                left join `nih-nci-dceg-connect-prod-6d04.FlatConnect.clinicalBioSurvey_v1` bu 
                on bu.Connect_ID=pts.Connect_ID
                WHERE pts.Connect_ID IS NOT NULL and d_253883960='231311385' and 
                (pts.d_512820379='486306141' OR pts.d_512820379='854703046') and pts.d_821247024 = '197316935'",
  CV_lang_c = "SELECT pts.Connect_ID, cv.d_784119588 as language, d_255077064 
                FROM `nih-nci-dceg-connect-prod-6d04.FlatConnect.participants` pts
                left join `nih-nci-dceg-connect-prod-6d04.FlatConnect.covid19Survey_v1` cv
                on cv.Connect_ID=pts.Connect_ID
                WHERE pts.Connect_ID IS NOT NULL and d_220186468='231311385' and 
                DATE(d_268176409) >= '2023-07-05' and --stand alone covid survey only
                (pts.d_512820379='486306141' OR pts.d_512820379='854703046') and pts.d_821247024 = '197316935'",  
  Mens_lang_c = "SELECT pts.Connect_ID, mns.d_784119588 as language, d_255077064 
                FROM `nih-nci-dceg-connect-prod-6d04.FlatConnect.participants` pts
                left join `nih-nci-dceg-connect-prod-6d04.FlatConnect.menstrualSurvey_v1` mns
                on mns.Connect_ID=pts.Connect_ID
                WHERE pts.Connect_ID IS NOT NULL and d_459098666='231311385' and 
                (pts.d_512820379='486306141' OR pts.d_512820379='854703046') and pts.d_821247024 = '197316935'",
  MW_lang_c = "SELECT pts.Connect_ID, mw.d_784119588 as language, d_255077064 
                FROM `nih-nci-dceg-connect-prod-6d04.FlatConnect.participants` pts
                left join `nih-nci-dceg-connect-prod-6d04.FlatConnect.mouthwash_v1` mw
                on mw.Connect_ID=pts.Connect_ID
                WHERE pts.Connect_ID IS NOT NULL and d_547363263='231311385' and 
                (pts.d_512820379='486306141' OR pts.d_512820379='854703046') and pts.d_821247024 = '197316935'",
  QOL_lang_c = "SELECT pts.Connect_ID, qol.d_784119588 as language, d_255077064
                FROM `nih-nci-dceg-connect-prod-6d04.FlatConnect.participants` pts
                left join `nih-nci-dceg-connect-prod-6d04.FlatConnect.promis_v1` qol
                on qol.Connect_ID=pts.Connect_ID
                WHERE pts.Connect_ID IS NOT NULL and d_320303124='231311385' and 
                (pts.d_512820379='486306141' OR pts.d_512820379='854703046') and pts.d_821247024 = '197316935'",
  CES_lang_c = "SELECT pts.Connect_ID, ces.d_784119588 as language, d_255077064
                FROM `nih-nci-dceg-connect-prod-6d04.FlatConnect.participants` pts
                left join `nih-nci-dceg-connect-prod-6d04.FlatConnect.experience2024` ces
                on ces.Connect_ID=pts.Connect_ID
                WHERE pts.Connect_ID IS NOT NULL and d_956490759='231311385' and 
                (pts.d_512820379='486306141' OR pts.d_512820379='854703046') and pts.d_821247024 = '197316935'",
  CSH_lang_c = "SELECT pts.Connect_ID, csh.d_784119588 as language, d_255077064
                FROM `nih-nci-dceg-connect-prod-6d04.FlatConnect.participants` pts
                left join `nih-nci-dceg-connect-prod-6d04.FlatConnect.cancerScreeningHistorySurvey` csh
                on csh.Connect_ID=pts.Connect_ID
                WHERE pts.Connect_ID IS NOT NULL and d_176068627='231311385' and 
                (pts.d_512820379='486306141' OR pts.d_512820379='854703046') and pts.d_821247024 = '197316935'",
  DHQ_lang_c = "SELECT Connect_ID, d_748726394  as language, d_255077064 -- here dhq language is in the participants table NOT the DHQ table
                FROM `nih-nci-dceg-connect-prod-6d04.FlatConnect.participants`
                WHERE Connect_ID IS NOT NULL and d_692560814='231311385'  and
               (d_512820379='486306141' OR d_512820379='854703046') and d_821247024 = '197316935'"
  
  
#   ROI_lang_c = "SELECT pts.Connect_ID, csh.d_784119588 as language, d_255077064
#                 FROM `nih-nci-dceg-connect-prod-6d04.FlatConnect.participants` pts
#                 left join `nih-nci-dceg-connect-prod-6d04.FlatConnect.cancerScreeningHistorySurvey` csh
#                 on csh.Connect_ID=pts.Connect_ID
#                 WHERE pts.Connect_ID IS NOT NULL and d_176068627='231311385' and 
#                 (pts.d_512820379='486306141' OR pts.d_512820379='854703046') and pts.d_821247024 = '197316935'"
# 
)


results_list <- list()


## Download all the language preferences, both in consent and per survey, to compare

for (name in names(queries)) {
  query <- queries[[name]]
  query_result <- bq_project_query(project, query)
  data <- bq_table_download(query_result, bigint = "integer64")
  results_list[[name]] <- data
}


m1_lang <- results_list$m1_lang_c
m2_lang <- results_list$m2_lang_c
m3_lang <- results_list$m3_lang_c
m4_lang <- results_list$m4_lang_c
BUM_lang <- results_list$BUM_lang_c
BU_lang <- results_list$BU_lang_c
CV_lang <- results_list$CV_lang_c
Mens_lang <- results_list$Mens_lang_c
MW_lang <- results_list$MW_lang_c
QOL_lang <- results_list$QOL_lang_c
CES_lang <- results_list$CES_lang_c
CSH_lang <- results_list$CSH_lang_c
DHQ_lang <- results_list$DHQ_lang_c
# ROI_lang <- results_list$ROI_lang_c



```


\FloatBarrier
```{r Svy_Lang_Diff, echo=FALSE, warning=FALSE, message=FALSE, results='asis'}

#must match the order for survey_acronyms in the chunk below
survey_dfs <- list(m1_lang, m2_lang, m3_lang, m4_lang, BUM_lang, BU_lang, CV_lang, Mens_lang, MW_lang, QOL_lang, DHQ_lang, CSH_lang, CES_lang 
                   # ROI_lang
                   ) 

# Initialize an empty data frame to store results for all participants
all_scenarios <- data.frame(Connect_ID = character(), Flag = character(), Pref_lang = character(), stringsAsFactors = FALSE)

# Loop through each survey data frame
for (current_df in survey_dfs) {
  current_df <- current_df %>%
    mutate(
      Flag = ifelse(is.na(language), NA, 
                    ifelse(language == 773342525, "Spanish", "English")), 
      Pref_lang = case_when(d_255077064 == 773342525 ~ "Spanish", TRUE ~ "English")
    )
  
  # Extract relevant columns and add to the scenario tracking data frame
  participant_scenarios <- current_df %>%
    select(Connect_ID, Flag, Pref_lang)
  
  all_scenarios <- bind_rows(all_scenarios, participant_scenarios)
}

# Summarize the scenario for each participant
final_scenarios <- all_scenarios %>%
  group_by(Connect_ID) %>%
  summarize(
    Flag_set = unique(na.omit(Flag)), # Remove NAs from Flags
    Pref_lang_set = unique(Pref_lang),
    scenario = case_when(
      length(Flag_set) == 0 ~ "No survey language preference has been made", 
      all(Flag_set == Pref_lang_set) ~ "Survey Flags and Preferred Language Consistent",
      any(Flag_set != Pref_lang_set) ~ "Any Survey Flag Inconsistent with Preferred Language"
    )
  ) %>%
  ungroup()

# Summarize the counts for each scenario
scenario_counts <- final_scenarios %>%
  count(scenario) %>%
  dplyr::rename(Scenario = scenario, 'Total Participants' = n)

consist <- knitr::kable(scenario_counts,
                        caption = "Table 9.2. Consistency of Language Choice in Survey Completion",
                        row.names = FALSE, align = c("l", "c"), digits = 2, booktabs = TRUE) %>%
  kable_styling(latex_options = "scale_down") %>% 
  footnote(general="Those who do not start any surveys will not have survey flags, and thus not be counted in this table. Those that start but do not complete a survey will still choose a survey language.", 
           general_title = "Note: ", 
           footnote_as_chunk = T)

knitr::kable(scenario_counts,
             caption = "Table 9.2. Consistency of Language Choice in Survey Completion",
             row.names = FALSE, align = c("l", "c"), digits = 2, booktabs = TRUE) %>%
  kable_styling(latex_options = "scale_down") %>% 
  footnote(
    general = "Those who do not start any surveys will not have survey flags, and thus not be counted in this table. Those that start but do not complete a survey will still choose a survey language.",
    general_title = "Note: ",
    footnote_as_chunk = TRUE
  )


```

\newpage                        
\FloatBarrier
```{r Svy_Lang_Compare, echo=FALSE, warning=FALSE, message=FALSE, results='asis'}

# must match the order for survey_dfs in the chunk above
survey_acronyms <- c("BOH", "MRE", "SAS", "LAW", "BUM", "BU", "COVID", "MENS", "MW", "QOL", "DHQ", "CSH",  "CES" 
                     # "ROI"
                     ) 


create_table <- function(current_df, current_acronym) {
  if (nrow(current_df) == 0) {
    return(data.frame(Survey = current_acronym, English = 0, Spanish = 0, Total = 0))
  }
  
  all_svry_flags <- current_df %>%
    mutate(Survey = case_when(!is.na(Connect_ID) ~ current_acronym,
                              TRUE ~ "NA"),
           Flag = case_when(language == 773342525 ~ "Spanish", 
                            TRUE ~ "English")) %>%
    tbl_cross(
      col =Flag,
      row = Survey,
      digits = c(0, 2),
      percent = "row",
      label = list(Flag = "Survey Flag",
                   Site = "Survey"),
      missing = "ifany",
      margin_text = "Total") %>%
    modify_header(stat_0 = "Total")
  
  df_all_svry_flags <- as.data.frame(all_svry_flags)
  colnames(df_all_svry_flags)[1] <- "Survey"
  df_all_svry_flags <- df_all_svry_flags[2,]
  
  # Ensure the data frame has consistent columns by adding missing ones with zeros
  expected_columns <- c("Survey", "English", "Spanish", "Total")
  missing_columns <- setdiff(expected_columns, names(df_all_svry_flags))
  
  if (length(missing_columns) > 0) {
    for (col in missing_columns) {
      df_all_svry_flags[[col]] <- 0
    }
  }
  
  df_all_svry_flags <- df_all_svry_flags[expected_columns]
  
  return(df_all_svry_flags)
}

# Initialize empty lists to store the results for each condition
all_flags_list_overall <- list()
all_flags_list_condition1 <- list()
all_flags_list_condition2 <- list()

# Loop through each survey data frame and acronym
for (i in seq_along(survey_dfs)) {
  # Get the current data frame and acronym
  current_df <- survey_dfs[[i]]
  current_acronym <- survey_acronyms[i]
  
  # Overall table
  df_overall <- create_table(current_df, current_acronym)
  all_flags_list_overall[[current_acronym]] <- df_overall
  
  # Spanish
  current_df_cond1 <- current_df %>% filter(d_255077064 == 773342525)
  df_condition1 <- create_table(current_df_cond1, current_acronym)
  all_flags_list_condition1[[current_acronym]] <- df_condition1
  
  # English
  current_df_cond2 <- current_df %>% filter(d_255077064 == 163149180 | is.na(d_255077064))
  df_condition2 <- create_table(current_df_cond2, current_acronym)
  all_flags_list_condition2[[current_acronym]] <- df_condition2
}


final_df_overall <- do.call(rbind, all_flags_list_overall)
final_df_condition1 <- do.call(rbind, all_flags_list_condition1)
final_df_condition2 <- do.call(rbind, all_flags_list_condition2)



knitr::kable(final_df_overall,
               caption = paste0("Table 9.3. Survey Completion by Survey Language \n Among All Participants"),
               row.names = FALSE, align = c("l","c","c","c"), digits = 2, booktabs = TRUE) %>% 
  add_indent(1:nrow(final_df_overall)) %>%  
  kable_styling(latex_options = "scale_down") %>% 
  footnote(general="Note: The DHQ survey is completed in the DHQ Research Platform. Participants are able to toggle between English and Spanish throughout the DHQ survey and the language captured is the language the survey was toggled to at time of submission. All other surveys are completed within MyConnect and participants do not have the option to change their language selection once they start the survey.",
           general_title = "",
           footnote_as_chunk = TRUE,
           escape = FALSE,
           threeparttable = TRUE)

knitr::kable(final_df_condition1,
               caption = paste0("Table 9.3.a. Survey Completion by Survey Language \n Among Participants with Preferred language of Spanish"),
               row.names = FALSE, align = c("l","c","c","c"), digits = 2, booktabs = TRUE) %>% 
  add_indent(1:nrow(final_df_condition1)) %>%  
  kable_styling(latex_options = "scale_down") %>%  
  footnote(general="Note: The DHQ survey is completed in the DHQ Research Platform. Participants are able to toggle between English and Spanish throughout the DHQ survey and the language captured is the language the survey was toggled to at time of submission. All other surveys are completed within MyConnect and participants do not have the option to change their language selection once they start the survey.",
           general_title = "",
           footnote_as_chunk = TRUE,
           escape = FALSE,
           threeparttable = TRUE)

knitr::kable(final_df_condition2,
               caption = paste0("Table 9.3.b. Survey Completion by Survey Language \n Among Participants with Preferred language of English"),
               row.names = FALSE, align = c("l","c","c","c"), digits = 2, booktabs = TRUE) %>% 
  add_indent(1:nrow(final_df_condition2)) %>%  
  kable_styling(latex_options = "scale_down")  %>% 
  footnote(general="Note: The DHQ survey is completed in the DHQ Research Platform. Participants are able to toggle between English and Spanish throughout the DHQ survey and the language captured is the language the survey was toggled to at time of submission. All other surveys are completed within MyConnect and participants do not have the option to change their language selection once they start the survey.",
           general_title = "",
           footnote_as_chunk = TRUE,
           escape = FALSE,
           threeparttable = TRUE)


```


\newpage

\FloatBarrier
```{r BL_start_stop_Lang, echo=FALSE, warning=FALSE, message=FALSE, results='asis'}

start_stop_lang <- function(data, filter_column, filter_value, language_value, target_column) {
    data %>% 
        filter(!!sym(filter_column) == filter_value & Pref_lang == language_value) %>% 
        summarize('N' = n(),
                  Min = min(!!sym(target_column), na.rm = TRUE),
                  Q1 = quantile(!!sym(target_column), 0.25, na.rm = TRUE),
                  Median = median(!!sym(target_column), na.rm = TRUE),
                  Mean = mean(!!sym(target_column), na.rm = TRUE), 
                  SD = sd(!!sym(target_column), na.rm = TRUE),
                  Q3 = quantile(!!sym(target_column), 0.75, na.rm = TRUE),
                  'Perc.90' = quantile(!!sym(target_column), 0.90, na.rm = TRUE),
                  Max = max(!!sym(target_column), na.rm = TRUE))
}

BOH_LangE <- start_stop_lang(all_data, "d_949302066", 231311385, "English", "m1_comp_mins")
MRE_LangE <- start_stop_lang(all_data, "d_536735468", 231311385, "English", "m2_comp_mins")
SAS_LangE <- start_stop_lang(all_data, "d_976570371", 231311385, "English", "m3_comp_mins")
LAW_LangE <- start_stop_lang(all_data, "d_663265240", 231311385, "English", "m4_comp_mins")
DHQ_LangE <- start_stop_lang(all_data, "d_692560814", 231311385, "English", "dhq_comp_mins")
CSH_LangE <- start_stop_lang(all_data, "d_176068627", 231311385, "English", "csh_comp_mins")
# ROI_LangE <- start_stop_lang(all_data, "d_176068627", 231311385, "English", "roi_comp_mins")

BOH_LangSP <- start_stop_lang(all_data, "d_949302066", 231311385, "Spanish", "m1_comp_mins")
MRE_LangSP <- start_stop_lang(all_data, "d_536735468", 231311385, "Spanish", "m2_comp_mins")
SAS_LangSP <- start_stop_lang(all_data, "d_976570371", 231311385, "Spanish", "m3_comp_mins")
LAW_LangSP <- start_stop_lang(all_data, "d_663265240", 231311385, "Spanish", "m4_comp_mins")
DHQ_LangSP <- start_stop_lang(all_data, "d_692560814", 231311385, "Spanish", "dhq_comp_mins")
CSH_LangSP <- start_stop_lang(all_data, "d_176068627", 231311385, "Spanish", "csh_comp_mins")
#  ROI_LangSP <- start_stop_lang(all_data, "d_176068627", 231311385, "Spanish", "roi_comp_mins")


BL_lang_E <- rbind(BOH_LangE, MRE_LangE, SAS_LangE, LAW_LangE)
BL_lang_SP <- rbind(BOH_LangSP, MRE_LangSP, SAS_LangSP, LAW_LangSP)


BL_lang_E[,10] <- c("BOH", "MRE", "SAS", "LAW")
BL_lang_SP[,10] <- c("BOH", "MRE", "SAS", "LAW")

BL_lang_E<- BL_lang_E[, c(10,1:9)]
BL_lang_SP<- BL_lang_SP[, c(10,1:9)]


colnames(BL_lang_E)[1] <- "Section"
colnames(BL_lang_SP)[1] <- "Section"

knitr::kable(BL_lang_E, format.args = list(big.mark = ","), digits=2, 
             caption='Table 9.4.a Time (in minutes) from Start to Submit of Initial Survey Modules for English',
             row.names=FALSE, align=c("l","c","c","c","c","c","c","c","c"), booktabs = TRUE)%>% 
    kable_styling(latex_options = c("scale_down","hold_position")) 

knitr::kable(BL_lang_SP, format.args = list(big.mark = ","), digits=2, 
             caption='Table 9.4.b Time (in minutes) from Start to Submit of Initial Survey Modules for Spanish',
             row.names=FALSE, align=c("l","c","c","c","c","c","c","c","c"),booktabs = TRUE)%>% 
    kable_styling(latex_options = c("scale_down","hold_position")) 


 knitr::kable(DHQ_LangE, format.args = list(big.mark = ","), digits=2,
              caption='Table 9.5.a Time (in minutes) from Start to Submit of 6-month Diet History Questionaire for English',
              row.names=FALSE, align=c("l","c","c","c","c","c","c","c","c"), booktabs = TRUE)%>%
     kable_styling(latex_options = c("scale_down","hold_position"))

 knitr::kable(DHQ_LangSP, format.args = list(big.mark = ","), digits=2,
              caption='Table 9.5.b Time (in minutes) from Start to Submit of 6-month Diet History Questionaire for Spanish',
              row.names=FALSE, align=c("l","c","c","c","c","c","c","c","c"),booktabs = TRUE)%>%
     kable_styling(latex_options = c("scale_down","hold_position"))


 knitr::kable(CSH_LangE, format.args = list(big.mark = ","), digits=2,
              caption='Table 9.6.a Time (in minutes) from Start to Submit of Cancer Screening History Survey for English',
              row.names=FALSE, align=c("l","c","c","c","c","c","c","c","c"), booktabs = TRUE)%>%
     kable_styling(latex_options = c("scale_down","hold_position"))

 knitr::kable(CSH_LangSP, format.args = list(big.mark = ","), digits=2,
              caption='Table 9.6.b Time (in minutes) from Start to Submit of Cancer Screening History Survey for Spanish',
              row.names=FALSE, align=c("l","c","c","c","c","c","c","c","c"),booktabs = TRUE)%>%
     kable_styling(latex_options = c("scale_down","hold_position"))
 
 #  knitr::kable(ROI_LangE, format.args = list(big.mark = ","), digits=2,
 #              caption='Table 9.7.a Time (in minutes) from Start to Submit of ROI Preference Survey for English',
 #              row.names=FALSE, align=c("l","c","c","c","c","c","c","c","c"), booktabs = TRUE)%>%
 #     kable_styling(latex_options = c("scale_down","hold_position"))
 # 
 # knitr::kable(ROI_LangSP, format.args = list(big.mark = ","), digits=2,
 #              caption='Table 9.7.b Time (in minutes) from Start to Submit of ROI Preference Survey for Spanish',
 #              row.names=FALSE, align=c("l","c","c","c","c","c","c","c","c"),booktabs = TRUE)%>%
 #     kable_styling(latex_options = c("scale_down","hold_position"))

```





