---
title: "IRB Request"
author: "Kelsey Dowling"
date: "`r Sys.Date()`"
output:
  pdf_document: default
  html_document:
    df_print: paged
---



```{r, include=FALSE}
### NOTE!!!!! JAKES VERSION OF THE MODULE 1 FLATTENING STOPPED WORKING IN APRIL OF 2025. THE LAST SUCCESSFUL UPDATE WAS MAY 22ND AT 2025. This report ran in 2025 with that outdatd JP flattened data. The code has since been corrected with Eddie's version of the flattening to be used in 2026 and moving forward


```





```{r libraries, include=FALSE}


#  pdf-engine: xelatex
#tinytex::install_tinytex()

library(bigrquery)
library(epiDisplay) ##recommended applied here crosstable, tab1
library(gmodels) ##recommended
library(arsenal)
library(gtsummary)
library(rio)
library(glue)


library(ggplot2)
library(gridExtra)
library(scales)
library(gt)
library(tinytex)
library(data.table) ###to write or read and data management 
library(tidyverse) ###for data management
library(dplyr) ###data management
library(lubridate) ###date time
library(stringr) ###to work on patterns, charaters
library(kableExtra)


options(tinytex.verbose = TRUE)

bq_auth()

project <- "nih-nci-dceg-connect-prod-6d04"
billing <- "nih-nci-dceg-connect-prod-6d04" 

currentDate <- Sys.Date()
  
```




```{r merge1, include=FALSE, warning=FALSE}

## MERGE MOD1V1, MOD1V2


#Data Dictionary for column names
dictionary <- rio::import("https://episphere.github.io/conceptGithubActions/aggregate.json",format = "json")
dd <- dplyr::bind_rows(dictionary,.id="CID")
dd <-rbindlist(dictionary,fill=TRUE,use.names=TRUE,idcol="CID")
dd$`Variable Label`[is.na(dd$`Variable Label`)] <- replace_na(dd$'Variable Name')
dd <- as.data.frame.matrix(do.call("rbind",dictionary)) 
dd$CID <- rownames(dd)
#https://shaivyakodan.medium.com/7-useful-r-packages-for-analysis-7f60d28dca98
devtools::install_github("tidyverse/reprex")





## BQ Pull from the participants table just to use for versioning
project <- "nih-nci-dceg-connect-prod-6d04"
billing <- "nih-nci-dceg-connect-prod-6d04" 
recr_M1 <- bq_project_query(project, query="SELECT token,Connect_ID, d_821247024, d_914594314,  d_827220437,d_512820379,
                            d_949302066 , d_517311251  FROM  `nih-nci-dceg-connect-prod-6d04.FlatConnect.participants` WHERE  d_821247024='197316935' and d_949302066 ='231311385'")
recr_m1 <- bq_table_download(recr_M1,bigint = "integer64")
cnames <- names(recr_m1)
# Check that it doesn't match any non-number
numbers_only <- function(x) !grepl("\\D", x)
# to check variables in recr_noinact_wl1
for (i in 1: length(cnames)){
  varname <- cnames[i]
  var<-pull(recr_m1,varname)
  recr_m1[,cnames[i]] <- ifelse(numbers_only(var), as.numeric(as.character(var)), var)
}




#### Handling participants that somehow completed both Mod1 version 1 and Mod1 version 2

sql_M1_1 <- bq_project_query(project, query = "SELECT * FROM `nih-nci-dceg-connect-prod-6d04.FlatConnect.module1_v1` WHERE Connect_ID IS NOT NULL")
sql_M1_2 <- bq_project_query(project, query = "SELECT * FROM `nih-nci-dceg-connect-prod-6d04.FlatConnect.module1_v2` WHERE Connect_ID IS NOT NULL")

M1_V1 <- bq_table_download(sql_M1_1, bigint = "integer64")
M1_V2 <- bq_table_download(sql_M1_2, bigint = "integer64")

# Select matching column names
M1_V1_vars <- colnames(M1_V1)
M1_V2_vars <- colnames(M1_V2)
common_vars <- intersect(M1_V1_vars, M1_V2_vars)

# Subset to common columns
M1_V1_common <- M1_V1[, common_vars]
M1_V2_common <- M1_V2[, common_vars]

# Add version indicator
M1_V1_common$version <- 1
M1_V2_common$version <- 2

# Identify columns with mismatched types
mismatched_cols <- names(M1_V1_common)[sapply(names(M1_V1_common), function(col) {
  class(M1_V1_common[[col]]) != class(M1_V2_common[[col]])
})]

# Convert mismatched columns to character for consistency
M1_V1_common <- M1_V1_common %>%
  mutate(across(all_of(mismatched_cols), as.character))
M1_V2_common <- M1_V2_common %>%
  mutate(across(all_of(mismatched_cols), as.character))

# Combine both versions for participants who completed both
M1_common <- bind_rows(M1_V1_common, M1_V2_common) %>%
  arrange(Connect_ID, desc(version))

# For columns unique to each version
V1_only_vars <- setdiff(M1_V1_vars, common_vars)
V2_only_vars <- setdiff(M1_V2_vars, common_vars)

# Subset each version for unique columns and add version indicator
m1_v1_only <- M1_V1[, c("Connect_ID", V1_only_vars)] %>%
  mutate(version = 1)
m1_v2_only <- M1_V2[, c("Connect_ID", V2_only_vars)] %>%
  mutate(version = 2)

# Combine the unique and common data

M1_common$Connect_ID <- as.numeric(M1_common$Connect_ID)
m1_v1_only$Connect_ID <- as.numeric(m1_v1_only$Connect_ID)
m1_v2_only$Connect_ID <- as.numeric(m1_v2_only$Connect_ID)

m1_common_v1 <- left_join(M1_common, m1_v1_only, by = c("Connect_ID", "version"))

m1_common_v1$Connect_ID <- as.numeric(m1_common_v1$Connect_ID)
m1_combined_v1v2 <- left_join(m1_common_v1, m1_v2_only, by = c("Connect_ID", "version"))

# Filter for complete cases where specific completion criteria are met
m1_complete <- m1_combined_v1v2 %>%
  filter(Connect_ID %in% recr_m1$Connect_ID[recr_m1$d_949302066 == 231311385]) %>%
  arrange(desc(version))

# Remove duplicates, keeping only the most recent version for each Connect_ID
m1_complete_nodup <- m1_complete[!duplicated(m1_complete$Connect_ID),]

m1_complete_nodup$Connect_ID <- as.numeric(m1_complete_nodup$Connect_ID)







#dim(base_vars)

knitr::opts_chunk$set(comment = NA)



parts <- "SELECT Connect_ID, d_564964481, d_795827569, d_544150384, d_117249500, d_454445267,d_949302066 FROM `nih-nci-dceg-connect-prod-6d04.FlatConnect.participants` where Connect_ID IS NOT NULL and 
d_821247024='197316935' and d_747006172!='353358909' and d_831041022!='353358909' and
DATE(d_914594314) < DATE(CURRENT_TIMESTAMP())" 
parts_table <- bq_project_query(project, parts)
parts_data <- bq_table_download(parts_table, bigint = "integer64",n_max = Inf, page_size = 10000)

parts_data$Connect_ID <- as.numeric(parts_data$Connect_ID)


irb= left_join(parts_data,m1_complete_nodup,  by="Connect_ID") 
dim(irb)


```


```{r Race, warning=FALSE, echo=FALSE, message=FALSE}


#################### Multi-racial

#NOT including Hispanic here because its being considered an ethnicity instead of a race-- if they choose hispanic and ONE other race they shouldn't be counted as multi-racial
race_columns <- c("D_384191091_D_384191091_D_583826374", 
                  "D_384191091_D_384191091_D_636411467",
                  "D_384191091_D_384191091_D_458435048",
                  "D_384191091_D_384191091_D_973565052",
                  "D_384191091_D_384191091_D_586825330",
                  "D_384191091_D_384191091_D_412790539",
                  "D_384191091_D_384191091_D_807835037")

# All data is currently string values, need to convert "1" and "0" to 1 and 0 to be summarized
irb[race_columns] <- lapply(irb[race_columns], as.numeric)

irb$multi_racial <- ifelse(rowSums(irb[race_columns], na.rm = TRUE) > 1, 1, 0)




########## DOB

# Convert to numeric and handle non-numeric values
irb <- irb %>%
  mutate(
    d_544150384 = as.numeric(as.character(d_544150384)),
    d_795827569 = as.numeric(as.character(d_795827569)),
    d_564964481 = as.numeric(as.character(d_564964481))
  )

# Ensure month and day are two digits
irb <- irb %>%
  mutate(
    d_795827569 = ifelse(d_795827569 < 10, paste0("0", d_795827569), as.character(d_795827569)),
    d_564964481 = ifelse(d_564964481 < 10, paste0("0", d_564964481), as.character(d_564964481))
  )







irb = irb %>%  mutate(race= case_when(d_949302066==231311385 & multi_racial==1 ~ "More than One Race",
                                      d_949302066==231311385 &  (D_384191091_D_384191091_D_412790539==1 | D_384191091_D_384191091_D_973565052==1) ~ "White",
                                      d_949302066==231311385 &  D_384191091_D_384191091_D_583826374==1 ~ "American Indian/Alaska Native",
                                      d_949302066==231311385 &  D_384191091_D_384191091_D_636411467==1 ~ "Asian",
                                      d_949302066==231311385 &  D_384191091_D_384191091_D_458435048==1 ~ "Black or African American",
                                      #d_949302066==231311385 &  D_384191091_D_384191091_D_706998638==1 ~ "Hispanic, Latino, or Spanish", #category instead
                                      #d_949302066==231311385 &  D_384191091_D_384191091_D_973565052==1 ~ "Middle Eastern or North African", #grouped with White as requested
                                      d_949302066==231311385 &  D_384191091_D_384191091_D_586825330==1 ~ "Native Hawaiian or Other Pacific Islander",
                                      TRUE  ~ "Unknown or Not Reported"),
                      race_hisp= case_when(d_949302066==231311385 & D_384191091_D_384191091_D_706998638==0 ~ "Not Hispanic or Latino",
                                           d_949302066==231311385 & D_384191091_D_384191091_D_706998638==1 ~ "Hispanic or Latino",
                                           TRUE  ~ "Unknown/Not Reported Ethnicity"),
                     sex_at_birth= case_when(d_949302066==231311385& D_407056417== 536341288 ~ "Female",
                                             d_949302066==231311385 & D_407056417== 654207589 ~ "Male",
                                             TRUE ~"Unknown/Not Reported"),
                     DOB = as.Date(paste(d_544150384, d_564964481, d_795827569, sep = "-")),
                     consent_date = as.Date(d_454445267),
                     age_at_consent=lubridate::time_length(consent_date-DOB, "year"),
                     age= round(age_at_consent,digits=0))

                     
```
 
```{r Documenting, echo=FALSE, message=FALSE, warning=FALSE, collapse=TRUE}

wd_ver <- "SELECT Connect_ID,d_821247024,d_747006172  FROM `nih-nci-dceg-connect-prod-6d04.FlatConnect.participants` where Connect_ID IS NOT NULL
and DATE(d_914594314) < DATE(CURRENT_TIMESTAMP())" 
wd_ver_table <- bq_project_query(project, wd_ver)
wd_ver_data <- bq_table_download(wd_ver_table, bigint = "integer64",n_max = Inf, page_size = 10000)


wd <- wd_ver_data %>%  filter(d_747006172=='353358909' & d_821247024=='197316935')
ver <- wd_ver_data %>%  filter(d_821247024=='197316935') #d_747006172!='353358909' & 
finished_m1 <- irb %>% filter(d_949302066=='231311385')
current_date <- Sys.Date()

cat(paste("Data Extracted and Report Ran: ", currentDate))

cat(paste("Data includes enrollment through ", (currentDate-1)))

cat("Total number of verified participants= ", nrow(ver))

cat("Total number of verified participants who are withdrawn = ", nrow(wd))

cat("Denominator included in this report = ", nrow(irb))

cat("Of those,", nrow(finished_m1) , " submitted Module 1.")	



```
 
Participants who did not submit Module 1 are counted as race, ethnicity and sex = unknown.

The question RACEETH was used for race and ethnicity.

The question on sex at birth was used for this report. It is a required question on Module 1.

The age listed is the age at consent, calculated by subtracting the DOB from the date the participant consented.

Middle Eastern or North African is an option in our survey but not an option on the Inclusion 
Enrollment Report. Following former census precedent, we classified those participants as White.

Hispanic, Latino, or Spanish is a race option in our survey but not an option on the Inclusion
Enrollment Report. For those that selected Hispanic, Latino, or Spanish as their only race in Module 1,
we classified  as 'Unknown/Not Reported'.

If Hispanic, Latino or Spanish was not selected but RACEETH was answered with at least one response category, 
they are defined as Ethnicity = Not Hispanic or Latino.

If Hispanic, Latino or Spanish was selected and RACEETH was answered with at least one response category, 
they are defined as Ethnicity = Hispanic or Latino.

If RACETH was entirely missing, Ethnicity = Unknown.

\newpage
 
```{r Table1, warning=FALSE, echo=FALSE, message=FALSE}



count_table <- irb %>%
  group_by(race, race_hisp, sex_at_birth) %>%
  summarize(count = n(), .groups = 'drop') %>%
  arrange(race, race_hisp, sex_at_birth)

colnames(count_table) <- c("Race", "Ethnicity", "Sex", "Total")


# Add a total row
count_table <- count_table %>%
  bind_rows(
    data.frame(
      Race = "Total",
      Ethnicity = "",
      Sex = "",
      Total = sum(count_table$Total, na.rm = TRUE)
    )
  )


knitr::kable(count_table, format.args = list(big.mark = ","),
             caption="Cumulative Inclusion Enrollment Report", 
             row.names=FALSE,align=c("l","c","c","c"),
             booktabs = TRUE) %>%  
  add_indent(seq(1, nrow(count_table) - 1))  %>% 
  kable_styling(latex_options = "scale_down")
    
  
```


```{r Table2, warning=FALSE, echo=FALSE, message=FALSE}

irb$age_unit <- rep("Years", times=nrow(irb))

table2csv <- irb %>%  group_by(Connect_ID) %>%  select(Connect_ID, race,race_hisp, sex_at_birth,age, age_unit) 
table2csv <- table2csv[, c(2:ncol(table2csv))]

write.csv(table2csv,glue("Participant_Age_Data_Table_{currentDate}.csv"),row.names = F,na="")

```

```{r crosswalk, warning=FALSE, echo=FALSE, message=FALSE}



### Section Deemed no longer useful on 4/25/2025

# confusion on how to handle multiracial for modile 1 responses so Hispanic+ one other race wasn't randomly assigned by case when order 



# ### How participants actually responded, leaving our categories as they are asked in Mod1. Those that didn't complete Mod1 go into 'Skipped this question'
# irb= irb %>%  mutate(actual_race= case_when(multi_racial==1 ~ "Multi-Racial",
#                                                      D_384191091_D_384191091_D_583826374==1 ~ "American Indian or Native American",
#                                                      D_384191091_D_384191091_D_636411467==1 ~ "Asian/Asian American",
#                                                      D_384191091_D_384191091_D_458435048==1 ~ "Black, African American, or African",
#                                                      D_384191091_D_384191091_D_706998638==1 ~ "Hispanic, Latino, or Spanish",
#                                                      D_384191091_D_384191091_D_973565052==1 ~ "Middle Eastern or North African",
#                                                      D_384191091_D_384191091_D_586825330==1 ~ "Hawaiian or Pacific Islander",
#                                                      D_384191091_D_384191091_D_412790539==1 ~ "White",
#                                                      (D_384191091_D_384191091_D_807835037==1 | !is.na(D_384191091_D_747350323)) ~ "Other",
#                                                      D_384191091_D_384191091_D_746038746==1 ~ "Prefer Not to Answer",
#                                                      TRUE  ~ "Skipped this question "))
# 
# race_crosswalk <- irb %>% dplyr::select(race,actual_race)  %>% 
#   tbl_cross(
#     row = actual_race,
#     col = race,
#     digits=c(0,1),
#     percent = "col",
#     label=list(actual_race="Module 1 Race Answers", race= "CIE Race Options"),
#     missing="ifany",
#     margin_text="Total")
# 
# race_crosswalk_totals <- as.data.frame(race_crosswalk)
# 
# race_crosswalk_totals <- race_crosswalk_totals[-1, ]
# 
# write.csv(race_crosswalk_totals,glue("RACEETH Options from Module 1 vs Race for the inclusion.csv"),row.names = F,na="")
# 
# 
# 
# 
# 
# 
# ## Deemed no longer useful 4/24/2025
# 
# eth_crosswalk <- irb %>% dplyr::select(race_hisp,actual_race)  %>% 
#   tbl_cross(
#     row = actual_race,
#     col = race_hisp,
#     digits=c(0,1),
#     percent = "col",
#     label=list(actual_race="Module 1 Race Answers", race_hisp= "CIE Ethnicity Options"),
#     missing="ifany",
#     margin_text="Total")
# 
# eth_crosswalk_totals <- as.data.frame(eth_crosswalk)
# 
# eth_crosswalk_totals <- eth_crosswalk_totals[-1, ]
# 
# 
# knitr::kable(eth_crosswalk_totals ,
#              caption='RACEETH Options from Module 1 vs Ethnicity for the inclusion',
#              row.names=FALSE,align=c("l","c","c","c","c","c","c"),
#              booktabs = TRUE)  %>%
#   add_indent(seq(1, nrow(eth_crosswalk_totals) - 1))  %>%
#   kable_styling(latex_options = "scale_down") %>% landscape()


```

