---
title: "Monthly Derived Survey Variables"
author: "Kelsey Sanchez"
date: "`r Sys.Date()`"
output: pdf_document
---




```{r libraries, include=FALSE}


#  pdf-engine: xelatex
#tinytex::install_tinytex()   ## only needs to be installed once 

library(bigrquery)
library(epiDisplay) ##recommended applied here crosstable, tab1
library(gmodels) ##recommended
library(arsenal)
library(gtsummary)
library(rio)



library(ggplot2)
library(gridExtra)
library(scales)
library(gt)
library(tinytex)
library(data.table) ###to write or read and data management 
library(tidyverse) ###for data management
library(dplyr) ###data management
library(lubridate) ###date time
library(stringr) ###to work on patterns, characters
options(tinytex.verbose = TRUE)

bq_auth()

```




```{r merge1, include=FALSE, warning=FALSE}


#Data Dictionary for column names
dictionary <- rio::import("https://episphere.github.io/conceptGithubActions/aggregate.json",format = "json")
dd <- dplyr::bind_rows(dictionary,.id="CID")
dd <-rbindlist(dictionary,fill=TRUE,use.names=TRUE,idcol="CID")
dd$`Variable Label`[is.na(dd$`Variable Label`)] <- replace_na(dd$'Variable Name')
dd <- as.data.frame.matrix(do.call("rbind",dictionary)) 
dd$CID <- rownames(dd)
#https://shaivyakodan.medium.com/7-useful-r-packages-for-analysis-7f60d28dca98
devtools::install_github("tidyverse/reprex")





## BQ Pull from the participants table just to use for versioning
project <- "nih-nci-dceg-connect-prod-6d04"
billing <- "nih-nci-dceg-connect-prod-6d04" 
recr_M1 <- bq_project_query(project, query="SELECT token,Connect_ID, d_821247024, d_914594314,  d_827220437,d_512820379,
                            d_949302066 , d_517311251  FROM  `nih-nci-dceg-connect-prod-6d04.FlatConnect.participants_JP` WHERE  d_821247024='197316935' and d_949302066 ='231311385'")
recr_m1 <- bq_table_download(recr_M1,bigint = "integer64")
cnames <- names(recr_m1)
# Check that it doesn't match any non-number
numbers_only <- function(x) !grepl("\\D", x)
# to check variables in recr_noinact_wl1
for (i in 1: length(cnames)){
  varname <- cnames[i]
  var<-pull(recr_m1,varname)
  recr_m1[,cnames[i]] <- ifelse(numbers_only(var), as.numeric(as.character(var)), var)
}




#### Handling participants that somehow completed both Mod1 version 1 and Mod1 version 2

sql_M1_1 <- bq_project_query(project, 
                             query = "SELECT D_276353712, D_659784914, D_607773106_1_1, D_607773106_2_2, D_607773106_3_3, D_607773106_4_4, D_607773106_5_5, D_607773106_6_6, 
                             D_607773106_7_7,  D_607773106_8_8, D_607773106_9_9,  D_607773106_10_10, D_607773106_11_11, D_607773106_12_12, D_607773106_13_13, D_718867914_1_1, 
                             D_718867914_2_2, D_718867914_3_3, D_718867914_4_4, D_718867914_5_5,D_718867914_6_6, D_718867914_7_7, D_718867914_8_8, D_718867914_9_9, 
                             D_718867914_10_10, D_114314839_D_340854069, D_114314839_D_600462977, D_746012894, Connect_ID
                             FROM `nih-nci-dceg-connect-prod-6d04.FlatConnect.module1_v1_JP` WHERE Connect_ID IS NOT NULL")

sql_M1_2 <- bq_project_query(project, 
                             query = "SELECT D_276353712, D_659784914, D_607773106_1_1, D_607773106_2_2, D_607773106_3_3, D_607773106_4_4, D_607773106_5_5, D_607773106_6_6, 
                             D_607773106_7_7,  D_607773106_8_8, D_607773106_9_9,  D_607773106_10_10, D_607773106_11_11, D_607773106_12_12, D_607773106_13_13, D_718867914_1_1, 
                             D_718867914_2_2, D_718867914_3_3, D_718867914_4_4, D_718867914_5_5,D_718867914_6_6, D_718867914_7_7, D_718867914_8_8, D_718867914_9_9, 
                             D_718867914_10_10, D_114314839_D_340854069, D_114314839_D_600462977, D_746012894, Connect_ID
                             FROM `nih-nci-dceg-connect-prod-6d04.FlatConnect.module1_v2_JP` WHERE Connect_ID IS NOT NULL")

M1_V1 <- bq_table_download(sql_M1_1, bigint = "integer64")
M1_V2 <- bq_table_download(sql_M1_2, bigint = "integer64")

# Select matching column names
M1_V1_vars <- colnames(M1_V1)
M1_V2_vars <- colnames(M1_V2)
common_vars <- intersect(M1_V1_vars, M1_V2_vars)

# Subset to common columns
M1_V1_common <- M1_V1[, common_vars]
M1_V2_common <- M1_V2[, common_vars]

# Add version indicator
M1_V1_common$version <- 1
M1_V2_common$version <- 2

# Identify columns with mismatched types
mismatched_cols <- names(M1_V1_common)[sapply(names(M1_V1_common), function(col) {
  class(M1_V1_common[[col]]) != class(M1_V2_common[[col]])
})]

# Convert mismatched columns to character for consistency
M1_V1_common <- M1_V1_common %>%
  mutate(across(all_of(mismatched_cols), as.character))
M1_V2_common <- M1_V2_common %>%
  mutate(across(all_of(mismatched_cols), as.character))

# Combine both versions for participants who completed both
M1_common <- bind_rows(M1_V1_common, M1_V2_common) %>%
  arrange(Connect_ID, desc(version))

# For columns unique to each version
V1_only_vars <- setdiff(M1_V1_vars, common_vars)
V2_only_vars <- setdiff(M1_V2_vars, common_vars)

# Subset each version for unique columns and add version indicator
m1_v1_only <- M1_V1[, c("Connect_ID", V1_only_vars)] %>%
  mutate(version = 1)
m1_v2_only <- M1_V2[, c("Connect_ID", V2_only_vars)] %>%
  mutate(version = 2)

# Combine the unique and common data
m1_common_v1 <- left_join(M1_common, m1_v1_only, by = c("Connect_ID", "version"))
m1_combined_v1v2 <- left_join(m1_common_v1, m1_v2_only, by = c("Connect_ID", "version"))

# Filter for complete cases where specific completion criteria are met
m1_complete <- m1_combined_v1v2 %>%
  filter(Connect_ID %in% recr_m1$Connect_ID[recr_m1$d_949302066 == 231311385]) %>%
  arrange(desc(version))

# Remove duplicates, keeping only the most recent version for each Connect_ID
m1_complete_nodup <- m1_complete[!duplicated(m1_complete$Connect_ID),]

m1_complete_nodup$Connect_ID <- as.numeric(m1_complete_nodup$Connect_ID)


## Define requirements of the data: active or passive,  user profile done, consented, mod1 done, verified
parts <- "SELECT Connect_ID, token,  state_d_934298480, d_564964481, d_795827569, d_544150384,  d_126331570, 
d_536735468, d_663265240, d_878865966, d_684635302, d_167958071, d_949302066 ,  d_976570371, d_914639140, d_311580100, d_100767870
FROM `nih-nci-dceg-connect-prod-6d04.FlatConnect.participants_JP` 
where Connect_ID IS NOT NULL and (d_512820379='486306141' OR d_512820379='854703046') and d_919254129='353358909' and d_699625233='353358909' and 
d_949302066='231311385'  and d_821247024='197316935'" 


parts_table <- bq_project_query(project, parts)
parts_data <- bq_table_download(parts_table, bigint = "integer64",n_max = Inf, page_size = 10000)

parts_data$Connect_ID <- as.numeric(parts_data$Connect_ID)


merged= left_join(parts_data, m1_complete_nodup, by="Connect_ID")
dim(merged)


data_tib_base <- as_tibble(merged)


knitr::opts_chunk$set(comment = NA)

```


\newpage

# BMI
```{r bmi, echo=FALSE, warning=FALSE, message=FALSE}

knitr::opts_chunk$set(dev = "png", fig.path = "")


data_tib_base$D_114314839_D_340854069=as.numeric(data_tib_base$D_114314839_D_340854069)
data_tib_base$D_114314839_D_600462977=as.numeric(data_tib_base$D_114314839_D_600462977)

data_tib_base$in_D_inches= (ifelse(is.na(data_tib_base$D_114314839_D_340854069), 0,(data_tib_base$D_114314839_D_340854069*12)))+ 
  (ifelse(is.na(data_tib_base$D_114314839_D_600462977), 0, (data_tib_base$D_114314839_D_600462977))) 

data_tib_base$D_746012894=as.numeric(data_tib_base$D_746012894) 
data_tib_base$D_746012894=round(data_tib_base$D_746012894, digits=0)

data_tib_base= data_tib_base %>%  mutate(BMI= (D_746012894/in_D_inches^2)*703)

bmi_box= data_tib_base %>%  filter(!is.na(BMI)) %>%  ggplot(aes(x=BMI))+
    xlab("Score") + geom_boxplot()+  ggtitle("BMI Distribution of Participants") + xlim(c(0,100))

bmi_box

```


# Primary Relative Diagnosed with Cancer
```{r PrimRelCancer, echo=FALSE, warning=FALSE, message=FALSE}



family= data_tib_base  %>%  mutate(status= case_when((D_276353712==353358909 | D_659784914==353358909 | D_607773106_1_1==353358909 | D_607773106_2_2==353358909 | 
                                      D_607773106_3_3==353358909 | D_607773106_4_4==353358909 | D_607773106_5_5==353358909 | D_607773106_6_6==353358909 |
                                      D_607773106_7_7==353358909| D_607773106_8_8==353358909 | D_607773106_9_9==353358909| D_607773106_10_10==353358909 |
                                      D_607773106_11_11==353358909 | D_607773106_12_12==353358909 | D_607773106_13_13==353358909 | D_718867914_1_1==353358909 | 
                                      D_718867914_2_2==353358909 | D_718867914_3_3==353358909 | D_718867914_4_4==353358909 | D_718867914_5_5==353358909 |
                                      D_718867914_6_6==353358909 | D_718867914_7_7==353358909 | D_718867914_8_8==353358909 | D_718867914_9_9==353358909 |
                                      D_718867914_10_10==353358909) ~ "Yes", 
                                                    TRUE ~ "No"))


dt_fam_canc_summary <- family %>% group_by(status) %>%  dplyr::summarize(n=n(), percentage=100*n/nrow(.))  %>% dplyr::ungroup() %>%  dplyr::select(status, n, percentage)

#gt_total_func(dt_fam_canc_summary, "status", "Primary Relative(s) Diagnosed With Cancer")

dt_fam_canc_summary %>%  gt::gt(rowname_col = "row_lab") %>%  
  fmt_number(columns = "percentage", decimals = 2) %>% 
  fmt_number(column = "n", decimals=0, use_seps = TRUE) %>% 
  tab_header(title = md("Primary Relative(s) Diagnosed With Cancer")) %>% 
  cols_label(n= md("**N**"), status = md("**Answer**"), percentage = md("**%**")) %>% 
  grand_summary_rows(columns=c(n, percentage),fns = ~sum(.,na.rm = T))|>
  tab_options(
    stub.font.weight = "bold"
  ) %>%
  tab_style(
    style = list(
      cell_text(weight = "bold")
    ),
    locations = cells_body(
      columns = status,
    )
  ) %>% 
  tab_footnote(footnote="Primary relatives consist of parents, siblings, and children.",
               placement = "left")

```










\newpage

```{r query3, include=FALSE}


querymod3 <- "SELECT Connect_ID, D_947205597_D_712653855, D_798549704, D_763164658, D_947205597_D_198133418, D_182431332, D_798549704, D_789271762, D_947205597_D_706254326, D_624111331, D_238422161
FROM `nih-nci-dceg-connect-prod-6d04.FlatConnect.module3_v1_JP` where Connect_ID IS NOT NULL"
mod3_table <- bq_project_query(project, querymod3)
mod3_data <- bq_table_download(mod3_table, bigint = "integer64")
mod3_data$Connect_ID <- as.numeric(mod3_data$Connect_ID)


data_all3= left_join(parts_data, mod3_data, by="Connect_ID")

data_all3 <- data_all3 %>% filter(d_976570371==231311385)

data_tib_all3 <- as_tibble(data_all3)


```




# Frequency of Cigarette Smoking

```{r cigerette, echo=FALSE, warning=FALSE, message=FALSE}

cig_frequency= data_tib_all3  %>% 
  mutate(often= case_when((D_947205597_D_712653855==0 | (D_947205597_D_712653855==1 & (D_763164658==151488193| D_763164658==805449318)))~"Never a Cigarette Smoker",
                             (D_947205597_D_712653855==1 & (D_763164658==486319890| D_763164658==132232896) & D_798549704==317567178)~"Currently a Cigarette Smoker",
                             (D_947205597_D_712653855==1 & (D_763164658==486319890| D_763164658==132232896)  & (D_798549704==484055234 | D_798549704==802197176))~"Formerly a Cigarette Smoker",
                             TRUE~"Skipped all these questions"))

dt_cig_frequency_summary <- cig_frequency %>% group_by(often) %>%  dplyr::summarize(n=n(), percentage=100*n/nrow(.))  %>% dplyr::ungroup() %>%  dplyr::select(often, n, percentage)


dt_cig_frequency_summary %>%  gt::gt(rowname_col = "row_lab") %>%  
  fmt_number(columns = "percentage", decimals = 2) %>% 
  fmt_number(column = "n", decimals=0, use_seps = TRUE) %>% 
  tab_header(title = md("Frequency of Cigarette Smoking")) %>% 
  cols_label(n= md("**N**"), often = md("**Answer**"), percentage = md("**%**")) %>% 
  grand_summary_rows(columns=c(n, percentage),fns = ~sum(.,na.rm = T))|>
  tab_options(
    stub.font.weight = "bold"
  ) %>%
  tab_style(
    style = list(
      cell_text(weight = "bold")
    ),
    locations = cells_body(
      columns = often,
    )
  ) 


```



# Frequency of Cigar Smoking

```{r cigar, echo=FALSE, warning=FALSE, message=FALSE}


cigar_frequency= data_tib_all3  %>% 
  mutate(often= case_when(D_947205597_D_198133418==0 | (D_947205597_D_198133418==1 & (D_182431332==151488193| D_182431332==805449318))~"Never a Cigar Smoker",
                             D_947205597_D_198133418==1 & (D_182431332==486319890| D_182431332==132232896) & D_798549704==317567178~"Currently a Cigar Smoker",
                             D_947205597_D_198133418==1 & (D_182431332==486319890| D_182431332==132232896)  & (D_789271762==484055234 | D_789271762==802197176)~"Formerly a Cigar Smoker",
                             TRUE~"Skipped all These Questions"))



dt_cigar_frequency_summary <- cigar_frequency %>% group_by(often) %>%  dplyr::summarize(n=n(), percentage=100*n/nrow(.))  %>% dplyr::ungroup() %>%  dplyr::select(often, n, percentage)

dt_cigar_frequency_summary %>%  gt::gt(rowname_col = "row_lab") %>%  
  fmt_number(columns = "percentage", decimals = 2) %>% 
  fmt_number(column = "n", decimals=0, use_seps = TRUE) %>% 
  tab_header(title = md("Frequency of Cigar Smoking")) %>% 
  cols_label(n= md("**N**"), often = md("**Answer**"), percentage = md("**%**")) %>% 
  grand_summary_rows(columns=c(n, percentage),fns = ~sum(.,na.rm = T))|>
  tab_options(
    stub.font.weight = "bold"
  ) %>%
  tab_style(
    style = list(
      cell_text(weight = "bold")
    ),
    locations = cells_body(
      columns = often,
    )
  ) 


```




# Frequency of E-cig Smoking

```{r ecig, echo=FALSE, warning=FALSE, message=FALSE}


e_cig_frequency= data_tib_all3  %>% 
  mutate(often= case_when(D_947205597_D_706254326==0 | (D_947205597_D_706254326==1 & (D_624111331==151488193| D_624111331==805449318))~"Never a E-cigarette Smoker",
                             D_947205597_D_706254326==1 & (D_624111331==486319890| D_624111331==132232896) & D_238422161==317567178~"Currently a E-cigarette Smoker",
                             D_947205597_D_706254326==1 & (D_624111331==486319890| D_624111331==132232896)  & (D_238422161==484055234 | D_238422161==802197176)~"Formerly a E-cigarette Smoker",
                             TRUE~"Skipped all These Questions"))



dt_e_cig_frequency_summary <- e_cig_frequency %>% group_by(often) %>%  dplyr::summarize(n=n(), percentage=100*n/nrow(.))  %>% dplyr::ungroup() %>%  dplyr::select(often, n, percentage)

dt_e_cig_frequency_summary %>%  gt::gt(rowname_col = "row_lab") %>%  
  fmt_number(columns = "percentage", decimals = 2) %>% 
  fmt_number(column = "n", decimals=0, use_seps = TRUE) %>% 
  tab_header(title = md("Frequency of Electronic Cigarette Smoking")) %>% 
  cols_label(n= md("**N**"), often = md("**Answer**"), percentage = md("**%**")) %>% 
  grand_summary_rows(columns=c(n, percentage),fns = ~sum(.,na.rm = T))|>
  tab_options(
    stub.font.weight = "bold"
  ) %>%
  tab_style(
    style = list(
      cell_text(weight = "bold")
    ),
    locations = cells_body(
      columns = often,
    )
  ) 


```
=======
---
title: "Monthly Derived Survey Variables"
author: "Kelsey Sanchez"
date: "`r Sys.Date()`"
output: pdf_document
---




```{r libraries, include=FALSE}


#  pdf-engine: xelatex
#tinytex::install_tinytex()   ## only needs to be installed once 

library(bigrquery)
library(epiDisplay) ##recommended applied here crosstable, tab1
library(gmodels) ##recommended
library(arsenal)
library(gtsummary)
library(rio)



library(ggplot2)
library(gridExtra)
library(scales)
library(gt)
library(tinytex)
library(data.table) ###to write or read and data management 
library(tidyverse) ###for data management
library(dplyr) ###data management
library(lubridate) ###date time
library(stringr) ###to work on patterns, characters
options(tinytex.verbose = TRUE)

bq_auth()

```




```{r merge1, include=FALSE, warning=FALSE}


#Data Dictionary for column names
dictionary <- rio::import("https://episphere.github.io/conceptGithubActions/aggregate.json",format = "json")
dd <- dplyr::bind_rows(dictionary,.id="CID")
dd <-rbindlist(dictionary,fill=TRUE,use.names=TRUE,idcol="CID")
dd$`Variable Label`[is.na(dd$`Variable Label`)] <- replace_na(dd$'Variable Name')
dd <- as.data.frame.matrix(do.call("rbind",dictionary)) 
dd$CID <- rownames(dd)
#https://shaivyakodan.medium.com/7-useful-r-packages-for-analysis-7f60d28dca98
devtools::install_github("tidyverse/reprex")





## BQ Pull from the participants table just to use for versioning
project <- "nih-nci-dceg-connect-prod-6d04"
billing <- "nih-nci-dceg-connect-prod-6d04" 
recr_M1 <- bq_project_query(project, query="SELECT token,Connect_ID, d_821247024, d_914594314,  d_827220437,d_512820379,
                            d_949302066 , d_517311251  FROM  `nih-nci-dceg-connect-prod-6d04.FlatConnect.participants_JP` WHERE  d_821247024='197316935' and d_949302066 ='231311385'")
recr_m1 <- bq_table_download(recr_M1,bigint = "integer64")
cnames <- names(recr_m1)
# Check that it doesn't match any non-number
numbers_only <- function(x) !grepl("\\D", x)
# to check variables in recr_noinact_wl1
for (i in 1: length(cnames)){
  varname <- cnames[i]
  var<-pull(recr_m1,varname)
  recr_m1[,cnames[i]] <- ifelse(numbers_only(var), as.numeric(as.character(var)), var)
}




#### Handling participants that somehow completed both Mod1 version 1 and Mod1 version 2

sql_M1_1 <- bq_project_query(project, 
                             query = "SELECT D_276353712, D_659784914, D_607773106_1_1, D_607773106_2_2, D_607773106_3_3, D_607773106_4_4, D_607773106_5_5, D_607773106_6_6, 
                             D_607773106_7_7,  D_607773106_8_8, D_607773106_9_9,  D_607773106_10_10, D_607773106_11_11, D_607773106_12_12, D_607773106_13_13, D_718867914_1_1, 
                             D_718867914_2_2, D_718867914_3_3, D_718867914_4_4, D_718867914_5_5,D_718867914_6_6, D_718867914_7_7, D_718867914_8_8, D_718867914_9_9, 
                             D_718867914_10_10, D_114314839_D_340854069, D_114314839_D_600462977, D_746012894, Connect_ID
                             FROM `nih-nci-dceg-connect-prod-6d04.FlatConnect.module1_v1_JP` WHERE Connect_ID IS NOT NULL")

sql_M1_2 <- bq_project_query(project, 
                             query = "SELECT D_276353712, D_659784914, D_607773106_1_1, D_607773106_2_2, D_607773106_3_3, D_607773106_4_4, D_607773106_5_5, D_607773106_6_6, 
                             D_607773106_7_7,  D_607773106_8_8, D_607773106_9_9,  D_607773106_10_10, D_607773106_11_11, D_607773106_12_12, D_607773106_13_13, D_718867914_1_1, 
                             D_718867914_2_2, D_718867914_3_3, D_718867914_4_4, D_718867914_5_5,D_718867914_6_6, D_718867914_7_7, D_718867914_8_8, D_718867914_9_9, 
                             D_718867914_10_10, D_114314839_D_340854069, D_114314839_D_600462977, D_746012894, Connect_ID
                             FROM `nih-nci-dceg-connect-prod-6d04.FlatConnect.module1_v2_JP` WHERE Connect_ID IS NOT NULL")

M1_V1 <- bq_table_download(sql_M1_1, bigint = "integer64")
M1_V2 <- bq_table_download(sql_M1_2, bigint = "integer64")

# Select matching column names
M1_V1_vars <- colnames(M1_V1)
M1_V2_vars <- colnames(M1_V2)
common_vars <- intersect(M1_V1_vars, M1_V2_vars)

# Subset to common columns
M1_V1_common <- M1_V1[, common_vars]
M1_V2_common <- M1_V2[, common_vars]

# Add version indicator
M1_V1_common$version <- 1
M1_V2_common$version <- 2

# Identify columns with mismatched types
mismatched_cols <- names(M1_V1_common)[sapply(names(M1_V1_common), function(col) {
  class(M1_V1_common[[col]]) != class(M1_V2_common[[col]])
})]

# Convert mismatched columns to character for consistency
M1_V1_common <- M1_V1_common %>%
  mutate(across(all_of(mismatched_cols), as.character))
M1_V2_common <- M1_V2_common %>%
  mutate(across(all_of(mismatched_cols), as.character))

# Combine both versions for participants who completed both
M1_common <- bind_rows(M1_V1_common, M1_V2_common) %>%
  arrange(Connect_ID, desc(version))

# For columns unique to each version
V1_only_vars <- setdiff(M1_V1_vars, common_vars)
V2_only_vars <- setdiff(M1_V2_vars, common_vars)

# Subset each version for unique columns and add version indicator
m1_v1_only <- M1_V1[, c("Connect_ID", V1_only_vars)] %>%
  mutate(version = 1)
m1_v2_only <- M1_V2[, c("Connect_ID", V2_only_vars)] %>%
  mutate(version = 2)

# Combine the unique and common data
m1_common_v1 <- left_join(M1_common, m1_v1_only, by = c("Connect_ID", "version"))
m1_combined_v1v2 <- left_join(m1_common_v1, m1_v2_only, by = c("Connect_ID", "version"))

# Filter for complete cases where specific completion criteria are met
m1_complete <- m1_combined_v1v2 %>%
  filter(Connect_ID %in% recr_m1$Connect_ID[recr_m1$d_949302066 == 231311385]) %>%
  arrange(desc(version))

# Remove duplicates, keeping only the most recent version for each Connect_ID
m1_complete_nodup <- m1_complete[!duplicated(m1_complete$Connect_ID),]

m1_complete_nodup$Connect_ID <- as.numeric(m1_complete_nodup$Connect_ID)


## Define requirements of the data: active or passive,  user profile done, consented, mod1 done, verified
parts <- "SELECT Connect_ID, token,  state_d_934298480, d_564964481, d_795827569, d_544150384,  d_126331570, 
d_536735468, d_663265240, d_878865966, d_684635302, d_167958071, d_949302066 ,  d_976570371, d_914639140, d_311580100, d_100767870
FROM `nih-nci-dceg-connect-prod-6d04.FlatConnect.participants_JP` 
where Connect_ID IS NOT NULL and (d_512820379='486306141' OR d_512820379='854703046') and d_919254129='353358909' and d_699625233='353358909' and 
d_949302066='231311385'  and d_821247024='197316935'" 


parts_table <- bq_project_query(project, parts)
parts_data <- bq_table_download(parts_table, bigint = "integer64",n_max = Inf, page_size = 10000)

parts_data$Connect_ID <- as.numeric(parts_data$Connect_ID)


merged= left_join(parts_data, m1_complete_nodup, by="Connect_ID")
dim(merged)


data_tib_base <- as_tibble(merged)


knitr::opts_chunk$set(comment = NA)

```


\newpage

# BMI
```{r bmi, echo=FALSE, warning=FALSE, message=FALSE}

knitr::opts_chunk$set(dev = "png", fig.path = "")


data_tib_base$D_114314839_D_340854069=as.numeric(data_tib_base$D_114314839_D_340854069)
data_tib_base$D_114314839_D_600462977=as.numeric(data_tib_base$D_114314839_D_600462977)

data_tib_base$in_D_inches= (ifelse(is.na(data_tib_base$D_114314839_D_340854069), 0,(data_tib_base$D_114314839_D_340854069*12)))+ 
  (ifelse(is.na(data_tib_base$D_114314839_D_600462977), 0, (data_tib_base$D_114314839_D_600462977))) 

data_tib_base$D_746012894=as.numeric(data_tib_base$D_746012894) 
data_tib_base$D_746012894=round(data_tib_base$D_746012894, digits=0)

data_tib_base= data_tib_base %>%  mutate(BMI= (D_746012894/in_D_inches^2)*703)

bmi_box= data_tib_base %>%  filter(!is.na(BMI)) %>%  ggplot(aes(x=BMI))+
    xlab("Score") + geom_boxplot()+  ggtitle("BMI Distribution of Participants") + xlim(c(0,100))

bmi_box

```


# Primary Relative Diagnosed with Cancer
```{r PrimRelCancer, echo=FALSE, warning=FALSE, message=FALSE}



family= data_tib_base  %>%  mutate(status= case_when((D_276353712==353358909 | D_659784914==353358909 | D_607773106_1_1==353358909 | D_607773106_2_2==353358909 | 
                                      D_607773106_3_3==353358909 | D_607773106_4_4==353358909 | D_607773106_5_5==353358909 | D_607773106_6_6==353358909 |
                                      D_607773106_7_7==353358909| D_607773106_8_8==353358909 | D_607773106_9_9==353358909| D_607773106_10_10==353358909 |
                                      D_607773106_11_11==353358909 | D_607773106_12_12==353358909 | D_607773106_13_13==353358909 | D_718867914_1_1==353358909 | 
                                      D_718867914_2_2==353358909 | D_718867914_3_3==353358909 | D_718867914_4_4==353358909 | D_718867914_5_5==353358909 |
                                      D_718867914_6_6==353358909 | D_718867914_7_7==353358909 | D_718867914_8_8==353358909 | D_718867914_9_9==353358909 |
                                      D_718867914_10_10==353358909) ~ "Yes", 
                                                    TRUE ~ "No"))


dt_fam_canc_summary <- family %>% group_by(status) %>%  dplyr::summarize(n=n(), percentage=100*n/nrow(.))  %>% dplyr::ungroup() %>%  dplyr::select(status, n, percentage)

#gt_total_func(dt_fam_canc_summary, "status", "Primary Relative(s) Diagnosed With Cancer")

dt_fam_canc_summary %>%  gt::gt(rowname_col = "row_lab") %>%  
  fmt_number(columns = "percentage", decimals = 2) %>% 
  fmt_number(column = "n", decimals=0, use_seps = TRUE) %>% 
  tab_header(title = md("Primary Relative(s) Diagnosed With Cancer")) %>% 
  cols_label(n= md("**N**"), status = md("**Answer**"), percentage = md("**%**")) %>% 
  grand_summary_rows(columns=c(n, percentage),fns = ~sum(.,na.rm = T))|>
  tab_options(
    stub.font.weight = "bold"
  ) %>%
  tab_style(
    style = list(
      cell_text(weight = "bold")
    ),
    locations = cells_body(
      columns = status,
    )
  ) %>% 
  tab_footnote(footnote="Primary relatives consist of parents, siblings, and children.",
               placement = "left")

```










\newpage

```{r query3, include=FALSE}


querymod3 <- "SELECT Connect_ID, D_947205597_D_712653855, D_798549704, D_763164658, D_947205597_D_198133418, D_182431332, D_798549704, D_789271762, D_947205597_D_706254326, D_624111331, D_238422161
FROM `nih-nci-dceg-connect-prod-6d04.FlatConnect.module3_v1_JP` where Connect_ID IS NOT NULL"
mod3_table <- bq_project_query(project, querymod3)
mod3_data <- bq_table_download(mod3_table, bigint = "integer64")
mod3_data$Connect_ID <- as.numeric(mod3_data$Connect_ID)


data_all3= left_join(parts_data, mod3_data, by="Connect_ID")

data_all3 <- data_all3 %>% filter(d_976570371==231311385)

data_tib_all3 <- as_tibble(data_all3)


```




# Frequency of Cigarette Smoking

```{r cigerette, echo=FALSE, warning=FALSE, message=FALSE}

cig_frequency= data_tib_all3  %>% 
  mutate(often= case_when((D_947205597_D_712653855==0 | (D_947205597_D_712653855==1 & (D_763164658==151488193| D_763164658==805449318)))~"Never a Cigarette Smoker",
                             (D_947205597_D_712653855==1 & (D_763164658==486319890| D_763164658==132232896) & D_798549704==317567178)~"Currently a Cigarette Smoker",
                             (D_947205597_D_712653855==1 & (D_763164658==486319890| D_763164658==132232896)  & (D_798549704==484055234 | D_798549704==802197176))~"Formerly a Cigarette Smoker",
                             TRUE~"Skipped all these questions"))

dt_cig_frequency_summary <- cig_frequency %>% group_by(often) %>%  dplyr::summarize(n=n(), percentage=100*n/nrow(.))  %>% dplyr::ungroup() %>%  dplyr::select(often, n, percentage)


dt_cig_frequency_summary %>%  gt::gt(rowname_col = "row_lab") %>%  
  fmt_number(columns = "percentage", decimals = 2) %>% 
  fmt_number(column = "n", decimals=0, use_seps = TRUE) %>% 
  tab_header(title = md("Frequency of Cigarette Smoking")) %>% 
  cols_label(n= md("**N**"), often = md("**Answer**"), percentage = md("**%**")) %>% 
  grand_summary_rows(columns=c(n, percentage),fns = ~sum(.,na.rm = T))|>
  tab_options(
    stub.font.weight = "bold"
  ) %>%
  tab_style(
    style = list(
      cell_text(weight = "bold")
    ),
    locations = cells_body(
      columns = often,
    )
  ) 


```



# Frequency of Cigar Smoking

```{r cigar, echo=FALSE, warning=FALSE, message=FALSE}


cigar_frequency= data_tib_all3  %>% 
  mutate(often= case_when(D_947205597_D_198133418==0 | (D_947205597_D_198133418==1 & (D_182431332==151488193| D_182431332==805449318))~"Never a Cigar Smoker",
                             D_947205597_D_198133418==1 & (D_182431332==486319890| D_182431332==132232896) & D_798549704==317567178~"Currently a Cigar Smoker",
                             D_947205597_D_198133418==1 & (D_182431332==486319890| D_182431332==132232896)  & (D_789271762==484055234 | D_789271762==802197176)~"Formerly a Cigar Smoker",
                             TRUE~"Skipped all These Questions"))



dt_cigar_frequency_summary <- cigar_frequency %>% group_by(often) %>%  dplyr::summarize(n=n(), percentage=100*n/nrow(.))  %>% dplyr::ungroup() %>%  dplyr::select(often, n, percentage)

dt_cigar_frequency_summary %>%  gt::gt(rowname_col = "row_lab") %>%  
  fmt_number(columns = "percentage", decimals = 2) %>% 
  fmt_number(column = "n", decimals=0, use_seps = TRUE) %>% 
  tab_header(title = md("Frequency of Cigar Smoking")) %>% 
  cols_label(n= md("**N**"), often = md("**Answer**"), percentage = md("**%**")) %>% 
  grand_summary_rows(columns=c(n, percentage),fns = ~sum(.,na.rm = T))|>
  tab_options(
    stub.font.weight = "bold"
  ) %>%
  tab_style(
    style = list(
      cell_text(weight = "bold")
    ),
    locations = cells_body(
      columns = often,
    )
  ) 


```




# Frequency of E-cig Smoking

```{r ecig, echo=FALSE, warning=FALSE, message=FALSE}


e_cig_frequency= data_tib_all3  %>% 
  mutate(often= case_when(D_947205597_D_706254326==0 | (D_947205597_D_706254326==1 & (D_624111331==151488193| D_624111331==805449318))~"Never a E-cigarette Smoker",
                             D_947205597_D_706254326==1 & (D_624111331==486319890| D_624111331==132232896) & D_238422161==317567178~"Currently a E-cigarette Smoker",
                             D_947205597_D_706254326==1 & (D_624111331==486319890| D_624111331==132232896)  & (D_238422161==484055234 | D_238422161==802197176)~"Formerly a E-cigarette Smoker",
                             TRUE~"Skipped all These Questions"))



dt_e_cig_frequency_summary <- e_cig_frequency %>% group_by(often) %>%  dplyr::summarize(n=n(), percentage=100*n/nrow(.))  %>% dplyr::ungroup() %>%  dplyr::select(often, n, percentage)

dt_e_cig_frequency_summary %>%  gt::gt(rowname_col = "row_lab") %>%  
  fmt_number(columns = "percentage", decimals = 2) %>% 
  fmt_number(column = "n", decimals=0, use_seps = TRUE) %>% 
  tab_header(title = md("Frequency of Electronic Cigarette Smoking")) %>% 
  cols_label(n= md("**N**"), often = md("**Answer**"), percentage = md("**%**")) %>% 
  grand_summary_rows(columns=c(n, percentage),fns = ~sum(.,na.rm = T))|>
  tab_options(
    stub.font.weight = "bold"
  ) %>%
  tab_style(
    style = list(
      cell_text(weight = "bold")
    ),
    locations = cells_body(
      columns = often,
    )
  ) 


```
